### 2020-10-16 manuscript/manuscript.Rmd

---
title: "BMI-manuscript"
output: 
    bookdown::pdf_document2:  
        keep_tex: true
bibliography: cite.bib
link_citations: true
---
\section{introduction}
Body Mass Idex (BMI) playes an important rule in predicting heart disease risk. BMI     
 .
[@van2012estimating]
\section{methode}
From the figure we see ...

```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "exploratory.png"))) {
    source(here::here("exploratory-data-analysis.R"))
}
knitr::include_graphics(here::here("images", "exploratory.png"))
```
# References

### 2020-10-16 manuscript/manuscript.tex

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={BMI-manuscript},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\title{BMI-manuscript}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\section{introduction}

Body Mass Idex (BMI) playes an important rule in predicting heart
disease risk. BMI\\
. (Van de Kassteele et al. 2012) \section{methode} From the figure we
see \ldots{}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/exploratory}

}

\caption{A better figure caption}\label{fig:unnamed-chunk-1}
\end{figure}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-van2012estimating}{}
Van de Kassteele, Jan, RT Hoogenveen, PM Engelfriet, PHM Van Baal, and
HC Boshuizen. 2012. ``Estimating Net Transition Probabilities from
Cross-Sectional Data with Application to Risk Factors in Chronic Disease
Modeling.'' \emph{Statistics in Medicine} 31 (6). Wiley Online Library:
533--43.

\end{document}

### 2020-10-26 manuscript/manuscript.Rmd
impliminting quantreg

@@
 \section{introduction}
-Body Mass Idex (BMI) playes an important rule in predicting heart disease risk. BMI     
+
+Body Mass Idex (BMI) playes an important rule in predicting heart disease risk.      
  .
@@
 \section{methode}
-From the figure we see ...
+We used Bayesian hierarchical logistic regression (12) with random intercepts by calendar year to estimate diabetes
+prevalence and incidence as a function
+of age (18 – 84 years in 1-year
+intervals), race/ethnicity (non-Hispanic
+white, non-Hispanic black, Hispanic, or
+other), sex, and BMI (underweight,
+ 18.5 kg/m2; normal weight, 18.5 to
+ 25 kg/m2; overweight, 25 to 30 kg/
+m2; obese, 30 to 35 kg/m2; and very
+From the figure we see
 

### 2020-10-26 manuscript/manuscript.tex
impliminting quantreg

@@
 Body Mass Idex (BMI) playes an important rule in predicting heart
-disease risk. BMI\\
-. (Van de Kassteele et al. 2012) \section{methode} From the figure we
-see \ldots{}
+disease risk.\\
+. (Van de Kassteele et al. 2012) \section{methode} We used Bayesian
+hierarchical logistic regression (12) with random intercepts by calendar
+year to estimate diabetes prevalence and incidence as a function of age
+(18 -- 84 years in 1-year intervals), race/ethnicity (non-Hispanic
+white, non-Hispanic black, Hispanic, or other), sex, and BMI
+(underweight, 18.5 kg/m2; normal weight, 18.5 to 25 kg/m2; overweight,
+25 to 30 kg/ m2; obese, 30 to 35 kg/m2; and very From the figure we see
 

### 2020-10-26 LTR_Code_Example.R

@@ -7,7 +7,6 @@ library("truncnorm")
 library('ggplot2')
 library('ggpubr')
 library("dplyr")
-library("ggpubr")
 library("matlib")
 library('MortalityLaws')
 library("pracma")

### 2020-10-26 exploratory-data-analysis.R

@@ -18,7 +18,7 @@ bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
 
 ## Data clean ready to use
 
-data_male= na.omit(bmi.data[,c(5,6,9,28)])
+data_male= na.omit(bmi.data[,c(5,6,9,28,43)])
 #data_male <- data_male[(data_male$LBXGLU>99.9 & data_male$LBXGLU<500.9 ),]
 Type <- seq(1,length = nrow(data_male))
 temp <- lapply(Type , function(x) ifelse(data_male$LBXGLU[x]<=125.9, "Pre","Diab") )
@@ -55,13 +55,22 @@ data_male=cbind(data_male,Chol)
 ############  Graphing 
 
 library(ggplot2)
-
+#facet on race(RIDRETH1 )
 fig <- ggplot(data_male , aes(x  = Age)) +
     geom_bar(aes( fill = type  ) , position ="fill") +
     scale_fill_viridis_d(end = 1.0) +
     facet_wrap(~ RIDRETH1)
 
 fig
+# Facet on statin use(TCrx)
+fig <- ggplot(data_male , aes(x  = Age)) +
+    geom_bar(aes( fill = type  ) , position ="fill") +
+    scale_fill_viridis_d(end = 1.0) +
+    facet_wrap(~TCRx )
+
+fig
+
+
 
 png(file = here::here("images", "exploratory.png"),
     res = 400, height = 9, width = 16, units = "in")
@@ -75,6 +84,34 @@ fig <- ggplot(data_male[data_male$Type=="Diab",] , aes(x  = Age)) + geom_bar(aes
 
 library(tidyverse)
 print(data_male %>%
-    ggplot(aes(y = BMXBMI, x = type)) +
-    geom_violin())
+          ggplot(aes(y = BMXBMI, x = type)) +
+          geom_violin())
 
+
+########################################################
+bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
+# generate data with non-constant variance
+bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
+dat=data.frame(bmi.data$RIDAGEYR,as.factor(bmi.data$RIDRETH1),as.factor(bmi.data$RIAGENDR),as.factor(bmi.data$TCRx),bmi.data$BMXBMI)
+dat=na.omit(dat)
+colnames(dat) <- c("x","x2","x3","x4","y")
+library(ggplot2)
[…]

### 2020-10-27 exploratory-data-analysis_JRT.R
added JRT changes to script

@@ -1,0 +1,159 @@
+
+# Load packages
+# (Install lpSolve package first)
+library(mgcv)
+library(Matrix)
+library(lpSolve)
+library(here)
+
+#setwd("C:/Users/Muhannad/Desktop/multvariat/Time_series/mdp/Net-transition-probabilities-master")
+# Read data
+#
+
+
+bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
+
+#remove duplicated rows
+bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
+
+## Data clean ready to use
+
+data_male= na.omit(bmi.data[,c(5,6,9,28,43)])
+#data_male <- data_male[(data_male$LBXGLU>99.9 & data_male$LBXGLU<500.9 ),]
+Type <- seq(1,length = nrow(data_male))
+temp <- lapply(Type , function(x) ifelse(data_male$LBXGLU[x]<=125.9, "Pre","Diab") )
+temp <- do.call(rbind,temp)
+Type <- as.factor(temp)
+rm(temp)
+## error here
+data_male <- cbind(data_male,Type)
+
+### Creating factor for age
+Age <-seq(1,length = nrow(data_male))
+f<- function(x) { (x%/%10) }
+temp <- lapply(Age , function(x) f(data_male$RIDAGEYR[x]) )
+temp <- do.call(rbind, temp)
+Age <- as.factor(temp)
+
+data_male <- cbind(data_male,Age)
+
+
+#####
+
+
+###
+
+###  Classifying Cholesterol Level.
+Lip_Rati=data_male[,3]/data_male[,4]
+data_male=cbind(data_male,Lip_Rati)
+Chol=seq(1,length=nrow(data_male))
+temp=lapply(Chol, function(x) ifelse(data_male$BMXBMI[x]<=25,"normal",ifelse(data_male$BMXBMI[x]<=30,"obes","ovrwieght")))
+temp=do.call(rbind,temp)
+Chol=as.factor(temp)
+type=as.factor(temp)
+data_male=cbind(data_male,Chol)
+
+############  Graphing 
+
+library(ggplot2)
+#facet on race(RIDRETH1 )
+fig <- ggplot(data_male , aes(x  = Age)) +
+    geom_bar(aes( fill = type  ) , position ="fill") +
+    scale_fill_viridis_d(end = 1.0) +
+    facet_wrap(~ RIDRETH1)
+
+fig
+# Facet on statin use(TCrx)
[…]

### 2020-11-09 manuscript/manuscript.Rmd
update

--- 2020-10-16 manuscript/manuscript.Rmd
@@
 \section{introduction}
-Body Mass Idex (BMI) playes an important rule in predicting heart disease risk. BMI     
- .
-[@van2012estimating]
-\section{methode}
-From the figure we see ...
+
+Body Mass Index (BMI) plays an important rule in predicting heart disease risk[@katbody]. Our goal is to compare 90th quatile regrission for BMI in Diabtese and prediabtes population.
+
+\section{Quantile regression}
+Quantile regression is an important tool used to regress the dependent variable with high variance over the independent variables.The independent variabeles are Gender, Age, race, and statin use.
+
+For a random variable $X$, the comulative distrubution function (CDF) is $$F(X)=P(X\leq x)$$, and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} $$ where $0<\tau<1$.
+Let the loss function is defined by $$\rho_{\tau}(u)= u(\tau-I(u<0))$$  
+[@koenker2005]. The expected loss function is defined by
+\begin{equation}
+E\rho_{\tau}(X-\hat{x})=
+\end{equation}
+
+Least square method solve $$ \underset{\mu}{\text{min}}\sum_{i=1}^n(y_i-\mu)^2$$
+
+\section{methods}
+
+prevalence and incidence as a function
+of age (18 – 84 years in 1-year
+intervals), race/ethnicity (non-Hispanic
+white, non-Hispanic black, Hispanic, or
+other), sex, and BMI (underweight,
+ 18.5 kg/m2; normal weight, 18.5 to
+ 25 kg/m2; overweight, 25 to 30 kg/
+m2; obese, 30 to 35 kg/m2; and very
+From the figure we see
+
+#Data
+ The data used in this study is National Health and Nutrition Examination Survey data (NHANES)[@NHANES]. The data has
 

### 2020-11-09 manuscript/manuscript.tex
update

--- 2020-10-16 manuscript/manuscript.tex
@@
 
-Body Mass Idex (BMI) playes an important rule in predicting heart
-disease risk. BMI\\
-. (Van de Kassteele et al. 2012) \section{methode} From the figure we
-see \ldots{}
+Body Mass Index (BMI) plays an important rule in predicting heart
+disease risk(Katzmarzyk et al. 2012). Our goal is to compare 90th
+quatile regrission for BMI in Diabtese and prediabtes population.
+
+(Van de Kassteele et al. 2012)
+
+\section{methods}
+
+prevalence and incidence as a function of age (18 -- 84 years in 1-year
+intervals), race/ethnicity (non-Hispanic white, non-Hispanic black,
+Hispanic, or other), sex, and BMI (underweight, 18.5 kg/m2; normal
+weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/ m2; obese, 30 to 35
+kg/m2; and very From the figure we see
+
+\section{Quantile regression}
+
+Quantile regression is an important tool used to regress the dependent
+variable with high variance over the independent variables.
+
+For a random variable \(X\), the comulative distrubution function (CDF)
+is \[F(X)=P(X\leq x)\], and the \(\tau\)th quantile of \(X\) is defined
+by \[ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} \] where \(0<\tau<1\)
+
+\section{Data}\label{data}
+
+The data used in this study is National Health and Nutrition Examination
+Survey data (NHANES)(Disease Control and (CDC) 2018)
 
@@
 \hypertarget{refs}{}
+\hypertarget{ref-NHANES}{}
+Disease Control, Centers for, and Prevention (CDC). 2018. ``National
+Health and Nutrition Examination Survey Data (Nhanes.''
+
+\hypertarget{ref-katbody}{}
+Katzmarzyk, Peter T, Bruce A Reeder, Susan Elliott, Michel R Joffres,
+Punam Pahwa, Kim D Raine, Susan A Kirkland, and Gilles Paradis. 2012.
+``Body Mass Index and Risk of Cardiovascular Disease, Cancer and
+All-Cause Mortality.'' \emph{Canadian Journal of Public Health} 103 (2).
+Springer: 147--51.
+
 \hypertarget{ref-van2012estimating}{}

### 2020-11-09 exploratory-data-analysis.R

@@ -119,4 +119,7 @@ r1 <- rq(  y ~x+x2+x3+x4 , data=dat, tau = c(0.5))
 r2<- rq(  y ~x+x2+x3+x4 , data=dat, tau = c(0.9))
 anova(r1,r2)
 
+
+
+################################################################################################
  

### 2020-11-09 exploratory-data-analysis_JRT.R

@@ -3,71 +3,67 @@
 # (Install lpSolve package first)
 library(mgcv)
 library(Matrix)
-library(lpSolve)
 library(here)
-
-#setwd("C:/Users/Muhannad/Desktop/multvariat/Time_series/mdp/Net-transition-probabilities-master")
-# Read data
-#
+library(dplyr)
+library(tidyverse)
+library(quantreg)
+library(splines)
 
 
 bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
 
-#remove duplicated rows
+#remove duplicated rows and remove na data.
 bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
 
-## Data clean ready to use
+bmi.data= na.omit(bmi.data[,c(5,6,9,28,43,32)]) 
 
-data_male= na.omit(bmi.data[,c(5,6,9,28,43)])
-#data_male <- data_male[(data_male$LBXGLU>99.9 & data_male$LBXGLU<500.9 ),]
-Type <- seq(1,length = nrow(data_male))
-temp <- lapply(Type , function(x) ifelse(data_male$LBXGLU[x]<=125.9, "Pre","Diab") )
+colnames(bmi.data) <- c("Gender","Age","Race","BMI","Statin_status","Glu")
+
+# Classifying population to diabetes and non diabetes
+
+
+Type <- seq(1,length = nrow(bmi.data))
+temp <- lapply(Type , function(x) ifelse(bmi.data$Glu[x]<=125.9, "Pre","Diab") )
 temp <- do.call(rbind,temp)
-Type <- as.factor(temp)
-rm(temp)
-## error here
-data_male <- cbind(data_male,Type)
+Type_glu <- as.factor(temp)
+bmi.data <- cbind(bmi.data,Type_glu)
+
 
 ### Creating factor for age
-Age <-seq(1,length = nrow(data_male))
+Age_10 <-seq(1,length = nrow(bmi.data))
 f<- function(x) { (x%/%10) }
-temp <- lapply(Age , function(x) f(data_male$RIDAGEYR[x]) )
+temp <- lapply(Age_10 , function(x) f(bmi.data$Age[x]) )
 temp <- do.call(rbind, temp)
-Age <- as.factor(temp)
+Age_10 <- as.factor(temp)
 
-data_male <- cbind(data_male,Age)
+bmi.data <- cbind(bmi.data,Age_10)
 
+ 
 
-#####
-
[…]

### 2020-11-09 exploratory-data-analysis_JRT.R
My messages.

@@ -84,30 +84,55 @@ print(bmi.data %>%
 
 dat=data.frame(bmi.data$Age,as.factor(bmi.data$Race),as.factor(bmi.data$Gender),as.factor(bmi.data$Statin_status),bmi.data$BMI,bmi.data$Type_glu)
 colnames(dat) <- c("Age","Race","Gender","Statin_status","BMI","Type_glu")
-ggplot(dat, aes(y=BMI  ,x=Age)) + geom_point()
-ggplot(dat, aes(Age ,BMI )) + geom_point() + geom_smooth(method="lm")
-# quantile regression 
-ggplot(dat, aes(Age ,BMI)) + 
+ggplot(dat, aes(y=BMI  ,x=Age)) +
+    geom_point()
+ggplot(dat, aes(Age ,BMI )) +
     geom_point() + 
-    geom_quantile(quantiles = 0.9)
-#Prediabetes population
-dat_pre=dat %>% filter(dat$Type_glu=="Pre")
-X <- model.matrix( BMI ~ (bs(Age, df = 4) + Race +Gender ) * Statin_status, data = dat_pre)
-qr1 <- rq(  dat_pre$BMI ~ X - 1, data=dat_pre, tau = 0.9)
+    geom_smooth(method="lm")
+# quantile regression 
+ggplot(dat, aes(Age ,BMI, group = Statin_status)) + 
+    geom_point() + 
+    geom_quantile(aes(color = Statin_status), quantiles = 0.8) +
+    geom_quantile(aes(color = Statin_status), quantiles = 0.9) +
+    geom_quantile(aes(color = Statin_status), quantiles = 0.99) +
+    facet_grid(Gender ~ Type_glu)
+
+dat %>%
+    group_by(Race, Gender, Statin_status) %>%
+    summarize(count = n())
+
+
+##
+## Fit model to prediabetes sample
+##
+
+dat_pre <- dat %>% 
+    filter(dat$Type_glu=="Pre")
+
+X      <- model.matrix( BMI ~ (bs(Age, df = 4) + Race + Gender ) * Statin_status, data = dat_pre)
+qr_fit_pre_diabetes <- rq( BMI ~ bs(Age, df = 4) + Race + Gender + Statin_status, data=dat_pre, tau = 0.9)
 
 # qr1 <- rq(  y ~ x+x2+x3+x4 , data=dat, tau = 0.5)
-summary(qr1) #lower bd and upper bd values are confidence intervals calculated using the "rank" method 
-#
[…]

### 2020-11-16 manuscript/manuscript.Rmd
update

--- 2020-10-16 manuscript/manuscript.Rmd
@@
 ---
-title: "BMI-manuscript"
+title: "Body Mass index effects on statin prescribtions"
 output: 
@@
 \section{introduction}
-Body Mass Idex (BMI) playes an important rule in predicting heart disease risk. BMI     
- .
-[@van2012estimating]
-\section{methode}
-From the figure we see ...
+
+Body Mass Index (BMI) plays an important rule in predicting heart disease risk[@katbody].
+Our goal is to compare 90Th quantile regression for BMI in Diabetes and prediabetes population.
+Quantile regression has many succesfyl application in ecology where different factores interect in a complicated way that produce different variation of one factor for different levels of another variabels[@cade2003].
+
+\section{Quantile Regression}
+Quantile regression is an important tool used to regress the dependent variable with high variance over the independent variables.
+QR is developed to study the relationships between variables that have week or no-relationshipes between their means.
+Quantile regression is more robust for an  outlier than ordinaty least squares regression(OLS).
+Moreover, QR is  .
+The independent variables are Gender, Age, race, diabetes status, and statin use.
+
+For a random variable $X$, the cumulative distrubution function (CDF) is $$F(X)=P(X\leq x)$$, and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} $$ where $0<\tau<1$.
+Let the loss function is defined by $$\rho_{\tau}(u)= u(\tau-I_{(u<0)})$$ where $I$ is the indicator function  [@koenker2005].
+The quantile estimator is the value that manimizes the expected loss function
+
+$E\rho_{\tau}(X-\hat{x})=(\tau-1)\int_{-\infty}^{\hat{x}} (x-\hat{x})dF(x)+\tau\int_{\hat{x}}^{-\infty} (x-\hat{x})dF(x).$
+Differentiating with respect to $\hat{x}$, we get
+$$ 0  =(\tau-1)\int_{-\infty}^{\hat{x}} dF(x)+\tau\int_{\hat{x}}^{-\infty} dF(x)
+=F(\hat{x})-\tau.$$ 
+Due to monotnicity of the cumulative distribution function, any solution that satisfies $\{x:F(x)=\tau \}$ is a minimzing for the expected loss function.
+
+Least square method expresses conditional mean of y given x as $\mu(x)=x^T\beta$ and it solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.$$ Quantile regression expresses conditional quantile function $Q_y(\tau|x)=x^T \beta ({\tau)}$ and solve $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.$$This minimization problem can be reformalated to a linear programming problem $$ \underset{\beta\in \mathcal{R}^p}{\text{min}} $$
+
+\section{methods}
+
+prevalence and incidence as a function
+of age (18 – 84 years in 1-year
+intervals), race/ethnicity (non-Hispanic
+white, non-Hispanic black, Hispanic, or
+other), sex, and BMI (underweight,
+ 18.5 kg/m2; normal weight, 18.5 to
+ 25 kg/m2; overweight, 25 to 30 kg/
+m2; obese, 30 to 35 kg/m2; and very
+From the figure we see
+
+#Data
+ The data used in this study is National Health and Nutrition Examination Survey data (NHANES)[@NHANES]. The data has
 
@@
 ```
+
+However,.
+
+```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "exploratory2.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "exploratory2.png"))
+```
+
+So,
+
+```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "quant90.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "quant90.png"))
+```
 # References

### 2020-11-16 manuscript/manuscript.tex
update

@@
 \hypersetup{
-            pdftitle={BMI-manuscript},
+            pdftitle={Body Mass index effects on statin prescribtions},
             pdfborder={0 0 0},
@@
 
-\title{BMI-manuscript}
+\title{Body Mass index effects on statin prescribtions}
 \author{}
@@
 Body Mass Index (BMI) plays an important rule in predicting heart
-disease risk(Katzmarzyk et al. 2012). Our goal is to compare 90th
-quatile regrission for BMI in Diabtese and prediabtes population.
+disease risk(Katzmarzyk et al. 2012). Our goal is to compare 90Th
+quantile regression for BMI in Diabetes and prediabetes population.
+Quantile regression has many succesfyl application in ecology where
+different factores interect in a complicated way that produce different
+variation of one factor for different levels of another variabels(Cade
+and Noon 2003).
 
-(Van de Kassteele et al. 2012)
+\section{Quantile Regression}
+
+Quantile regression is an important tool used to regress the dependent
+variable with high variance over the independent variables. QR is
+developed to study the relationships between variables that have week or
+no-relationshipes between their means. Quantile regression is more
+robust for an outlier than ordinaty least squares regression(OLS).
+Moreover, QR is . The independent variables are Gender, Age, race,
+diabetes status, and statin use.
+
+For a random variable \(X\), the cumulative distrubution function (CDF)
+is \[F(X)=P(X\leq x)\], and the \(\tau\)th quantile of \(X\) is defined
+by \[ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} \] where \(0<\tau<1\).
+Let the loss function is defined by
+\[\rho_{\tau}(u)= u(\tau-I_{(u<0)})\] where \(I\) is the indicator
+function (Koenker 2005). The quantile estimator is the value that
+manimizes the expected loss function
+
+\(E\rho_{\tau}(X-\hat{x})=(\tau-1)\int_{-\infty}^{\hat{x}} (x-\hat{x})dF(x)+\tau\int_{\hat{x}}^{-\infty} (x-\hat{x})dF(x).\)
+Differentiating with respect to \(\hat{x}\), we get
+\[ 0  =(\tau-1)\int_{-\infty}^{\hat{x}} dF(x)+\tau\int_{\hat{x}}^{-\infty} dF(x)
+=F(\hat{x})-\tau.\] Due to monotnicity of the cumulative distribution
+function, any solution that satisfies \(\{x:F(x)=\tau \}\) is a
+minimzing for the expected loss function.
+
+Least square method expresses conditional mean of y given x as
+\(\mu(x)=x^T\beta\) and it solves
+\[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.\]
+Quantile regression expresses conditional quantile function
+\(Q_y(\tau|x)=x^T \beta ({\tau)}\) and solve
+\[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.\]This
+minimization problem can be reformalated to a linear programming problem
+\[ \underset{\beta\in \mathcal{R}^p}{\text{min}} \]
 
@@
 
-\section{Quantile regression}
-
-Quantile regression is an important tool used to regress the dependent
-variable with high variance over the independent variables.
-
-For a random variable \(X\), the comulative distrubution function (CDF)
-is \[F(X)=P(X\leq x)\], and the \(\tau\)th quantile of \(X\) is defined
-by \[ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} \] where \(0<\tau<1\)
-
 \section{Data}\label{data}
@@
 The data used in this study is National Health and Nutrition Examination
-Survey data (NHANES)(Disease Control and (CDC) 2018)
+Survey data (NHANES)(Disease Control and (CDC) 2018). The data has
 
@@
 
+However,.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/exploratory2}
+
+}
+
+\caption{A better figure caption}\label{fig:unnamed-chunk-2}
+\end{figure}
+
+So,
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/quant90}
+
+}
+
+\caption{A better figure caption}\label{fig:unnamed-chunk-3}
+\end{figure}
+
 \section*{References}\label{references}
@@
 \hypertarget{refs}{}
+\hypertarget{ref-cade2003}{}
+Cade, Brian S, and Barry R Noon. 2003. ``A Gentle Introduction to
+Quantile Regression for Ecologists.'' \emph{Frontiers in Ecology and the
+Environment} 1 (8). Wiley Online Library: 412--20.
+
 \hypertarget{ref-NHANES}{}
@@
 
-\hypertarget{ref-van2012estimating}{}
-Van de Kassteele, Jan, RT Hoogenveen, PM Engelfriet, PHM Van Baal, and
-HC Boshuizen. 2012. ``Estimating Net Transition Probabilities from
-Cross-Sectional Data with Application to Risk Factors in Chronic Disease
-Modeling.'' \emph{Statistics in Medicine} 31 (6). Wiley Online Library:
-533--43.
+\hypertarget{ref-koenker2005}{}
+Koenker, Roger. 2005. ``Quantile Regression, Volume 38 of.''
+\emph{Econometric Society Monographs}.
 

### 2020-11-16 QR_LR.R

@@ -14,10 +14,11 @@ bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
 
 #remove duplicated rows and remove na data.
 bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
+bmi.data$LR=bmi.data$LBXTC/bmi.data$LBDHDD
+bmi.data= na.omit(bmi.data[,c(5,6,9,28,43,32,48)]) 
 
-bmi.data= na.omit(bmi.data[,c(5,6,9,28,43,32)]) 
-
-colnames(bmi.data) <- c("Gender","Age","Race","BMI","Statin_status","Glu")
+colnames(bmi.data) <- c("Gender","Age","Race","BMI","Statin_status","Glu","LR") 
+bmi.data= bmi.data[,c(1,2,3,5,6,7)]
 
 bmi.data$Gender=recode(bmi.data$Gender, "1" = "Male", "2" = "Femal" )
 # RIDRETH1 (race, 1=mexican, 2=otherHispanic, 3= Non-Hispanic White,4=Non-Hispanic Black ,5=Other Race - Including Multi-Racial
@@ -42,10 +43,10 @@ Age_10 <- as.factor(temp)
 
 bmi.data <- cbind(bmi.data,Age_10)
 
- 
+
 
 ###  Classifying BMI Level.
- 
+
 BMI_bin=seq(1,length=nrow(bmi.data))
 temp=lapply(BMI_bin, function(x) ifelse(bmi.data$BMI[x]<=25,"normal",ifelse(bmi.data$BMI[x]<=30,"obes","ovrwieght")))
 temp=do.call(rbind,temp)
@@ -86,30 +87,30 @@ print(bmi.data %>%
 
 ########################################################
 
-dat=data.frame(bmi.data$Age,as.factor(bmi.data$Race),as.factor(bmi.data$Gender),as.factor(bmi.data$Statin_status),bmi.data$BMI,bmi.data$Type_glu)
-colnames(dat) <- c("Age","Race","Gender","Statin_status","BMI","Type_glu")
-ggplot(dat, aes(y=BMI  ,x=Age)) +
+dat=data.frame(bmi.data$Age,as.factor(bmi.data$Race),as.factor(bmi.data$Gender),as.factor(bmi.data$Statin_status),bmi.data$LR,bmi.data$Type_glu)
[…]

### 2020-12-28 manuscript/manuscript.Rmd
update

--- 2020-10-26 manuscript/manuscript.Rmd
@@
 ---
-title: "BMI-manuscript"
+title: " Quantile Regression Analysis for Statin effects on glucose level"
 output: 
@@
 link_citations: true
+geometry: margin=1in
+fontsize: 12pt
+fig_caption: yes
+indent: true
+header-includes:
+    - \usepackage{setspace}\doublespacing
+    - \usepackage{float}
 ---
@@
 
-Body Mass Idex (BMI) playes an important rule in predicting heart disease risk.      
- .
-[@van2012estimating]
-\section{methode}
-We used Bayesian hierarchical logistic regression (12) with random intercepts by calendar year to estimate diabetes
-prevalence and incidence as a function
-of age (18 – 84 years in 1-year
-intervals), race/ethnicity (non-Hispanic
-white, non-Hispanic black, Hispanic, or
-other), sex, and BMI (underweight,
- 18.5 kg/m2; normal weight, 18.5 to
- 25 kg/m2; overweight, 25 to 30 kg/
-m2; obese, 30 to 35 kg/m2; and very
-From the figure we see
+---
+# here's a comment
+# ```{r}
+# Body Mass Index (BMI) plays an important rule in predicting heart disease #risk[@katbody].
+Our goal is to compare 90Th quantile regression for BMI in Diabetes and #prediabetes population.
+Quantile regression has many succesfyl application in ecology #where different factores interect in a complicated way that produce different variation #of one factor for different levels of another variabels[@cade2003].
+# ```
+---
+Approximately, 18 million deaths annually per year are caused by cardiovascular diseases(CVD) and similar to this number of nonfatal cardiovascular events [@hay2017gbd].
+For 2011, annual costs for CVD and stroke were $\$320.1$ billion, which is more than cancer cost.
+This cost include \$195.6  billion in direct costs (healthcare costs), and cost of future productivity loss is  \$124.5 [@mozaffarian2015executive].
+Abnormal lipid ratio  is a risk  factor for CVD [@yusuf2004effect].
+Lowering low-density lipoprotein (LDL) using statin reduces risk of cardiovascular diseases even with population with no CVD  [@yusuf2016].
+It is known that diabetes is a risk factor for CVD, however, it is shown that elevated  glucose, prediabetes,is also a risk factor for CVD [@balkau2004prediction].
 
-```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+Statin use associated with high risk of a new onset diabetes in normoglcemic (HR 1.19,95% CI , 1.05 to 1.35) and in prediabetes (HR 1.24 95% CI , 1.11 to 1.38).
+On the other hand, overall mortality risks went down  in both normoglycemic (HR 0.70;
+95 % CI, 0.66 to 0.80) and IFG patients (HR
+0.77, 95 % CI, 0.64 to 0.91) with statin use [@castro2016].
+For population with one or more risk factor for diabetes, statin use associate with 39% reduction in the primary end points (the hazard ratio (HR) 0.61), and a 28% (HR 1.28)increase in diabetes[@ridker2012].Pandya at el.[pandya2015] suggested the dis-utility associated with taking a pill daily, statin price, and the risk of statin-induced diabetes negatively impacted the cost effectiveness of statin use recommendation.
+
+\section{Quantile Regression}
+Quantile regression is an important tool used to regress the dependent variable with high variance over the independent variables.
+QR is developed to study the relationships between variables that have week or no-relationships between their means.
+One of the advantage of using QR over OLS is robust for outliers.
+
+For a random variable $X$, the cumulative distribution function (CDF) is $$F(X)=P(X\leq x)$$, and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} $$ where $0<\tau<1$.
+Let the loss function is defined by $$\rho_{\tau}(u)= u(\tau-I_{(u<0)})$$ where $I$ is the indicator function  [@koenker2005].
+The quantile estimator is the value that minimizes the expected loss function
+
+$E\rho_{\tau}(X-\hat{x})=(\tau-1)\int_{-\infty}^{\hat{x}} (x-\hat{x})dF(x)+\tau\int_{\hat{x}}^{-\infty} (x-\hat{x})dF(x).$
+Differentiating with respect to $\hat{x}$, we get
+$$ 0  =(\tau-1)\int_{-\infty}^{\hat{x}} dF(x)+\tau\int_{\hat{x}}^{-\infty} dF(x)
+=F(\hat{x})-\tau.$$ 
+Due to monotnicity of the cumulative distribution function, any solution that satisfies $\{x:F(x)=\tau \}$ is a minimizing for the expected loss function.
+
+Least square method expresses conditional mean of y given x as $\mu(x)=x^T\beta$ and it solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.$$ Quantile regression expresses conditional quantile function $Q_y(\tau|x)=x^T \beta ({\tau)}$ and solve $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.$$This minimization problem can be reformulated to a linear programming problem $$ \underset{\beta\in \mathcal{R}^p}{\text{min}} $$
+
+\section{Methods}
+A multivariate quantile regression model is used to assess the characteristics of the   association variability in different quantiles of the conditional distribution of the glucose levels.
+Moreover, the independent variables are Gender, Age, race, diabetes status, and statin use.
+
+#Data
+ The data used in this study is National Health and Nutrition Examination Survey data (NHANES)[@NHANES].
+The survey examines a nationally representative sample of U.S.
+population.It focuses on  variety of health and nutrition measurements.
+In this study, we cumulated 6 cycles of NHANES data (2007–2018).
+There are 12,406 records.
+The dependent variables in our model are gender, race, age, BMI, total cholesterol, and statin use (yes or no).
+All type of statin are included.
+The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.
+BMI are classified into different categories according to underweight, 18.5 kg/m2; normal weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/m2; obese, 30 to 35 kg/m2; and very obese more than 35 kg/m2.
+
+| Syntax      | Male  | Femal     |
+| :---        |    :----:   |          ---: |
+| count |  5990      | 6416   |
+| Mean of Age | 49.9       | 49.73   |
+| glucose        |  112.618     |  106.47   |
+| TC         | Title       | Here's this   |
+| Statin use (ratio) | 0.198       | 0.181   |
+
+```{r data, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 ```
-# References
+
+to cite figure #See Figure \@ref(fig:data)
+However,.
+
+```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "exploratory2.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "exploratory2.png"))
+```
+
+So,
+
+```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "quant90.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "quant90.png"))
+```
+\section{Results}
+The resulting estimate of effects on conditional mean of glucose level may not reflect the size and nature of theses effects on lower or upper quantile.
+For example, in the Figure \@ref(fig:resu1), the conditional mean shows the conditional mean effects of gender on glucose level is about 7.
+However, the disparity of the gender effects on lower tails is much smaller which is about 3 but the disparity is higher for the upper tail of the distribution somewhat larger than 10 mg/dL.
+
+From the OLS it is obvious statin users have on average  higher glucose levels if compared to non-statin users which is around 10 mg/dL.
+The disparity in glucose level for statin users vs non-statin users is negligible in the left tail, however, statin uses seems to be associated with a rather large effects on glucose levels somewhat larger than 55 mg/dL for the right quantile.
+
+```{r resu1, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "newfig.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "newfig.png"))
+```
+ So,
+ therefore
+```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "newfig2.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "newfig2.png"))
+``` 
+So,
+ Age effect modeled as a quadratic factor.
+The age effect  is linear in general, see Figure \@ref(fig:resu3).
+The slope for the  left quantile is lower than the slope of the right quantile.
+This can be interpreted as age effect tends to increase over the entire range of conditional distribution of glucose in faster rate for the higher quantile than in the left quantile.In other word, diabetes population have higher rate of change with respect to age if compared to non diabetes population.
+It was found that there is  a significantly correlation between glucose and age[@tsaousis2014].
+
+The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014],[@chang2011].
+They found that there is a positive correlation between the two groups.
+However, we found that
+
+```{r resu3, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic age effect on glucose leveles for four different quantiles of the conditional glucose distribution.
+The ", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "newfig3.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "newfig3.png"))
+```
+Quadratic effect of total cholesterol on the conditional distribution of glucose is convex.
+At the lower tail, decreasing glucose level by somewhat around 1.4 up to around 180 Cholesterol level.
+Then, started to increase glucose levels after TC beyond 180.
+At higher quantile, the reverse in the cholesterol effects is shifted to higher cholesterol levels which around 200, Figure \@ref(fig:resu4).
+The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014],[@chang2011].
+They found that there is a positive correlation between the two groups on average.
+
+```{r resu4, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic cholestrol effect on glucose leveles for four different quantiles of the conditional glucose distribution.
+The ", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "newfig4.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "newfig4.png"))
+```
+
+<!-- ```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE} -->
+<!-- library(knitr) -->
+<!--  kable(dat[,2:3],caption="A nit table") -->
+<!-- ``` -->
+
+\section{Conclusion}
+ Multivariate quantile regression is used to study effects of different variables on fasting glucose level.
+Our study showed that people who have TC levels around 190 mg/dL have lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile the optimal cholesterol level is around 200 mg/dL.
+Moreover, Statin effects on glucose at lower quantile is very small if compared to upper quantile.
+\newpage
+\section{References}

### 2020-12-28 Q_reg_plot.R

@@ -1,0 +1,180 @@
+# Plot of quantile regression for glucose reressed on Gender, Age,Race,BMI,Statin_status,BMI
+require(quantreg)
+library(tidyverse)
+bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
+
+#remove duplicated rows and remove na data.
+bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
+#both DID070 and DIQ 070 represent an answer for question Are you useing medication for glucose
+#yes 1 no 2
+bmi.data$diab_drug=coalesce(bmi.data$DIQ070,bmi.data$DID070)
+ 
+bmi.data=data.frame(bmi.data$RIAGENDR,bmi.data$RIDAGEYR, bmi.data$RIDRETH1,bmi.data$BMXBMI,
+                    bmi.data$LBXTC,bmi.data$TCRx,bmi.data$LBXGLU,bmi.data$BMXWAIST)
+#bmi.data= na.omit(bmi.data[,c(5,6,9,29,33,43,32)])
+#bmi.data=bmi.data[bmi.data$bmi.data.diab_drug==2,]
+#bmi.data=na.omit(bmi.data[,c(1:7)])
+colnames(bmi.data) <- c("Gender","Age","Race","BMI","Total_chol" ,"Statin_status","Glu","Waist_cir")
+bmi.data=na.omit(bmi.data)
+bmi.data=bmi.data%>%filter(bmi.data$Age>19)
+bmi.data$Gender=recode(bmi.data$Gender, "1" = "Male", "2" = "Female" )
+# RIDRETH1 (race, 1=mexican, 2=otherHispanic, 3= Non-Hispanic White,4=Non-Hispanic Black ,5=Other Race - Including Multi-Racial
+
+bmi.data$Race=recode(bmi.data$Race, "1" = "Mexican", "2" = "Other_Hispanic","3"="White","4"="Black","5"="Other" )
+# Classifying population to diabetes and non diabetes
+
+bmi.data <- cbind(bmi.data, Age2 = bmi.data$Age^2)
+bmi.data <- cbind(bmi.data, BMI2 = bmi.data$BMI^2)
+bmi.data <- cbind(bmi.data, Total_col2 = bmi.data$Total_chol^2)
[…]

### 2020-12-30 Q_reg_plot2.R
Splines

@@ -1,0 +1,209 @@
+# Plot of quantile regression for glucose reressed on Gender, Age,Race,BMI,Statin_status,BMI
+require(quantreg)
+library(tidyverse)
+library(splines)
+bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
+
+#remove duplicated rows and remove na data.
+bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
+ 
+bmi.data=data.frame(bmi.data$RIAGENDR,bmi.data$RIDAGEYR, bmi.data$RIDRETH1,bmi.data$BMXBMI,
+                    bmi.data$LBXTC,bmi.data$TCRx,bmi.data$LBXGLU,bmi.data$BMXWAIST)
+#bmi.data= na.omit(bmi.data[,c(5,6,9,29,33,43,32)])
+#bmi.data=bmi.data[bmi.data$bmi.data.diab_drug==2,]
+#bmi.data=na.omit(bmi.data[,c(1:7)])
+colnames(bmi.data) <- c("Gender","Age","Race","BMI","Total_chol" ,"Statin_status","Glu","Waist_cir")
+bmi.data=na.omit(bmi.data)
+bmi.data=bmi.data%>%filter(bmi.data$Age>19)
+bmi.data$Gender=recode(bmi.data$Gender, "1" = "Male", "2" = "Female" )
+# RIDRETH1 (race, 1=mexican, 2=otherHispanic, 3= Non-Hispanic White,4=Non-Hispanic Black ,5=Other Race - Including Multi-Racial
+
+bmi.data$Race=recode(bmi.data$Race, "1" = "Mexican", "2" = "Other_Hispanic","3"="White","4"="Black","5"="Other" )
+# Classifying population to diabetes and non diabetes
+
+ 
+#formula <- Glu ~Gender+Age+Race+BMI+Statin_status+Age2+BMI2+Total_chol+Total_col2+Waist_cir 
+formula <- Glu ~Gender+Race+BMI+Statin_status+bs(Age,intercept=FALSE,df=5)+bs(Total_chol,intercept=FALSE,df=5)+Waist_cir      
+fit3.ols <- summary(lm(formula,data =bmi.data))$coefficients
+#attach(bmi.data)
+p <- nrow(fit3.ols)
+taus <- c(1:4/100, 1:19/20)
[…]

### 2021-01-11 manuscript/manuscript.Rmd
update

@@
 
----
-# here's a comment
-# ```{r}
-# Body Mass Index (BMI) plays an important rule in predicting heart disease #risk[@katbody].
+<!-- # here's a comment -->
+<!-- # ```{r} -->
+<!-- # Body Mass Index (BMI) plays an important rule in predicting heart disease #risk[@katbody].
 Our goal is to compare 90Th quantile regression for BMI in Diabetes and #prediabetes population.
 Quantile regression has many succesfyl application in ecology #where different factores interect in a complicated way that produce different variation #of one factor for different levels of another variabels[@cade2003].
-# ```
----
+-->
+<!-- # ``` -->
+
 Approximately, 18 million deaths annually per year are caused by cardiovascular diseases(CVD) and similar to this number of nonfatal cardiovascular events [@hay2017gbd].
@@
 For population with one or more risk factor for diabetes, statin use associate with 39% reduction in the primary end points (the hazard ratio (HR) 0.61), and a 28% (HR 1.28)increase in diabetes[@ridker2012].Pandya at el.[pandya2015] suggested the dis-utility associated with taking a pill daily, statin price, and the risk of statin-induced diabetes negatively impacted the cost effectiveness of statin use recommendation.
+
+Several studies esimated the association of different factors like waist circumference, Cholestrol with the conditional mean of glucose using OLS or logistic regression model.
+The drawback in these study is not considering the dispersion of the association of covariates with conditional distribution of the dependent variables, glucose levele.
 
@@
 
+\subsection{Quantile Regression }
+
 \section{Methods}
 A multivariate quantile regression model is used to assess the characteristics of the   association variability in different quantiles of the conditional distribution of the glucose levels.
-Moreover, the independent variables are Gender, Age, race, diabetes status, and statin use.
 
-#Data
+ The dependent variables in our model are gender, race, age, BMI, total cholesterol, Choesterol drug uses (yes or no), and waist circumference.
+All type of cholesterol drug are included including  statins.
+The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.
+
+\section{Numerical Example}
+\subsection{Data}
  The data used in this study is National Health and Nutrition Examination Survey data (NHANES)[@NHANES].
@@
 In this study, we cumulated 6 cycles of NHANES data (2007–2018).
-There are 12,406 records.
-The dependent variables in our model are gender, race, age, BMI, total cholesterol, and statin use (yes or no).
-All type of statin are included.
-The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.
+There are  around 12,000 records.
+We selected  population age between 20 and 80.
 BMI are classified into different categories according to underweight, 18.5 kg/m2; normal weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/m2; obese, 30 to 35 kg/m2; and very obese more than 35 kg/m2.
@@
  So,
+
+```{r resu12, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "newfig11.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "newfig11.png"))
+```
  therefore
@@
 So,
+```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "newfig22.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "newfig22.png"))
+``` 
  Age effect modeled as a quadratic factor.
@@
 ```
+
+So,
+
+```{r resu33, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic age effect on glucose leveles for four different quantiles of the conditional glucose distribution.
+The ", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "newfig33.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "newfig33.png"))
+```
+
 Quadratic effect of total cholesterol on the conditional distribution of glucose is convex.
@@
 
+So,
+```{r resu44, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic cholestrol effect on glucose leveles for four different quantiles of the conditional glucose distribution.
+The ", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "newfig44.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "newfig44.png"))
+```
 <!-- ```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE} -->
@@
 <!-- ``` -->
+
+So,
 

### 2021-01-11 Q_reg_plot2.R

@@ -2,6 +2,7 @@
 require(quantreg)
 library(tidyverse)
 library(splines)
+
 bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
 
 #remove duplicated rows and remove na data.
@@ -23,7 +24,7 @@ bmi.data$Race=recode(bmi.data$Race, "1" = "Mexican", "2" = "Other_Hispanic","3"=
 
  
 #formula <- Glu ~Gender+Age+Race+BMI+Statin_status+Age2+BMI2+Total_chol+Total_col2+Waist_cir 
-formula <- Glu ~Gender+Race+BMI+Statin_status+bs(Age,intercept=FALSE,df=5)+bs(Total_chol,intercept=FALSE,df=5)+Waist_cir      
+formula <- Glu ~Gender+Race+BMI+Statin_status+bs(Age,intercept=FALSE,df=5)+bs(Total_chol,intercept=FALSE,df=5)+bs(Waist_cir,intercept=FALSE,df=5)      
 fit3.ols <- summary(lm(formula,data =bmi.data))$coefficients
 #attach(bmi.data)
 p <- nrow(fit3.ols)
@@ -75,11 +76,11 @@ png(file = here::here("images", "newfig.png"),
     res = 400, height = 9, width = 16, units = "in")
 p <- dim(fit3)[1]
 #blab <- c("Intercept","Male ","Age","RaceMexican", "RaceOther", "RaceOther_Hispanic ", "White ", "BMI", " Statin_status","Age Suqared","BMI^2","Total cholesterol","Total cholestrol^2","Waist Circumference")
-blab <- c("Intercept","Male ","Age","RaceMexican", "RaceOther", "RaceOther_Hispanic ", "White ", "BMI", " Statin_status","Age1","BMI^2","Total cholesterol","Total cholestrol^2","Waist Circumference",
-          "Age1","Age2","Age3","Age4","Age5","TC1","TC2","TC3","TC4","TC5","Wasist")
+blab <- c("Intercept","Male ","Age","RaceMexican", "RaceOther", "RaceOther_Hispanic ", "White ", "BMI", " Statin_status","Age1","BMI2","Total cholesterol","Total cholestrol2","Waist Circumference",
+          "Age1","Age2","Age3","Age4","Age5","TC1","TC2","TC3","TC4","TC5","Wasist1","Wasist2","Wasist3","Wasist4","Wasist5")
 
-par(mfrow=c(5,4))
-for(i in c(1:19)){
[…]

### 2021-01-15 manuscript/manuscript.tex
updating files

@@
-\documentclass[]{article}
+\documentclass[12pt,]{article}
 \usepackage{lmodern}
@@
 \hypersetup{
-            pdftitle={Body Mass index effects on statin prescribtions},
+            pdftitle={Quantile Regression Analysis for Statin effects on glucose level},
             pdfborder={0 0 0},
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 
-\title{Body Mass index effects on statin prescribtions}
+\usepackage{setspace}\doublespacing
+\usepackage{float}
+
+\title{Quantile Regression Analysis for Statin effects on glucose level}
 \author{}
@@
 
-Body Mass Index (BMI) plays an important rule in predicting heart
-disease risk(Katzmarzyk et al. 2012). Our goal is to compare 90Th
-quantile regression for BMI in Diabetes and prediabetes population.
-Quantile regression has many succesfyl application in ecology where
-different factores interect in a complicated way that produce different
-variation of one factor for different levels of another variabels(Cade
-and Noon 2003).
+Approximately, 18 million deaths annually per year are caused by
+cardiovascular diseases(CVD) and similar to this number of nonfatal
+cardiovascular events (Hay et al. 2017). For 2011, annual costs for CVD
+and stroke were \(\$320.1\) billion, which is more than cancer cost.
+This cost include \$195.6 billion in direct costs (healthcare costs),
+and cost of future productivity loss is \$124.5 (Mozaffarian et al.
+2015). Abnormal lipid ratio is a risk factor for CVD (Yusuf et al.
+2004). Lowering low-density lipoprotein (LDL) using statin reduces risk
+of cardiovascular diseases even with population with no CVD (Yusuf et
+al. 2016). It is known that diabetes is a risk factor for CVD, however,
+it is shown that elevated glucose, prediabetes,is also a risk factor for
+CVD (Balkau et al. 2004).
+
+Statin use associated with high risk of a new onset diabetes in
+normoglcemic (HR 1.19,95\% CI , 1.05 to 1.35) and in prediabetes (HR
+1.24 95\% CI , 1.11 to 1.38). On the other hand, overall mortality risks
+went down in both normoglycemic (HR 0.70; 95 \% CI, 0.66 to 0.80) and
+IFG patients (HR 0.77, 95 \% CI, 0.64 to 0.91) with statin use (Castro
+et al. 2016). For population with one or more risk factor for diabetes,
+statin use associate with 39\% reduction in the primary end points (the
+hazard ratio (HR) 0.61), and a 28\% (HR 1.28)increase in diabetes(Ridker
+et al. 2012).Pandya at el.{[}pandya2015{]} suggested the dis-utility
+associated with taking a pill daily, statin price, and the risk of
+statin-induced diabetes negatively impacted the cost effectiveness of
+statin use recommendation.
+
+Several studies esimated the association of different factors like waist
+circumference, Cholestrol with the conditional mean of glucose using OLS
+or logistic regression model. The drawback in these study is not
+considering the dispersion of the association of covariates with
+conditional distribution of the dependent variables, glucose levele.
 
@@
 developed to study the relationships between variables that have week or
-no-relationshipes between their means. Quantile regression is more
-robust for an outlier than ordinaty least squares regression(OLS).
-Moreover, QR is . The independent variables are Gender, Age, race,
-diabetes status, and statin use.
+no-relationships between their means. One of the advantage of using QR
+over OLS is robust for outliers.
 
-For a random variable \(X\), the cumulative distrubution function (CDF)
+For a random variable \(X\), the cumulative distribution function (CDF)
 is \[F(X)=P(X\leq x)\], and the \(\tau\)th quantile of \(X\) is defined
@@
 function (Koenker 2005). The quantile estimator is the value that
-manimizes the expected loss function
+minimizes the expected loss function
 
@@
 function, any solution that satisfies \(\{x:F(x)=\tau \}\) is a
-minimzing for the expected loss function.
+minimizing for the expected loss function.
 
@@
 \[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.\]This
-minimization problem can be reformalated to a linear programming problem
+minimization problem can be reformulated to a linear programming problem
 \[ \underset{\beta\in \mathcal{R}^p}{\text{min}} \]
 
-\section{methods}
+\subsection{Quantile Regression Technique }
 
-prevalence and incidence as a function of age (18 -- 84 years in 1-year
-intervals), race/ethnicity (non-Hispanic white, non-Hispanic black,
-Hispanic, or other), sex, and BMI (underweight, 18.5 kg/m2; normal
-weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/ m2; obese, 30 to 35
-kg/m2; and very From the figure we see
+\section{Methods}
 
-\section{Data}\label{data}
+A multivariate quantile regression model is used to assess the
+characteristics of the association variability in different quantiles of
+the conditional distribution of the glucose levels.
+
+The dependent variables in our model are gender, race, age, BMI, total
+cholesterol, Choesterol drug uses (yes or no), and waist circumference.
+All type of cholesterol drug are included including statins. The
+included races are non-Hispanic white, non-Hispanic black, Hispanic, or
+other.
+
+\section{Numerical Example}\subsection{Data}
 
 The data used in this study is National Health and Nutrition Examination
-Survey data (NHANES)(Disease Control and (CDC) 2018). The data has
+Survey data (NHANES)(Disease Control and (CDC) 2018). The survey
+examines a nationally representative sample of U.S. population.It
+focuses on variety of health and nutrition measurements. In this study,
+we cumulated 6 cycles of NHANES data (2007--2018). There are around
+12,000 records. We selected population age between 20 and 80. BMI are
+classified into different categories according to underweight, 18.5
+kg/m2; normal weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/m2;
+obese, 30 to 35 kg/m2; and very obese more than 35 kg/m2.
+
+\begin{longtable}[]{@{}lcr@{}}
+\toprule
+Syntax & Male & Femal\tabularnewline
+\midrule
+\endhead
+count & 5990 & 6416\tabularnewline
+Mean of Age & 49.9 & 49.73\tabularnewline
+glucose & 112.618 & 106.47\tabularnewline
+TC & Title & Here's this\tabularnewline
+Statin use (ratio) & 0.198 & 0.181\tabularnewline
+\bottomrule
+\end{longtable}
 
@@
 
-\caption{A better figure caption}\label{fig:unnamed-chunk-1}
+\caption{A better figure caption}\label{fig:data}
 \end{figure}
 
-However,.
+to cite figure \#See Figure \ref{fig:data} However,.
 
@@
 
-\caption{A better figure caption}\label{fig:unnamed-chunk-2}
+\caption{A better figure caption}\label{fig:unnamed-chunk-1}
 \end{figure}
@@
 
+\caption{A better figure caption}\label{fig:unnamed-chunk-2}
+\end{figure}\section{Results}
+
+The resulting estimate of effects on conditional mean of glucose level
+may not reflect the size and nature of theses effects on lower or upper
+quantile. For example, in the Figure \ref{fig:resu1}, the conditional
+mean shows the conditional mean effects of gender on glucose level is
+about 7. However, the disparity of the gender effects on lower tails is
+much smaller which is about 3 but the disparity is higher for the upper
+tail of the distribution somewhat larger than 10 mg/dL.
+
+From the OLS it is obvious statin users have on average higher glucose
+levels if compared to non-statin users which is around 10 mg/dL. The
+disparity in glucose level for statin users vs non-statin users is
+negligible in the left tail, however, statin uses seems to be associated
+with a rather large effects on glucose levels somewhat larger than 55
+mg/dL for the right quantile.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/newfig}
+
+}
+
+\caption{A better figure caption}\label{fig:resu1}
+\end{figure}
+
+So,
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/newfig11}
+
+}
+
+\caption{A better figure caption}\label{fig:resu12}
+\end{figure}
+
+therefore
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/newfig2}
+
+}
+
 \caption{A better figure caption}\label{fig:unnamed-chunk-3}
@@
 
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
+So,
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/newfig22}
+
+}
+
+\caption{A better figure caption}\label{fig:unnamed-chunk-4}
+\end{figure}
+
+Age effect modeled as a quadratic factor. The age effect is linear in
+general, see Figure \ref{fig:resu3}. The slope for the left quantile is
+lower than the slope of the right quantile. This can be interpreted as
+age effect tends to increase over the entire range of conditional
+distribution of glucose in faster rate for the higher quantile than in
+the left quantile.In other word, diabetes population have higher rate of
+change with respect to age if compared to non diabetes population. It
+was found that there is a significantly correlation between glucose and
+age(Tsaousis 2014).
+
+The relation between total cholesterol and fasting glucose has been
+studied in (Tsaousis 2014),(Chang et al. 2011). They found that there is
+a positive correlation between the two groups. However, we found that
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/newfig3}
+
+}
+
+\caption{Illustration of the quadratic age effect on glucose leveles for four different quantiles of the conditional glucose distribution.  The }\label{fig:resu3}
+\end{figure}
+
+So,
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/newfig33}
+
+}
+
+\caption{Illustration of the quadratic age effect on glucose leveles for four different quantiles of the conditional glucose distribution.  The }\label{fig:resu33}
+\end{figure}
+
+Quadratic effect of total cholesterol on the conditional distribution of
+glucose is convex. At the lower tail, decreasing glucose level by
+somewhat around 1.4 up to around 180 Cholesterol level. Then, started to
+increase glucose levels after TC beyond 180. At higher quantile, the
+reverse in the cholesterol effects is shifted to higher cholesterol
+levels which around 200, Figure \ref{fig:resu4}. The relation between
+total cholesterol and fasting glucose has been studied in (Tsaousis
+2014),(Chang et al. 2011). They found that there is a positive
+correlation between the two groups on average.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/newfig4}
+
+}
+
+\caption{Illustration of the quadratic cholestrol effect on glucose leveles for four different quantiles of the conditional glucose distribution.  The }\label{fig:resu4}
+\end{figure}
+
+So,
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/newfig44}
+
+}
+
+\caption{Illustration of the quadratic cholestrol effect on glucose leveles for four different quantiles of the conditional glucose distribution.  The }\label{fig:resu44}
+\end{figure}
+
+So,
+
+\section{Conclusion}
+
+Multivariate quantile regression is used to study effects of different
+variables on fasting glucose level. Our study showed that people who
+have TC levels around 190 mg/dL have lowest fasting glucose levels for
+the lowest quantile, for the second quantile optimal cholesterol level
+is around 220mg/dL, and for the upper quantile the optimal cholesterol
+level is around 200 mg/dL. Moreover, Statin effects on glucose at lower
+quantile is very small if compared to upper quantile. \newpage
+\section{References}
 
 \hypertarget{refs}{}
-\hypertarget{ref-cade2003}{}
-Cade, Brian S, and Barry R Noon. 2003. ``A Gentle Introduction to
-Quantile Regression for Ecologists.'' \emph{Frontiers in Ecology and the
-Environment} 1 (8). Wiley Online Library: 412--20.
+\hypertarget{ref-balkau2004prediction}{}
+Balkau, Beverley, Gang Hu, Qing Qiao, Jaakko Tuomilehto, Knut
+Borch-Johnsen, K Pyorala, DECODE Study Group, European Diabetes
+Epidemiology Group, and others. 2004. ``Prediction of the Risk of
+Cardiovascular Mortality Using a Score That Includes Glucose as a Risk
+Factor. the Decode Study.'' \emph{Diabetologia} 47 (12). Springer
+Science \& Business Media: 2118.
+
+\hypertarget{ref-castro2016}{}
+Castro, M Regina, Gyorgy Simon, Stephen S Cha, Barbara P Yawn, L Joseph
+Melton, and Pedro J Caraballo. 2016. ``Statin Use, Diabetes Incidence
+and Overall Mortality in Normoglycemic and Impaired Fasting Glucose
+Patients.'' \emph{Journal of General Internal Medicine} 31 (5).
+Springer: 502--8.
+
+\hypertarget{ref-chang2011}{}
+Chang, Jin-Biou, Nain-Feng Chu, Jhu-Ting Syu, An-Tsz Hsieh, and Yi-Ren
+Hung. 2011. ``Advanced Glycation End Products (Ages) in Relation to
+Atherosclerotic Lipid Profiles in Middle-Aged and Elderly Diabetic
+Patients.'' \emph{Lipids in Health and Disease} 10 (1). Springer: 228.
 
@@
 
-\hypertarget{ref-katbody}{}
-Katzmarzyk, Peter T, Bruce A Reeder, Susan Elliott, Michel R Joffres,
-Punam Pahwa, Kim D Raine, Susan A Kirkland, and Gilles Paradis. 2012.
-``Body Mass Index and Risk of Cardiovascular Disease, Cancer and
-All-Cause Mortality.'' \emph{Canadian Journal of Public Health} 103 (2).
-Springer: 147--51.
+\hypertarget{ref-hay2017gbd}{}
+Hay, Simon I, Sudha P Jayaraman, Alejandra G Contreras Manzano, Anoushka
+Millear, Laura Kemmer, Brent Bell, Juan Jesus Carrero, et al. 2017.
+``GBD 2015 Risk Factors Collaborators. Global, Regional, and National
+Comparative Risk Assessment of 79 Behavioural, Environmental and
+Occupational, and Metabolic Risks or Clusters of Risks, 1990-2015: A
+Systematic Analysis for the Global Burden of Disease Study 2015 (Vol
+388, Pg 1659, 2016).'' \emph{Lancet} 389 (10064). ELSEVIER SCIENCE INC
+360 PARK AVE SOUTH, NEW YORK, NY 10010-1710 USA: E1--E1.
 
@@
 
+\hypertarget{ref-mozaffarian2015executive}{}
+Mozaffarian, Dariush, Emelia J Benjamin, Alan S Go, Donna K Arnett,
+Michael J Blaha, Mary Cushman, Sarah De Ferranti, et al. 2015.
+``Executive Summary: Heart Disease and Stroke Statistics---2015 Update:
+A Report from the American Heart Association.'' \emph{Circulation} 131
+(4). Am Heart Assoc: 434--41.
+
+\hypertarget{ref-ridker2012}{}
+Ridker, Paul M, Aruna Pradhan, Jean G MacFadyen, Peter Libby, and Robert
+J Glynn. 2012. ``Cardiovascular Benefits and Diabetes Risks of Statin
+Therapy in Primary Prevention: An Analysis from the Jupiter Trial.''
+\emph{The Lancet} 380 (9841). Elsevier: 565--71.
+
+\hypertarget{ref-tsaousis2014}{}
+Tsaousis, Konstantinos T. 2014. ``Blood Glucose and Cholesterol
+Concentrations in a Mediterranean Rural Population of Andros Island,
+Greece.'' \emph{International Journal of Preventive Medicine} 5 (11).
+Wolters Kluwer--Medknow Publications: 1464.
+
+\hypertarget{ref-yusuf2016}{}
+Yusuf, Salim, Jackie Bosch, Gilles Dagenais, Jun Zhu, Denis Xavier,
+Lisheng Liu, Prem Pais, et al. 2016. ``Cholesterol Lowering in
+Intermediate-Risk Persons Without Cardiovascular Disease.'' \emph{New
+England Journal of Medicine} 374 (21). Mass Medical Soc: 2021--31.
+
+\hypertarget{ref-yusuf2004effect}{}
+Yusuf, Salim, Steven Hawken, Stephanie Ôunpuu, Tony Dans, Alvaro Avezum,
+Fernando Lanas, Matthew McQueen, et al. 2004. ``Effect of Potentially
+Modifiable Risk Factors Associated with Myocardial Infarction in 52
+Countries (the Interheart Study): Case-Control Study.'' \emph{The
+Lancet} 364 (9438). Elsevier: 937--52.
+
 \end{document}

### 2021-01-15 Q_reg_plot.R

@@ -1,13 +1,11 @@
 # Plot of quantile regression for glucose reressed on Gender, Age,Race,BMI,Statin_status,BMI
 require(quantreg)
 library(tidyverse)
+library(splines)
 bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
 
 #remove duplicated rows and remove na data.
 bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
-#both DID070 and DIQ 070 represent an answer for question Are you useing medication for glucose
-#yes 1 no 2
-bmi.data$diab_drug=coalesce(bmi.data$DIQ070,bmi.data$DID070)
  
 bmi.data=data.frame(bmi.data$RIAGENDR,bmi.data$RIDAGEYR, bmi.data$RIDRETH1,bmi.data$BMXBMI,
                     bmi.data$LBXTC,bmi.data$TCRx,bmi.data$LBXGLU,bmi.data$BMXWAIST)
@@ -27,31 +25,36 @@ bmi.data <- cbind(bmi.data, Age2 = bmi.data$Age^2)
 bmi.data <- cbind(bmi.data, BMI2 = bmi.data$BMI^2)
 bmi.data <- cbind(bmi.data, Total_col2 = bmi.data$Total_chol^2)
 formula <- Glu ~Gender+Age+Race+BMI+Statin_status+Age2+BMI2+Total_chol+Total_col2+Waist_cir 
-     
+#formula <- Glu ~Gender+Race+BMI+Statin_status+Age+Total_chol+Waist_cir      
 fit3.ols <- summary(lm(formula,data =bmi.data))$coefficients
 #attach(bmi.data)
 p <- nrow(fit3.ols)
 taus <- c(1:4/100, 1:19/20)
 fit3 <- array(fit3.ols,c(p,4,length(taus)))
+rownames(fit3)=rownames(fit3.ols)
+colnames(fit3)=colnames(fit3.ols)
+dimnames(fit3)[[3]]=taus
+fit3["Age2","Estimate",'0.05']
 for(i in 1:length(taus)){
     print(taus[i])
     f <- rq(formula, taus[i], data = bmi.data, method="fn")
     fit3[,,i] <- summary(f)$coefficients
 }
 ##
-Value   Std. Error     t value     Pr(>|t|)
-(Intercept)         66.876965374 22.109483682  3.02480901 0.0024927857
[…]

### 2021-01-15 Q_reg_plot2.R

@@ -13,7 +13,7 @@ bmi.data=data.frame(bmi.data$RIAGENDR,bmi.data$RIDAGEYR, bmi.data$RIDRETH1,bmi.d
 #bmi.data= na.omit(bmi.data[,c(5,6,9,29,33,43,32)])
 #bmi.data=bmi.data[bmi.data$bmi.data.diab_drug==2,]
 #bmi.data=na.omit(bmi.data[,c(1:7)])
-colnames(bmi.data) <- c("Gender","Age","Race","BMI","Total_chol" ,"Statin_status","Glu","Waist_cir")
+colnames(bmi.data) <- c("Gender","Age","Race","BMI","Total_chol" ,"Statin_status","Glu","waist_cir")
 bmi.data=na.omit(bmi.data)
 bmi.data=bmi.data%>%filter(bmi.data$Age>19)
 bmi.data$Gender=recode(bmi.data$Gender, "1" = "Male", "2" = "Female" )
@@ -24,7 +24,7 @@ bmi.data$Race=recode(bmi.data$Race, "1" = "Mexican", "2" = "Other_Hispanic","3"=
 
  
 #formula <- Glu ~Gender+Age+Race+BMI+Statin_status+Age2+BMI2+Total_chol+Total_col2+Waist_cir 
-formula <- Glu ~Gender+Race+BMI+Statin_status+bs(Age,intercept=FALSE,df=5)+bs(Total_chol,intercept=FALSE,df=5)+bs(Waist_cir,intercept=FALSE,df=5)      
+formula <- Glu ~Gender+Race+BMI+Statin_status+bs(Age,intercept=FALSE,df=5)+bs(Total_chol,intercept=FALSE,df=5)+bs(waist_cir,intercept=FALSE,df=5)      
 fit3.ols <- summary(lm(formula,data =bmi.data))$coefficients
 #attach(bmi.data)
 p <- nrow(fit3.ols)
@@ -39,28 +39,7 @@ for(i in 1:length(taus)){
     f <- rq(formula, taus[i], data = bmi.data, method="fn")
     fit3[,,i] <- summary(f)$coefficients
 }
-##
-Value   Std. Error     t value     Pr(>|t|)
-(Intercept)                                 225.801759  121.0212519  1.86580254 6.209346e-02
-GenderMale                                    2.498428    2.4264868  1.02964826 3.031960e-01
-RaceMexican                                   5.427993    7.8351224  0.69277707 4.884629e-01
[…]

### 2021-01-15 exploratory-data-analysis_JRT.R

@@ -265,12 +265,11 @@ temp <- do.call(rbind, temp)
 Age_10 <- as.factor(temp)
 
 #dat <- cbind(dat,Age_10)
-bmi.data$
-p<-ggplot(dat, aes(x=Age_10, y=bmi.data$Glu, color=Statin_status)) +
+p<-ggplot(dat, aes(x=Age_10, y=BMI, color=Statin_status)) +
     geom_boxplot(notch = FALSE, fill = "lightgray" )+
     stat_summary(fun = mean, geom = "point",
-    shape = 18, size = 2.5, color = "#FC4E07") 
-    #facet_grid(Gender,Type_glu)
+    shape = 18, size = 2.5, color = "#FC4E07")+ 
+    #facet_grid(Gender~Type_glu)
 p+labs(title ="  BMI for statin and non-statin users",subtitle =" ", caption = " NHANES data set")
 show(p)
  #############################################################################
@@ -279,4 +278,9 @@ plot(summary(rq(BMI~Statin_status+Type_glu+Race+Age+Gender,tau = 1:49/50,data=da
 
 plot(summary(rq(Glu~Statin_status+Race+Age+Gender,tau = 1:49/50,data=bmi.data ))) 
 
+#############
+##################
+###########
+
+l=bmi.data %>% subset(TCRx == 1) %>% count(RXDDRUG) %>% arrange(desc(n))
  

### 2021-01-15 rq11.R

@@ -17,7 +17,6 @@ for(i in 1:length(taus)){
 
 #########################################################################################
 
-
 #Plot results from newfit.R:
 #Formula:
 #weight ~ black + married + boy + tri2 + tri3 + novisit + ed.hs + ed.smcol +

### 2021-01-17 Q1.R
Update

@@ -1,0 +1,31 @@
+library(quantreg)
+library(ggplot2)
+library(dplyr)
+
+# OLS
+lm <- lm(data=mtcars, 
+         formula =  hp ~  disp + mpg + I(mpg^2) + qsec + am)
+
+ols <- as.data.frame(coef(lm))
+ols.ci <- as.data.frame(confint(lm))
+ols2 <- cbind(ols, ols.ci)
+ols2 <- tibble::rownames_to_column(ols2, var="term")
+
+# Quantile
+rq(data=mtcars, 
+   tau= 1:9/10,
+   formula = hp ~  disp + mpg + I(mpg^2) + qsec + am) %>%
+    broom::tidy(se.type = "boot") %>%
+    filter(!grepl("factor", term)) %>%
+    ggplot(aes(x=tau,y=estimate))+
+    
+    # quantilie results
+    geom_point(color="#27408b", size = 3)+ 
+    geom_line(color="#27408b", size = 1)+ 
+    geom_ribbon(aes(ymin=conf.low,ymax=conf.high),alpha=0.25, fill="#27408b")+
+    
+    # OLS results
+    geom_hline(data = ols2, aes(yintercept= `coef(lm)`), lty=1, color="red", size=1)+
+    geom_hline(data = ols2, aes(yintercept= `2.5 %`), lty=2, color="red", size=1)+
+    geom_hline(data = ols2, aes(yintercept= `97.5 %`), lty=2, color="red", size=1)+
+    facet_wrap(~term, scales="free", ncol=2) 

### 2021-02-12 manuscript/manuscript.Rmd
updating files
update

--- 2020-12-28 manuscript/manuscript.Rmd
@@
 ---
-title: " Quantile Regression Analysis for Statin effects on glucose level"
+title: " Quantile Regression Analysis for Statin Effects on Body mass Index"
 output: 
@@
 ---
+
 \section{introduction}
 
----
-# here's a comment
-# ```{r}
-# Body Mass Index (BMI) plays an important rule in predicting heart disease #risk[@katbody].
-Our goal is to compare 90Th quantile regression for BMI in Diabetes and #prediabetes population.
-Quantile regression has many succesfyl application in ecology #where different factores interect in a complicated way that produce different variation #of one factor for different levels of another variabels[@cade2003].
-# ```
----
+Body Mass Index (BMI) plays an important rule in predicting heart disease risk[@katbody].
+Our Goal is to estimate the trend in the $\tau$th quantile of  BMI using set of independent predictors.
+BMI departs normality because of the skewnes on the right and it is shown by using Box-cox transformation [@flegal1999].
+Estimation of underweight and overweight can be effected by the voilation of the normality.
+Quantile regression is a crucial tools used to estimate BMI with the dispersion of the association of predictors.
+We found that spline regressions produce different estimate than polynomial regressions.
+Quantile regression has many successful application in ecology where different factors interact in a complicated way that produce different variation of one factor for different levels of another variables[@cade2003].
+
 Approximately, 18 million deaths annually per year are caused by cardiovascular diseases(CVD) and similar to this number of nonfatal cardiovascular events [@hay2017gbd].
-For 2011, annual costs for CVD and stroke were $\$320.1$ billion, which is more than cancer cost.
+In 2011, annual costs for CVD and stroke were $\$320.1$ billion, which is more than cancer cost.
 This cost include \$195.6  billion in direct costs (healthcare costs), and cost of future productivity loss is  \$124.5 [@mozaffarian2015executive].
-Abnormal lipid ratio  is a risk  factor for CVD [@yusuf2004effect].
-Lowering low-density lipoprotein (LDL) using statin reduces risk of cardiovascular diseases even with population with no CVD  [@yusuf2016].
+Important factors that associated with CVD are high body mass index (BMI) and abnormal lipid ratio  [@yusuf2004effect],[@anderson1991].
+Lowering low-density lipoprotein (LDL) using statin or other drugs reduce risk of cardiovascular diseases even with population with no CVD  [@yusuf2016].
+Ferrieres at el.
+[@ferrieres2018] studied effect of BMI on the choice of lipid-lowering treatment.It is been found that statin intensity increases with high level of BMI($\rho=0.13$).
 It is known that diabetes is a risk factor for CVD, however, it is shown that elevated  glucose, prediabetes,is also a risk factor for CVD [@balkau2004prediction].
 
-Statin use associated with high risk of a new onset diabetes in normoglcemic (HR 1.19,95% CI , 1.05 to 1.35) and in prediabetes (HR 1.24 95% CI , 1.11 to 1.38).
+Statin use  associates with high risk of elevating BMI level[@sugiyama2014].
+It is been shown that statin users consume 192 additional calories per day which cause gaining a 6 lb-to-11 lb in a year.
+Statin users gain 1.3 units in the BMI measure while non-staining users gains 0.4 unit  .Moreover, consumption of fat in statin users raised by 14.4%.
+
+Statin has negative impact on glucose level.
+The hazard ratio of a new onset diabetes in  normoglycemic statin users(HR 1.19,95% CI , 1.05 to 1.35) and in pre-diabetes (HR 1.24 95% CI , 1.11 to 1.38).
 On the other hand, overall mortality risks went down  in both normoglycemic (HR 0.70;
-95 % CI, 0.66 to 0.80) and IFG patients (HR
+95 % CI, 0.66 to 0.80) and in prediabetes patients (HR
 0.77, 95 % CI, 0.64 to 0.91) with statin use [@castro2016].
-For population with one or more risk factor for diabetes, statin use associate with 39% reduction in the primary end points (the hazard ratio (HR) 0.61), and a 28% (HR 1.28)increase in diabetes[@ridker2012].Pandya at el.[pandya2015] suggested the dis-utility associated with taking a pill daily, statin price, and the risk of statin-induced diabetes negatively impacted the cost effectiveness of statin use recommendation.
+For population with one or more risk factor for diabetes, statin use associate with 39% reduction in the primary end points (the hazard ratio (HR) 0.61), and a 28% (HR 1.28)increase in diabetes[@ridker2012].Pandya at el.[@pandya2015] suggested the dis-utility associated with taking a pill daily, statin price, and the risk of statin-induced diabetes negatively impacted the cost effectiveness of statin use recommendation.
+
+Several studies estimated the association of different factors like lipid-lowering drug  with the conditional mean of BMI using OLS or logistic regression model[@ferrieres2018].
+The drawback in this study is not considering the dispersion of the association of covariates with conditional distribution of the dependent variables, BMI.
 
@@
 =F(\hat{x})-\tau.$$ 
-Due to monotnicity of the cumulative distribution function, any solution that satisfies $\{x:F(x)=\tau \}$ is a minimizing for the expected loss function.
+Due to monotonicity of the cumulative distribution function, any solution that satisfies $\{x:F(x)=\tau \}$ is a minimizing for the expected loss function.
 
@@
 
+\subsection{Quantile Regression Technique }
+
+\subsection{splines}
+   A continuous predictor can be linear, say $ X$, or nonlinear, say $X^2$ depends on the relationship with the response variable.
+Most of the relations between the responses and predictors variables are complicated to the point that linear regressions are not suitable to model these relationships[@bruce2017].
+For example, the response to different levels of drug doeses is not a linear relationship.
+Linear regressions can be generalized to deal with nonlinear effects.
+One approach is through including polynomial terms to regression equation.
+This approach is called  Polynomial regression.
+The mathematical model for $n$ degree polynomial regression is shown in the Eq\eqref{non}
+ \begin{equation}\label{non}
+ y=\beta_0+\beta_1 X+\beta_2 X^2+\cdots+\beta_nX^n.
+ \end{equation}
+
+ One of the limitations of using polynomial regression is the curvature that can be captured is limited with low order terms.
+However, including higher order terms has negative impact on the model by introducing undesirable "wiggliness" in the regression equation.
+Another robust approach to model nonlinear relationships is splines.
+It is similar to a technique used by draftsman's in ploting curves.
+Spline is a process of constructing a set of  piecewise continuous
+polynomials that are smoothly connected at set of points in the range of predictor variable.
+The connection points are called knots i.e.
+splines are used to smoothly interpolate between certain points.
+Let $a,b$ ,and $c$ are the end points of the $x$-axis intervals.
+A smooth cubic spline function is defined by the following equation.
+\begin{equation}
+f(X)=X\beta=\beta_{0}+\beta_{1}X+\beta_2X^2+\beta_{3}X^{3}+\beta_{4}(X-a)_{+}^3+\beta_{5}(X-b)_{+}^3+\beta_6(X-c)_{+}^3,
+\end{equation}
+
+where $$(u)_{+}=  
+ \left\{
+	\begin{array}{ll}
+		u  & \mbox{if } u > 0 \\
+		0 & \mbox{if } u \leq 0
+	\end{array}
+\right. $$
+
 \section{Methods}
-A multivariate quantile regression model is used to assess the characteristics of the   association variability in different quantiles of the conditional distribution of the glucose levels.
-Moreover, the independent variables are Gender, Age, race, diabetes status, and statin use.
+A multivariate quantile regression model is used to assess the characteristics of the   association variability in different quantiles of the conditional distribution of the body mass index.
 
-#Data
+ The independent variables in our model are gender, race, age, total cholesterol, Cholesterol drug uses (yes or no).
+All type of cholesterol drug are included including  statins.
+The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.
+
+\section{Numerical Example}
+\subsection{Data}
  The data used in this study is National Health and Nutrition Examination Survey data (NHANES)[@NHANES].
@@
 population.It focuses on  variety of health and nutrition measurements.
-In this study, we cumulated 6 cycles of NHANES data (2007–2018).
-There are 12,406 records.
-The dependent variables in our model are gender, race, age, BMI, total cholesterol, and statin use (yes or no).
-All type of statin are included.
-The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.
+The survey data are released every two years cycle.
+In this study, we accumulated 6 cycles of NHANES data (2007–2018).
+We used
+ two data files: One contains demographic variables, such as age, sex, race, income, etc, and the other contains data that are related to body measurements, such as BMI, head circumference, etc.
+These files are marged by using the respondent sequence number (SEQN)
+ There are  around 12,000 records. We selected  population age between 20 and 80.
  BMI are classified into different categories according to underweight, 18.5 kg/m2; normal weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/m2; obese, 30 to 35 kg/m2; and very obese more than 35 kg/m2.
 
-| Syntax      | Male  | Femal     |
+| Syntax      | Male  | Female     |
 | :---        |    :----:   |          ---: |
@@
 | Mean of Age | 49.9       | 49.73   |
-| glucose        |  112.618     |  106.47   |
-| TC         | Title       | Here's this   |
+| BMI        |  28.549    |  29.379  |
+| TC         |        |    |
 | Statin use (ratio) | 0.198       | 0.181   |
@@
 \section{Results}
-The resulting estimate of effects on conditional mean of glucose level may not reflect the size and nature of theses effects on lower or upper quantile.
+The resulting estimate of effects on conditional mean of BMI level may not reflect the size and nature of these effects on lower or upper quantile.
 For example, in the Figure \@ref(fig:resu1), the conditional mean shows the conditional mean effects of gender on glucose level is about 7.
@@
 
-```{r resu1, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+```{r resu1, out.width = "100%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
  So,
+
+```{r resu12, out.width = "100%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "newfig11.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "newfig11.png"))
+```
+
+```{r resu122, out.width = "80%", fig.align = "center", fig.cap = "Using Cubic splines", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "newfig111.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "newfig111.png"))
+```
+
  therefore
@@
 So,
+
  Age effect modeled as a quadratic factor.
@@
 
-```{r resu3, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic age effect on glucose leveles for four different quantiles of the conditional glucose distribution.
+```{r resu3, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic age effect on glucose leveles for four different quantiles of the conditional BMI distribution.
 The ", echo = FALSE}
@@
 ```
-Quadratic effect of total cholesterol on the conditional distribution of glucose is convex.
-At the lower tail, decreasing glucose level by somewhat around 1.4 up to around 180 Cholesterol level.
-Then, started to increase glucose levels after TC beyond 180.
-At higher quantile, the reverse in the cholesterol effects is shifted to higher cholesterol levels which around 200, Figure \@ref(fig:resu4).
-The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014],[@chang2011].
-They found that there is a positive correlation between the two groups on average.
+Using splines 
+```{r, out.width = "80%", fig.align = "center", fig.cap = "Age effect modeled using bsplines ", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "effect_Age_22.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "effect_Age_22.png"))
+```
+
+Marginal quadratic cholesterol effect
 
@@
 
-<!-- ```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE} -->
-<!-- library(knitr) -->
-<!--  kable(dat[,2:3],caption="A nit table") -->
-<!-- ``` -->
+Splines modeling
+
+```{r resu33, out.width = "80%", fig.align = "center", fig.cap = " Marginal Cholestrol effect modeled as B splines.  The ", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "effect_TC_22.png"))) {
+    source(here::here("exploratory-data-analysis_JRT.R"))
+}
+knitr::include_graphics(here::here("images", "effect_TC_22.png"))
+```
+
+Quadratic effect of total cholesterol on the conditional distribution of glucose is convex.
+At the lower tail, decreasing glucose level by somewhat around 1.4 up to around 180 Cholesterol level.
+Then, started to increase glucose levels after TC beyond 180.
+At higher quantile, the reverse in the cholesterol effects is shifted to higher cholesterol levels which around 200, Figure \@ref(fig:resu4).
+The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014],[@chang2011].
+They found that there is a positive correlation between the two groups on average.
+
+So,
 

### 2021-02-12 Q_reg_plot.R

@@ -1,4 +1,5 @@
-# Plot of quantile regression for glucose reressed on Gender, Age,Race,BMI,Statin_status,BMI
+# Plot of quantile regression for glucose regressed BMI on Gender, Age,Race,Statin_status
+#Roger Koenker
 require(quantreg)
 library(tidyverse)
 library(splines)
@@ -22,9 +23,9 @@ bmi.data$Race=recode(bmi.data$Race, "1" = "Mexican", "2" = "Other_Hispanic","3"=
 # Classifying population to diabetes and non diabetes
 
 bmi.data <- cbind(bmi.data, Age2 = bmi.data$Age^2)
-bmi.data <- cbind(bmi.data, BMI2 = bmi.data$BMI^2)
-bmi.data <- cbind(bmi.data, Total_col2 = bmi.data$Total_chol^2)
-formula <- Glu ~Gender+Age+Race+BMI+Statin_status+Age2+BMI2+Total_chol+Total_col2+Waist_cir 
+#bmi.data <- cbind(bmi.data, BMI2 = bmi.data$BMI^2)
+bmi.data <- cbind(bmi.data, Total_chol2 = bmi.data$Total_chol^2)
+formula <- BMI ~Gender+Race+Statin_status+Age+Age2+Total_chol+Total_chol2 
 #formula <- Glu ~Gender+Race+BMI+Statin_status+Age+Total_chol+Waist_cir      
 fit3.ols <- summary(lm(formula,data =bmi.data))$coefficients
 #attach(bmi.data)
@@ -41,20 +42,18 @@ for(i in 1:length(taus)){
     fit3[,,i] <- summary(f)$coefficients
 }
 ##
-(Intercept)        194.238571676 64.666035998  3.0037185 2.672537e-03
-GenderMale           3.647848794  3.155954251  1.1558624 2.477605e-01
-Age                  1.326574494  0.465484350  2.8498799 4.381047e-03
-RaceMexican          9.228608538  8.558627551  1.0782814 2.809300e-01
-RaceOther           -4.151100984  6.144220397 -0.6756107 4.993009e-01
-RaceOther_Hispanic   1.275710479  8.781682930  0.1452695 8.845006e-01
-RaceWhite          -14.390799248  5.627954833 -2.5570211 1.056951e-02
-BMI                 -4.380820563  1.552191187 -2.8223460 4.775236e-03
-Statin_status       44.861806366  6.279534638  7.1441291 9.583445e-13
[…]

### 2021-02-12 Q_reg_plot2.R

@@ -1,4 +1,5 @@
-# Plot of quantile regression for glucose reressed on Gender, Age,Race,BMI,Statin_status,BMI
+# Plot of quantile regression for BMI regressed on Gender, Age,Race,Statin_status
+#Using bsplines
 require(quantreg)
 library(tidyverse)
 library(splines)
@@ -20,11 +21,16 @@ bmi.data$Gender=recode(bmi.data$Gender, "1" = "Male", "2" = "Female" )
 # RIDRETH1 (race, 1=mexican, 2=otherHispanic, 3= Non-Hispanic White,4=Non-Hispanic Black ,5=Other Race - Including Multi-Racial
 
 bmi.data$Race=recode(bmi.data$Race, "1" = "Mexican", "2" = "Other_Hispanic","3"="White","4"="Black","5"="Other" )
-# Classifying population to diabetes and non diabetes
 
+
+# Save an object to a file
+saveRDS(bmi.data, file = "bmi.data.rds")
+# Restore the object
+bmi.data=readRDS(file = "bmi.data.rds")
+ 
  
 #formula <- Glu ~Gender+Age+Race+BMI+Statin_status+Age2+BMI2+Total_chol+Total_col2+Waist_cir 
-formula <- Glu ~Gender+Race+BMI+Statin_status+bs(Age,intercept=FALSE,df=5)+bs(Total_chol,intercept=FALSE,df=5)+bs(waist_cir,intercept=FALSE,df=5)      
+formula <- BMI ~Gender+Race+Statin_status+bs(Age,intercept=FALSE,df=5)+bs(Total_chol,intercept=FALSE,df=5)       
 fit3.ols <- summary(lm(formula,data =bmi.data))$coefficients
 #attach(bmi.data)
 p <- nrow(fit3.ols)
@@ -55,11 +61,11 @@ png(file = here::here("images", "newfig11.png"),
     res = 400, height = 9, width = 16, units = "in")
 p <- dim(fit3)[1]
 #blab <- c("Intercept","Male ","Age","RaceMexican", "RaceOther", "RaceOther_Hispanic ", "White ", "BMI", " Statin_status","Age Suqared","BMI^2","Total cholesterol","Total cholestrol^2","Waist Circumference")
[…]

### 2021-02-12 ci_splin.R

@@ -1,38 +1,76 @@
-
+#Marginal effect on BMI with splines
+#Plot for the confidence interval of BMI regressed on splines of Age, 
+#race, gender,and cholesterol medications use.
  
 library(quantreg)
 library(splines)
+library(tidyverse)
 
-
+#memory.limit(size=56000)
 #attach(bmi.data)
-bmi.data=readRDS(file = "bmi.data.rds")
+dat=readRDS(file = "bmi.data.rds")
+#dat=dat[dat$BMI<28,]
+dat=filter(dat,Statin_status!='9')
+levels(dat$Statin_status) <- c('1','2')
+dat$Statin_status <- factor(dat$Statin_status)
+X <- model.matrix( BMI ~ bs(Total_chol, df = 5) + Race + Gender + Statin_status, data = dat)
+qr_fit_dat <- rq(  dat$BMI ~ X - 1, data=dat, tau = 0.9)
 
-formula <- Glu ~Gender+Race+BMI+Statin_status+bs(Age,intercept=FALSE,df=5)+bs(Total_chol,intercept=FALSE,df=5)+bs(waist_cir,intercept=FALSE,df=5)      
+ 
+#formula <- Glu ~Gender+Race+BMI+Statin_status+bs(Age,intercept=FALSE,df=5)+bs(Total_chol,intercept=FALSE,df=5)+bs(waist_cir,intercept=FALSE,df=5)
+# formula <- Glu ~ Gender+Race+Statin_status+bs(Age,intercept=FALSE,df=5)#+bs(Total_chol,intercept=FALSE,df=5)+bs(waist_cir,intercept=FALSE,df=5)      
+
+  
+ 
  
 #model <- rq(Glu ~ bs(Age, knots=c(25,50,75))+BMI+Gender, tau=0.5, data=bmi.data ) 
 
-model <- rq(formula, tau=0.5, data=bmi.data ) 
+# qr_fit_dat <- rq(formula, tau=0.5, data=bmi.data ) 
  
  
 #plot
+#age_pred <- seq(16, 80, by = 1)
+x2_pred <- factor(1:5)
+x3_pred <- factor(1:2)
+x4_pred <- factor(1:2)
+x5_pred <-seq(min(dat$Total_chol),400,by=1)
+dat_pred <- data.frame(expand.grid(age_pred, x2_pred, x3_pred, x4_pred))
[…]

### 2021-03-18 manuscript/manuscript2.Rmd
update

 
---
title: " Quantile Regression Analysis for Statin Effects on Body mass Index"
output:
    bookdown::pdf_document2:  
        keep_tex: true
bibliography: cite.bib
link_citations: true
header-includes:
    - \usepackage{setspace} 
    - \usepackage{float}
abstract: "My abstract"
keywords: "My keywords"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontsize: 12pt
fig_caption: yes
indent: true
---
\setstretch{4}
\section{introduction}

  High BMI has negative impact on public health. Due to high cost of obesity, it is crucial to get better understanding of the underlying risk factor for obesity. This can help decision makers to create a new regulation that help to prevent and to stop the dramatic increase in the BMI index.

  Body Mass Index (BMI) plays an important role in predicting heart disease risk[@katbody]. Approximately, 18 million deaths annually per year are caused by cardiovascular diseases(CVD), and similar to this number of nonfatal cardiovascular events [@hay2017gbd].
In 2011, annual costs for CVD and stroke were $\$320.1$ billion, which is more than cancer cost. This cost includes \$195.6  billion in direct costs (healthcare costs), and the cost of future productivity loss is  \$124.5 [@mozaffarian2015executive]. Important factors associated with CVD are high body mass index (BMI) and abnormal lipid ratio  [@yusuf2004effect], [@anderson1991]. Lowering low-density lipoprotein (LDL) by using statin or other drugs reduces the risk of cardiovascular diseases even with a population with no CVD  [@yusuf2016]. Ferrieres et al. [@ferrieres2018] studied the effect of BMI on the choice of lipid-lowering treatment. It is been found that statin intensity increases with the high level of BMI($\rho=0.13$).

Taking cholesterol drug medication  associates with a high risk of elevating BMI level. It is been shown that statin users consume 192 additional calories per day which causes gaining a 6 lb to 11 lb. in a year. Statin users gain 1.3 units in the BMI measure while non-staining users gain 0.4 unit. Moreover, consumption of fat in statin users raised by 14.4%[@sugiyama2014].

 Logistic regression helps us to find out the group that has a higher odd of obesity, and ordinary least squares (OLS) regression helps us to study the effects of predictors on the average mean of the response. For example, estimating the association of different factors like a lipid-lowering drug with the conditional mean of BMI using OLS or logistic regression model[@ferrieres2018]. Both of these approaches do not give us insight into the predictor's effects on different quantiles of the responses.

  Quantile regression is used to investigate the heterogeneity in the association of the $\tau$th quantile of BMI with a set of independent predictors, that is investigate the effects of a specific predictors on the various quantiles of the BMI. BMI departs normality because of the skewness on the right and left tails [@flegal1999]. Estimation of underweight and overweight can be affected by the violation of normality. Quantile regression is a crucial tool used to estimate BMI with the dispersion of the association with predictors.

  Quantile regression has many successful applications in ecology where different factors interact in a complicated way that produces different variations of one factor for different levels of another variable [@cade2003]. The association between BMI and the set of predictors; low childhood socioeconomic position, high maternal weight, low childhood general cognition  is stronger in the upper end of BMI quantile. This trend  is found in the UK population[@bann2020]. One cause of this heterogeneity is that risk factors may have stronger effect on patients with worse health, and these effects may diminishes when conditional mean of the BMI is studied.

  We found that spline regressions produce a different estimate than polynomial regressions. Polynomial regression using the quadratic term of predictors forces the response to take convex or concave shape, see Figure 1.12 [@koenker2005]. This is because the limit of quadratic functions approach $\pm\infty$ as $x\rightarrow\pm\infty.$ However, when we model the predictor as splines the response is not forced to take a specific shape. In the latter case, different polynomials are constructed for the different regions in the range of predictors.

 \section{Quantile Regression}
Quantile regression is a tool used to regress the dependent variable with high variance over the independent variables. QR is developed to study the relationships between variables that have week or no-relationships between their means. One of the advantages of using QR over OLS is QR is robust for outliers.

For a random variable $X$, the cumulative distribution function (CDF) is $$F(X)=P(X\leq x),$$ and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} $$ where $0<\tau<1$.
Let the loss function is defined by $$\rho_{\tau}(u)= u(\tau-I_{(u<0)})$$ where $I$ is the indicator function  [@koenker2005]. The quantile estimator is the value that minimizes the expected loss function

$$E\rho_{\tau}(X-\hat{x})=(\tau-1)\int_{-\infty}^{\hat{x}} (x-\hat{x})dF(x)+\tau\int_{\hat{x}}^{-\infty} (x-\hat{x})dF(x).$$
Differentiating with respect to $\hat{x}$, we get
$$ 0  =(\tau-1)\int_{-\infty}^{\hat{x}} dF(x)+\tau\int_{\hat{x}}^{-\infty} dF(x)
=F(\hat{x})-\tau.$$
Due to the monotonicity of the cumulative distribution function, any solution that satisfies $\{x:F(x)=\tau \}$ is a minimizing for the expected loss function.

Least square method expresses conditional mean of y given x as $\mu(x)=x^T\beta$ and it solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.$$ Quantile regression expresses conditional quantile function $Q_y(\tau|x)=x^T \beta ({\tau)}$ and solve $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.$$This minimization problem can be reformulated to a linear programming problem $$ \underset{\beta\in \mathcal{R}^p}{\text{min}} $$

\subsection{Quantile Regression Technique }

\subsection{splines}
   A continuous predictor can be linear, say $X$, or nonlinear, say $X^2$ depends on the relationship with the response variable. Most of the relations between the responses and predictors variables are complicated to the point that linear regressions are not suitable to model these relationships[@bruce2020]. For example, the response to different levels of drug doses is not a linear relationship. Linear regressions can be generalized to deal with nonlinear effects. One approach is through including polynomial terms in the regression equation. This approach is called Polynomial regression. The mathematical model for $n$ degree polynomial regression is shown in the Eq\eqref{non}
 \begin{equation}\label{non}
 y=\beta_0+\beta_1 X+\beta_2 X^2+\cdots+\beta_nX^n.
 \end{equation}

 One of the limitations of using polynomial regression is the curvature that can be captured is limited with low order terms. However, including higher-order terms has a negative impact on the model by introducing undesirable "wiggliness" in the regression equation.  Another robust approach to model nonlinear relationships is splines. It is similar to a technique used by draftsmen in plotting curves. The spline is a process of constructing a set of piece-wise continuous
polynomials that are smoothly connected at a set of points in the range of the predictor variable. The connection points are called knots i.e. splines are used to smoothly interpolate between certain points. Let $a,b$ ,and $c$ are the endpoints of the $x$-axis intervals. A smooth cubic spline function is defined by the following equation.
\begin{equation}
f(X)=X\beta=\beta_{0}+\beta_{1}X+\beta_2X^2+\beta_{3}X^{3}+\beta_{4}(X-a)_{+}^3+\beta_{5}(X-b)_{+}^3+\beta_6(X-c)_{+}^3,
\end{equation}

where $$(u)_{+}=  
 \left\{
\begin{array}{ll}
u  & \mbox{if } u > 0 \\
0 & \mbox{if } u \leq 0
\end{array}
\right. $$

\section{Methods}
A multivariate quantile regression model is used to assess the characteristics of the association variability in different quantiles of the conditional distribution of the body mass index.

 The independent variables in our model are gender, race, age, total cholesterol, cholesterol drug use (yes or no). All types of cholesterol drugs are used including statins. The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.

\section{Numerical Example}
\subsection{Data}
 The data used in this study is National Health and Nutrition Examination Survey data (NHANES)[@NHANES]. The survey examines a nationally representative sample of the U.S. population. It focuses on a variety of health and nutrition measurements. The survey data are released every two years cycle.  In this study, we accumulated 6 cycles of NHANES data (2007–2018). We used two data files: One contains demographic variables, such as age, sex, race, income, etc., and the other contains data that are related to body measurements, such as BMI, head circumference, etc. These files are merged by using the respondent sequence number (SEQN)
 There are around 12,000 records. We selected a population age between 20 and 80.
 BMI are classified into different categories according to underweight, 18.5 kg/m2; normal weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/m2; obese, 30 to 35 kg/m2; and very obese more than 35 kg/m2.

| Syntax      | Male  | Female     |
| :---        |    :----:   |          ---: |
| count |  5990      | 6416   |
| Mean of Age | 49.9       | 49.73   |
| BMI        |  28.549    |  29.379  |
| TC         |        |    |
| Statin use (ratio) | 0.198       | 0.181   |

base_box_plot

```{r box, out.width = "100%", fig.align = "center", fig.cap = "Illustration of data distribution using a box plot. The plot compares cholesterol drug users vs non-cholesterol drug users", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "base_box_plot.png"))) {
    source(here::here("exploratory-data-analysis.R"))
}
knitr::include_graphics(here::here("images", "base_box_plot.png"))
```

Figure \@ref(fig:box) shows the association between age and BMI with respect to cholesterol drug is inconsistent. At the early age, the correlation is positive while at the middle age the correlation is almost flat, and at the old age the correlation is negative. Moreover, at low age cholesterol medications are  described only for a population with high BMI, but at a higher age, the difference in term of the BMI for a population that takes cholesterol medication and without cholesterol medication decreases until it diminishes as in the white population. The  heterogeneity can also be seen in gender ?, for the Hispanic female population, the cholesterol medication is taken by the population with lower BMI if compared to the population that does not take cholesterol medication.
```{r data, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "exploratory.png"))) {
    source(here::here("exploratory-data-analysis.R"))
}
knitr::include_graphics(here::here("images", "exploratory.png"))
```

```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "exploratory2.png"))) {
    source(here::here("exploratory-data-analysis_JRT.R"))
}
knitr::include_graphics(here::here("images", "exploratory2.png"))
```

So,

```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "quant90.png"))) {
    source(here::here("exploratory-data-analysis_JRT.R"))
}
knitr::include_graphics(here::here("images", "quant90.png"))
```

\section{Results}
The resulting estimate of effects on conditional mean of BMI level may not reflect the size and nature of these effects on lower or upper quantile. For example, in Figure \@ref(fig:resu1), the conditional mean effect of gender on BMI level is about -1, that is on average male's BMI is less than a female's BMI by one unit. However, the disparity of the gender effects on lower tails is much larger which is about 1, but the disparity is lower for the upper tail of the distribution somewhat around -3 unit.

From the OLS it is obvious cholesterol drug users have on average higher BMI levels if compared to non-cholesterol drug users which are around 1.75. The disparity in BMI level for cholesterol drug users vs non-cholesterol drug users is almost the same for different Quantiles. cholesterol drug use seems to be associated with rather large effects on BMI levels somewhat around 1.5 to 1.7.

```{r resu1, out.width = "100%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "newfig.png"))) {
    source(here::here("exploratory-data-analysis_JRT.R"))
}
knitr::include_graphics(here::here("images", "newfig.png"))
```
 So,

```{r resu12, out.width = "100%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "newfig11.png"))) {
    source(here::here("exploratory-data-analysis_JRT.R"))
}
knitr::include_graphics(here::here("images", "newfig11.png"))
```

```{r resu122, out.width = "80%", fig.align = "center", fig.cap = "Using Cubic splines", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "newfig111.png"))) {
    source(here::here("exploratory-data-analysis_JRT.R"))
}
knitr::include_graphics(here::here("images", "newfig111.png"))
```

 Age effect modeled as a quadratic factor. The age effect is concave in general, see Figure \@ref(fig:resu3). At the lower quantile, BMI increases from age 20 to around age 50, and it starts to decrease after that. In the 55th quantile, the concavity is stronger at age 50 if compared to the left or right tail. The quadratic effect of age is reflected in the hyperbolic shape. However, the age effect modeled as b spline behaves in a different way. Age effect on BMI increases from age 20 to around age 36 and then start to decrease up to around age 63 then move up again and then decreases up to age 80, see Fig.\@ref(fig:resu33). The BMI trend in this modeling is close to the trend shown in [@chen2005] by using a complicated polynomial and log transformation for the response.

```{r resu3, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic age effect on BMI leveles for four different quantiles of the conditional BMI distribution.  The ", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "p_age_effect.png"))) {
    source(here::here("exploratory-data-analysis_JRT.R"))
}
knitr::include_graphics(here::here("images", "p_age_effect.png"))
```
Using splines
```{r resu33, out.width = "80%", fig.align = "center", fig.cap = "Age effect modeled using bsplines ", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "s-age_effect.png")))
knitr::include_graphics(here::here("images", "s_age_effect.png"))
```

Using splines

```{r resu33g, out.width = "80%", fig.align = "center", fig.cap = "Age effect modeled using bsplines, ggplot plot ", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "Age_splin.png"))) {

}
knitr::include_graphics(here::here("images", "Age_splin.png"))
```

\ref{fig:resu33g}
Marginal quadratic cholesterol effect

```{r resu4, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic cholestrol effect on BMI leveles for four different quantiles of the conditional BMI distribution.  The ", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "p_TC_effect.png"))) {
    source(here::here("exploratory-data-analysis_JRT.R"))
}
knitr::include_graphics(here::here("images", "p_TC_effect.png"))
```

Splines modeling

```{r resu330, out.width = "80%", fig.align = "center", fig.cap = " Illustration of marginal cholestrol effect modeled as B splines.  The ", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "s_TC_effect")))  
knitr::include_graphics(here::here("images", "s_TC_effect.png"))
```

```{r resu3330, out.width = "80%", fig.align = "center", fig.cap = " Illustration of marginal cholestrol effect modeled as B splines using ggplot.  The ", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "TC_splin")))  
knitr::include_graphics(here::here("images", "TC_splin.png"))
```

The quadratic effect of total cholesterol on the conditional distribution of BMI is convex.  At the lower tail, the correlation is positive that is as cholesterol increases the BMI increases. decreasing glucose level by somewhat around 1.4 up to around 180 Cholesterol level. However, at higher quantile the association become negative that is as cholesterol level increases the BMI decreases, see  Figure \@ref(fig:resu4). The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014],[@chang2011]. They found that there is a positive correlation between the two groups on average.

On the other hand, when we use splines to modeled the total cholesterol, there is a huge difference in the shape of the association expect at the higher quantile there is some similarity. At the lower quantile, there is negative correlation between total cholesterol and BMI for total cholesterol in the range less than 160, then the correlation becomes positive for total cholesterol in the range of (170, 250). at the 55th quantile, the correlation is positive for low cholesterol level and then becomes almost flat for the rest cholesterol values. At a higher qunatile, the correlation becomes negative at cholesterol level in the range (160,300), see Figure \@ref(resu330).

\section{Conclusion}
 Multivariate quantile regression is used to study the effects of different risk factors on the BMI levels. Cholesterol drug effects on BMI is negligible at low quantile but at higher quantile cholesterol medication  effects on BMI is larger. This study showed that the association between BMI and total cholesterol is varying with repect to different quantile.

 tota people who have TC levels around 190 mg/dL have the lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile, the optimal cholesterol level is around 200 mg/dL. Moreover,

It is recommended to investigate why the effect estimates are varying across different BMI quantiles.

\newpage
\section{References}

### 2021-03-18 Q_reg_plot.R

@@ -1,33 +1,41 @@
-# Plot of quantile regression for BMI regressed  Gender, Age,Race,Statin_status, Total cholestrol
+# Plot of quantile regression for BMI regressed  Gender, Age,Race,Cholesterol_Drug_Use, Total cholestrol
 #Roger Koenker
 require(quantreg)
 library(tidyverse)
 library(splines)
+
+
 bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
 
 #remove duplicated rows and remove na data.
 bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
- 
+
 bmi.data=data.frame(bmi.data$RIAGENDR,bmi.data$RIDAGEYR, bmi.data$RIDRETH1,bmi.data$BMXBMI,
                     bmi.data$LBXTC,bmi.data$TCRx,bmi.data$LBXGLU,bmi.data$BMXWAIST)
 #bmi.data= na.omit(bmi.data[,c(5,6,9,29,33,43,32)])
 #bmi.data=bmi.data[bmi.data$bmi.data.diab_drug==2,]
 #bmi.data=na.omit(bmi.data[,c(1:7)])
-colnames(bmi.data) <- c("Gender","Age","Race","BMI","Total_chol" ,"Statin_status","Glu","Waist_cir")
+colnames(bmi.data) <- c("Gender","Age","Race","BMI","Total_chol" ,"Cholesterol_Drug_Use","Glu","waist_cir")
 bmi.data=na.omit(bmi.data)
 bmi.data=bmi.data%>%filter(bmi.data$Age>19)
 bmi.data$Gender=recode(bmi.data$Gender, "1" = "Male", "2" = "Female" )
 # RIDRETH1 (race, 1=mexican, 2=otherHispanic, 3= Non-Hispanic White,4=Non-Hispanic Black ,5=Other Race - Including Multi-Racial
 
 bmi.data$Race=recode(bmi.data$Race, "1" = "Mexican", "2" = "Other_Hispanic","3"="White","4"="Black","5"="Other" )
-# Classifying population to diabetes and non diabetes
+
+
+# Save an object to a file
+saveRDS(bmi.data, file = "bmi.data.rds")
+# Restore the object
+bmi.data=readRDS(file = "bmi.data.rds")
+
 
[…]

### 2021-03-18 Q_reg_plot2.R

@@ -1,36 +1,14 @@
-# Plot of quantile regression for BMI regressed on Gender, Age,Race,Statin_status
+# Plot of quantile regression for BMI regressed on Gender, Age,Race,Cholesterol_Drug_Use
 #Using bsplines
 require(quantreg)
 library(tidyverse)
 library(splines)
 
-bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
-
-#remove duplicated rows and remove na data.
-bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
- 
-bmi.data=data.frame(bmi.data$RIAGENDR,bmi.data$RIDAGEYR, bmi.data$RIDRETH1,bmi.data$BMXBMI,
-                    bmi.data$LBXTC,bmi.data$TCRx,bmi.data$LBXGLU,bmi.data$BMXWAIST)
-#bmi.data= na.omit(bmi.data[,c(5,6,9,29,33,43,32)])
-#bmi.data=bmi.data[bmi.data$bmi.data.diab_drug==2,]
-#bmi.data=na.omit(bmi.data[,c(1:7)])
-colnames(bmi.data) <- c("Gender","Age","Race","BMI","Total_chol" ,"Statin_status","Glu","waist_cir")
-bmi.data=na.omit(bmi.data)
-bmi.data=bmi.data%>%filter(bmi.data$Age>19)
-bmi.data$Gender=recode(bmi.data$Gender, "1" = "Male", "2" = "Female" )
-# RIDRETH1 (race, 1=mexican, 2=otherHispanic, 3= Non-Hispanic White,4=Non-Hispanic Black ,5=Other Race - Including Multi-Racial
-
-bmi.data$Race=recode(bmi.data$Race, "1" = "Mexican", "2" = "Other_Hispanic","3"="White","4"="Black","5"="Other" )
-
-
-# Save an object to a file
-saveRDS(bmi.data, file = "bmi.data.rds")
-# Restore the object
 bmi.data=readRDS(file = "bmi.data.rds")
- 
- 
-#formula <- Glu ~Gender+Age+Race+BMI+Statin_status+Age2+BMI2+Total_chol+Total_col2+Waist_cir 
-formula <- BMI ~Gender+Race+Statin_status+bs(Age,intercept=FALSE,df=5)+bs(Total_chol,intercept=FALSE,df=5)       
+
+
[…]

### 2021-03-18 ci_splin.R

@@ -1,4 +1,4 @@
- 
+
 #Marginal effect on BMI with splines
 #Plot for the confidence interval of BMI regressed on splines of Age, 
 #race, gender,and cholesterol medications use.
@@ -8,28 +8,31 @@ library(quantreg)
 library(splines)
 library(tidyverse)
 library(ggeffects)
+library(gridExtra)
 
-#memory.limit(size=56000)
-#attach(bmi.data)
+
+
+
 dat=readRDS(file = "bmi.data.rds")
 #dat=dat[dat$BMI<28,]
-dat=filter(dat,Statin_status!='9')
-#levels(dat$Statin_status) <- c('1','2')
-dat$Statin_status <- factor(dat$Statin_status)
+dat=filter(dat,Cholesterol_Drug_Use!='9')
+#levels(dat$Cholesterol_Drug_Use) <- c('1','2')
+dat$Cholesterol_Drug_Use <- factor(dat$Cholesterol_Drug_Use)
 dat$Age=as.numeric(dat$Age)
 
 #formula 1
-#formula=BMI ~ bs(Age, df = 5) + Race + Gender + Statin_status+Total_chol
+#formula=BMI ~ bs(Age, df = 5) + Race + Gender + Cholesterol_Drug_Use+Total_chol
 #formula 2
-#formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Statin_status
+#formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use
 # formula 3 
-#formula=BMI ~ Age+Age^2+Total_chol+ Total_chol^2+ Race + Gender + Statin_status
+#formula=BMI ~ Age+Age^2+Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use
 
 
 fit_rq=function(dat,index,tau){
-    if (index==1) {formula=BMI ~ bs(Age, df = 3) + Race + Gender + Statin_status}
-    else if(index ==2) {formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Statin_status}
-    else {formula=BMI ~ Age+Age^2+Total_chol+ Total_chol^2+ Race + Gender + Statin_status}
+    if (index==1) {formula=BMI ~ bs(Age, df = 3) + Race + Gender + Cholesterol_Drug_Use}
+    else if(index ==2) {formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use}
[…]

### 2021-03-18 exploratory-data-analysis_JRT.R

@@ -15,10 +15,12 @@ bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
 #remove duplicated rows and remove na data.
 bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
 
- 
-bmi.data= na.omit(data.frame(bmi.data$RIAGENDR,bmi.data$RIDAGEYR,bmi.data$RIDRETH1,bmi.data$BMXBMI,bmi.data$TCRx,bmi.data$LBXGLU)) 
-colnames(bmi.data) <- c("Gender","Age","Race","BMI","Statin_status","Glu")
 
+bmi.data= na.omit(data.frame(bmi.data$RIAGENDR,bmi.data$RIDAGEYR,bmi.data$RIDRETH1,bmi.data$BMXBMI,bmi.data$TCRx,bmi.data$LBXGLU)) 
+colnames(bmi.data) <- c("Gender","Age","Race","BMI","Cholesterol_Drug_Use","Glu")
+bmi.data=bmi.data[bmi.data$Age>19,]
+#Recoding
+#bmi.data$Cholesterol_Drug_Use=recode(bmi.data$Cholesterol_Drug_Use, "1" = "Yes", "0" = "No" )
 bmi.data$Gender=recode(bmi.data$Gender, "1" = "Male", "2" = "Female" )
 # RIDRETH1 (race, 1=mexican, 2=otherHispanic, 3= Non-Hispanic White,4=Non-Hispanic Black ,5=Other Race - Including Multi-Racial
 
@@ -42,13 +44,13 @@ Age_10 <- as.factor(temp)
 
 bmi.data <- cbind(bmi.data,Age_10)
 
- 
+
 # Saving on object in RData format
-save(bmi.data, file = "data.RData")
+save(bmi.data, file = "data.Rdata")
 
 
 ###  Classifying BMI Level.
- 
+
 BMI_bin=seq(1,length=nrow(bmi.data))
 temp=lapply(BMI_bin, function(x) ifelse(bmi.data$BMI[x]<=25,"normal",ifelse(bmi.data$BMI[x]<=30,"obes","ovrwieght")))
 temp=do.call(rbind,temp)
@@ -70,7 +72,7 @@ fig
 fig <- ggplot(bmi.data , aes(x  = Age_10)) +
     geom_bar(aes( fill = BMI__class  ) , position ="fill") +
[…]

### 2021-04-16 manuscript/manuscript.Rmd
update

@@
+ 
 ---
@@
 link_citations: true
+header-includes:
+    - \usepackage{setspace} 
+    - \usepackage{float}
+abstract: "My abstract"
+keywords: "My keywords"
+date: "`r format(Sys.time(), '%B %d, %Y')`"
 geometry: margin=1in
@@
 indent: true
-header-includes:
-    - \usepackage{setspace}\doublespacing
-    - \usepackage{float}
 ---
-
+\setstretch{4}
 \section{introduction}
 
-Body Mass Index (BMI) plays an important rule in predicting heart disease risk[@katbody].
-Our Goal is to estimate the trend in the $\tau$th quantile of  BMI using set of independent predictors.
-BMI departs normality because of the skewnes on the right and it is shown by using Box-cox transformation [@flegal1999].
-Estimation of underweight and overweight can be effected by the voilation of the normality.
-Quantile regression is a crucial tools used to estimate BMI with the dispersion of the association of predictors.
-We found that spline regressions produce different estimate than polynomial regressions.
-Quantile regression has many successful application in ecology where different factors interact in a complicated way that produce different variation of one factor for different levels of another variables[@cade2003].
+  High BMI has negative impact on public health.
+Due to high cost of obesity, it is crucial to get better understanding of the underlying risk factor for obesity.
+This can help decision makers to create a new regulation that help to prevent and to stop the dramatic increase in the BMI index.
 
-Approximately, 18 million deaths annually per year are caused by cardiovascular diseases(CVD) and similar to this number of nonfatal cardiovascular events [@hay2017gbd].
+  Body Mass Index (BMI) plays an important role in predicting heart disease risk[@katbody].
+Approximately, 18 million deaths annually per year are caused by cardiovascular diseases(CVD), and similar to this number of nonfatal cardiovascular events [@hay2017gbd].
 In 2011, annual costs for CVD and stroke were $\$320.1$ billion, which is more than cancer cost.
-This cost include \$195.6  billion in direct costs (healthcare costs), and cost of future productivity loss is  \$124.5 [@mozaffarian2015executive].
-Important factors that associated with CVD are high body mass index (BMI) and abnormal lipid ratio  [@yusuf2004effect],[@anderson1991].
-Lowering low-density lipoprotein (LDL) using statin or other drugs reduce risk of cardiovascular diseases even with population with no CVD  [@yusuf2016].
-Ferrieres at el.
-[@ferrieres2018] studied effect of BMI on the choice of lipid-lowering treatment.It is been found that statin intensity increases with high level of BMI($\rho=0.13$).
-It is known that diabetes is a risk factor for CVD, however, it is shown that elevated  glucose, prediabetes,is also a risk factor for CVD [@balkau2004prediction].
+This cost includes \$195.6  billion in direct costs (healthcare costs), and the cost of future productivity loss is  \$124.5 [@mozaffarian2015executive].
+Important factors associated with CVD are high body mass index (BMI) and abnormal lipid ratio  [@yusuf2004effect], [@anderson1991].
+Lowering low-density lipoprotein (LDL) by using statin or other drugs reduces the risk of cardiovascular diseases even with a population with no CVD  [@yusuf2016].
+Ferrieres et al.
+[@ferrieres2018] studied the effect of BMI on the choice of lipid-lowering treatment.
+It is been found that statin intensity increases with the high level of BMI($\rho=0.13$).
 
-Statin use  associates with high risk of elevating BMI level[@sugiyama2014].
-It is been shown that statin users consume 192 additional calories per day which cause gaining a 6 lb-to-11 lb in a year.
-Statin users gain 1.3 units in the BMI measure while non-staining users gains 0.4 unit  .Moreover, consumption of fat in statin users raised by 14.4%.
+Taking cholesterol drug medication  associates with a high risk of elevating BMI level.
+It is been shown that statin users consume 192 additional calories per day which causes gaining a 6 lb to 11 lb.
+in a year.
+Statin users gain 1.3 units in the BMI measure while non-staining users gain 0.4 unit.
+Moreover, consumption of fat in statin users raised by 14.4%[@sugiyama2014].
 
-Statin has negative impact on glucose level.
-The hazard ratio of a new onset diabetes in  normoglycemic statin users(HR 1.19,95% CI , 1.05 to 1.35) and in pre-diabetes (HR 1.24 95% CI , 1.11 to 1.38).
-On the other hand, overall mortality risks went down  in both normoglycemic (HR 0.70;
-95 % CI, 0.66 to 0.80) and in prediabetes patients (HR
-0.77, 95 % CI, 0.64 to 0.91) with statin use [@castro2016].
-For population with one or more risk factor for diabetes, statin use associate with 39% reduction in the primary end points (the hazard ratio (HR) 0.61), and a 28% (HR 1.28)increase in diabetes[@ridker2012].Pandya at el.[@pandya2015] suggested the dis-utility associated with taking a pill daily, statin price, and the risk of statin-induced diabetes negatively impacted the cost effectiveness of statin use recommendation.
+ Logistic regression helps us to find out the group that has a higher odd of obesity, and ordinary least squares (OLS) regression helps us to study the effects of predictors on the average mean of the response.
+For example, estimating the association of different factors like a lipid-lowering drug with the conditional mean of BMI using OLS or logistic regression model[@ferrieres2018].
+Both of these approaches do not give us insight into the predictor's effects on different quantiles of the responses.
 
-Several studies estimated the association of different factors like lipid-lowering drug  with the conditional mean of BMI using OLS or logistic regression model[@ferrieres2018].
-The drawback in this study is not considering the dispersion of the association of covariates with conditional distribution of the dependent variables, BMI.
+  Quantile regression is used to investigate the heterogeneity in the association of the $\tau$th quantile of BMI with a set of independent predictors, that is investigate the effects of a specific predictors on the various quantiles of the BMI.
+BMI departs normality because of the skewness on the right and left tails [@flegal1999].
+Estimation of underweight and overweight can be affected by the violation of normality.
+Quantile regression is a crucial tool used to estimate BMI with the dispersion of the association with predictors.
+
+  Quantile regression has many successful applications in ecology where different factors interact in a complicated way that produces different variations of one factor for different levels of another variable [@cade2003].
+The association between BMI and the set of predictors; low childhood socioeconomic position, high maternal weight, low childhood general cognition  is stronger in the upper end of BMI quantile.
+This trend  is found in the UK population[@bann2020].
+One cause of this heterogeneity is that risk factors may have stronger effect on patients with worse health, and these effects may diminishes when conditional mean of the BMI is studied.
+
+  We found that spline regressions produce a different estimate than polynomial regressions.
+Polynomial regression using the quadratic term of predictors forces the response to take convex or concave shape, see Figure 1.12 [@koenker2005].
+This is because the limit of quadratic functions approach $\pm\infty$ as $x\rightarrow\pm\infty.$ However, when we model the predictor as splines the response is not forced to take a specific shape.
+In the latter case, different polynomials are constructed for the different regions in the range of predictors.
 
  \section{Quantile Regression}
-Quantile regression is an important tool used to regress the dependent variable with high variance over the independent variables.
+Quantile regression is a tool used to regress the dependent variable with high variance over the independent variables.
 QR is developed to study the relationships between variables that have week or no-relationships between their means.
-One of the advantage of using QR over OLS is robust for outliers.
+One of the advantages of using QR over OLS is QR is robust for outliers.
 
-For a random variable $X$, the cumulative distribution function (CDF) is $$F(X)=P(X\leq x)$$, and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} $$ where $0<\tau<1$.
+For a random variable $X$, the cumulative distribution function (CDF) is $$F(X)=P(X\leq x),$$ and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} $$ where $0<\tau<1$.
 Let the loss function is defined by $$\rho_{\tau}(u)= u(\tau-I_{(u<0)})$$ where $I$ is the indicator function  [@koenker2005].
@@
 
-$E\rho_{\tau}(X-\hat{x})=(\tau-1)\int_{-\infty}^{\hat{x}} (x-\hat{x})dF(x)+\tau\int_{\hat{x}}^{-\infty} (x-\hat{x})dF(x).$
+$$E\rho_{\tau}(X-\hat{x})=(\tau-1)\int_{-\infty}^{\hat{x}} (x-\hat{x})dF(x)+\tau\int_{\hat{x}}^{-\infty} (x-\hat{x})dF(x).$$
 Differentiating with respect to $\hat{x}$, we get
@@
 =F(\hat{x})-\tau.$$
-Due to monotonicity of the cumulative distribution function, any solution that satisfies $\{x:F(x)=\tau \}$ is a minimizing for the expected loss function.
+Due to the monotonicity of the cumulative distribution function, any solution that satisfies $\{x:F(x)=\tau \}$ is a minimizing for the expected loss function.
 
@@
 \subsection{splines}
-   A continuous predictor can be linear, say $ X$, or nonlinear, say $X^2$ depends on the relationship with the response variable.
-Most of the relations between the responses and predictors variables are complicated to the point that linear regressions are not suitable to model these relationships[@bruce2017].
-For example, the response to different levels of drug doeses is not a linear relationship.
+   A continuous predictor can be linear, say $X$, or nonlinear, say $X^2$ depends on the relationship with the response variable.
+Most of the relations between the responses and predictors variables are complicated to the point that linear regressions are not suitable to model these relationships[@bruce2020].
+For example, the response to different levels of drug doses is not a linear relationship.
 Linear regressions can be generalized to deal with nonlinear effects.
-One approach is through including polynomial terms to regression equation.
+One approach is through including polynomial terms in the regression equation.
 This approach is called Polynomial regression.
@@
  One of the limitations of using polynomial regression is the curvature that can be captured is limited with low order terms.
-However, including higher order terms has negative impact on the model by introducing undesirable "wiggliness" in the regression equation.
+However, including higher-order terms has a negative impact on the model by introducing undesirable "wiggliness" in the regression equation.
 Another robust approach to model nonlinear relationships is splines.
-It is similar to a technique used by draftsman's in ploting curves.
-Spline is a process of constructing a set of  piecewise continuous
-polynomials that are smoothly connected at set of points in the range of predictor variable.
+It is similar to a technique used by draftsmen in plotting curves.
+The spline is a process of constructing a set of piece-wise continuous
+polynomials that are smoothly connected at a set of points in the range of the predictor variable.
 The connection points are called knots i.e.
 splines are used to smoothly interpolate between certain points.
-Let $a,b$ ,and $c$ are the end points of the $x$-axis intervals.
+Let $a,b$ ,and $c$ are the endpoints of the $x$-axis intervals.
 A smooth cubic spline function is defined by the following equation.
@@
 
- The independent variables in our model are gender, race, age, total cholesterol, Cholesterol drug uses (yes or no).
-All type of cholesterol drug are included including  statins.
+ The independent variables in our model are gender, race, age, total cholesterol, cholesterol drug use (yes or no).
+All types of cholesterol drugs are used including statins.
 The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.
@@
  The data used in this study is National Health and Nutrition Examination Survey data (NHANES)[@NHANES].
-The survey examines a nationally representative sample of U.S.
-population.It focuses on  variety of health and nutrition measurements.
+The survey examines a nationally representative sample of the U.S.
+population.
+It focuses on a variety of health and nutrition measurements.
 The survey data are released every two years cycle.
 In this study, we accumulated 6 cycles of NHANES data (2007–2018).
-We used
- two data files: One contains demographic variables, such as age, sex, race, income, etc, and the other contains data that are related to body measurements, such as BMI, head circumference, etc.
-These files are marged by using the respondent sequence number (SEQN)
- There are  around 12,000 records. We selected  population age between 20 and 80.
+We used two data files: One contains demographic variables, such as age, sex, race, income, etc., and the other contains data that are related to body measurements, such as BMI, head circumference, etc.
+These files are merged by using the respondent sequence number (SEQN)
+ There are around 12,000 records. We selected a population age between 20 and 80.
  BMI are classified into different categories according to underweight, 18.5 kg/m2; normal weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/m2; obese, 30 to 35 kg/m2; and very obese more than 35 kg/m2.
@@
 
+base_box_plot
+
+```{r box, out.width = "100%", fig.align = "center", fig.cap = "Illustration of data distribution using a box plot.
+The plot compares cholesterol drug users vs non-cholesterol drug users", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "base_box_plot.png"))) {
+    source(here::here("exploratory-data-analysis.R"))
+}
+knitr::include_graphics(here::here("images", "base_box_plot.png"))
+```
+
+Figure \@ref(fig:box) shows the association between age and BMI with respect to cholesterol drug is inconsistent.
+At the early age, the correlation is positive while at the middle age the correlation is almost flat, and at the old age the correlation is negative.
+Moreover, at low age cholesterol medications are  described only for a population with high BMI, but at a higher age, the difference in term of the BMI for a population that takes cholesterol medication and without cholesterol medication decreases until it diminishes as in the white population.
+The  heterogeneity can also be seen in gender ?, for the Hispanic female population, the cholesterol medication is taken by the population with lower BMI if compared to the population that does not take cholesterol medication.
 ```{r data, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
@@
 ```
-
-to cite figure #See Figure \@ref(fig:data)
-However,.
 
@@
 The resulting estimate of effects on conditional mean of BMI level may not reflect the size and nature of these effects on lower or upper quantile.
-For example, in the Figure \@ref(fig:resu1), the conditional mean shows the conditional mean effects of gender on glucose level is about 7.
-However, the disparity of the gender effects on lower tails is much smaller which is about 3 but the disparity is higher for the upper tail of the distribution somewhat larger than 10 mg/dL.
+For example, in Figure \@ref(fig:resu1), the conditional mean effect of gender on BMI level is about -1, that is on average male's BMI is less than a female's BMI by one unit.
+However, the disparity of the gender effects on lower tails is much larger which is about 1, but the disparity is lower for the upper tail of the distribution somewhat around -3 unit.
 
-From the OLS it is obvious statin users have on average  higher glucose levels if compared to non-statin users which is around 10 mg/dL.
-The disparity in glucose level for statin users vs non-statin users is negligible in the left tail, however, statin uses seems to be associated with a rather large effects on glucose levels somewhat larger than 55 mg/dL for the right quantile.
+From the OLS it is obvious cholesterol drug users have on average higher BMI levels if compared to non-cholesterol drug users which are around 1.75.
+The disparity in BMI level for cholesterol drug users vs non-cholesterol drug users is almost the same for different Quantiles.
+cholesterol drug use seems to be associated with rather large effects on BMI levels somewhat around 1.5 to 1.7.
 
@@
 
-```{r resu122, out.width = "80%", fig.align = "center", fig.cap = "Using Cubic splines", echo = FALSE}
+ Age effect modeled as a quadratic factor.
+The age effect is concave in general, see Figure \@ref(fig:resu3).
+At the lower quantile, BMI increases from age 20 to around age 50, and it starts to decrease after that.
+In the 55th quantile, the concavity is stronger at age 50 if compared to the left or right tail.
+The quadratic effect of age is reflected in the hyperbolic shape.
+However, the age effect modeled as b spline behaves in a different way.
+Age effect on BMI increases from age 20 to around age 36 and then start to decrease up to around age 63 then move up again and then decreases up to age 80, see Fig.\@ref(fig:resu33).
+The BMI trend in this modeling is close to the trend shown in [@chen2005] by using a complicated polynomial and log transformation for the response.
+
+```{r resu3, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic age effect on BMI leveles for four different quantiles of the conditional BMI distribution.
+The ", echo = FALSE}
 # Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "newfig111.png"))) {
+if (!file.exists(here::here("images", "p_age_effect.png"))) {
     source(here::here("exploratory-data-analysis_JRT.R"))
 }
-knitr::include_graphics(here::here("images", "newfig111.png"))
-```
-
- therefore
-```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
-# Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "newfig2.png"))) {
-    source(here::here("exploratory-data-analysis_JRT.R"))
-}
-knitr::include_graphics(here::here("images", "newfig2.png"))
-``` 
-So,
-
- Age effect modeled as a quadratic factor.
-The age effect  is linear in general, see Figure \@ref(fig:resu3).
-The slope for the  left quantile is lower than the slope of the right quantile.
-This can be interpreted as age effect tends to increase over the entire range of conditional distribution of glucose in faster rate for the higher quantile than in the left quantile.In other word, diabetes population have higher rate of change with respect to age if compared to non diabetes population.
-It was found that there is  a significantly correlation between glucose and age[@tsaousis2014].
-
-The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014],[@chang2011].
-They found that there is a positive correlation between the two groups.
-However, we found that
-
-```{r resu3, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic age effect on glucose leveles for four different quantiles of the conditional BMI distribution.
-The ", echo = FALSE}
-# Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "newfig3.png"))) {
-    source(here::here("exploratory-data-analysis_JRT.R"))
-}
-knitr::include_graphics(here::here("images", "newfig3.png"))
+knitr::include_graphics(here::here("images", "p_age_effect.png"))
 ```
 Using splines
-```{r, out.width = "80%", fig.align = "center", fig.cap = "Age effect modeled using bsplines ", echo = FALSE}
+```{r resu33, out.width = "80%", fig.align = "center", fig.cap = "Age effect modeled using bsplines ", echo = FALSE}
 # Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "effect_Age_22.png"))) {
-    source(here::here("exploratory-data-analysis_JRT.R"))
-}
-knitr::include_graphics(here::here("images", "effect_Age_22.png"))
+if (!file.exists(here::here("images", "s-age_effect.png")))
+knitr::include_graphics(here::here("images", "s_age_effect.png"))
 ```
@@
 
-```{r resu4, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic cholestrol effect on glucose leveles for four different quantiles of the conditional glucose distribution.
+```{r resu4, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic cholestrol effect on BMI leveles for four different quantiles of the conditional BMI distribution.
 The ", echo = FALSE}
 # Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "newfig4.png"))) {
+if (!file.exists(here::here("images", "p_TC_effect.png"))) {
     source(here::here("exploratory-data-analysis_JRT.R"))
 }
-knitr::include_graphics(here::here("images", "newfig4.png"))
+knitr::include_graphics(here::here("images", "p_TC_effect.png"))
 ```
@@
 
-```{r resu33, out.width = "80%", fig.align = "center", fig.cap = " Marginal Cholestrol effect modeled as B splines.  The ", echo = FALSE}
+```{r resu330, out.width = "80%", fig.align = "center", fig.cap = " Illustration of marginal cholestrol effect modeled as B splines.  The ", echo = FALSE}
 # Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "effect_TC_22.png"))) {
-    source(here::here("exploratory-data-analysis_JRT.R"))
-}
-knitr::include_graphics(here::here("images", "effect_TC_22.png"))
+if (!file.exists(here::here("images", "s_TC_effect")))  
+knitr::include_graphics(here::here("images", "s_TC_effect.png"))
 ```
 
-Quadratic effect of total cholesterol on the conditional distribution of glucose is convex.
-At the lower tail, decreasing glucose level by somewhat around 1.4 up to around 180 Cholesterol level.
-Then, started to increase glucose levels after TC beyond 180.
-At higher quantile, the reverse in the cholesterol effects is shifted to higher cholesterol levels which around 200, Figure \@ref(fig:resu4).
+The quadratic effect of total cholesterol on the conditional distribution of BMI is convex.
+At the lower tail, the correlation is positive that is as cholesterol increases the BMI increases.
+decreasing glucose level by somewhat around 1.4 up to around 180 Cholesterol level.
+However, at higher quantile the association become negative that is as cholesterol level increases the BMI decreases, see  Figure \@ref(fig:resu4).
 The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014],[@chang2011].
@@
 
-So,
+On the other hand, when we use splines to modeled the total cholesterol, there is a huge difference in the shape of the association expect at the higher quantile there is some similarity.
+At the lower quantile, there is negative correlation between total cholesterol and BMI for total cholesterol in the range less than 160, then the correlation becomes positive for total cholesterol in the range of (170, 250).
+at the 55th quantile, the correlation is positive for low cholesterol level and then becomes almost flat for the rest cholesterol values.
+At a higher qunatile, the correlation becomes negative at cholesterol level in the range (160,300), see Figure \@ref(resu330).
 
 \section{Conclusion}
- Multivariate quantile regression is used to study effects of different variables on fasting glucose level.
-Our study showed that people who have TC levels around 190 mg/dL have lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile the optimal cholesterol level is around 200 mg/dL.
-Moreover, Statin effects on glucose at lower quantile is very small if compared to upper quantile.
+ Multivariate quantile regression is used to study the effects of different risk factors on the BMI levels.
+Cholesterol drug effects on BMI is negligible at low quantile but at higher quantile cholesterol medication  effects on BMI is larger.
+This study showed that the association between BMI and total cholesterol is varying with repect to different quantile.
+
+ tota people who have TC levels around 190 mg/dL have the lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile, the optimal cholesterol level is around 200 mg/dL.
+Moreover,
+
+It is recommended to investigate why the effect estimates are varying across different BMI quantiles.
+
 \newpage
 \section{References}
+---
+nocite: '@*'
+...

### 2021-04-16 manuscript/manuscript2.Rmd
update

@@
 if (!file.exists(here::here("images", "newfig11.png"))) {
-    source(here::here("exploratory-data-analysis_JRT.R"))
+    source(here::here("Q_reg_plot2.R"))
 }

### 2021-04-16 ci_splin.R

@@ -31,7 +31,8 @@ dat$Age=as.numeric(dat$Age)
 fit_rq=function(dat,index,tau){
     if (index==1) {formula=BMI ~ bs(Age, df = 3) + Race + Gender + Cholesterol_Drug_Use}
     else if(index ==2) {formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use}
-    else {formula=BMI ~ Age+Age^2+Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use}
+    else if (index==3) {formula=BMI ~ Age+Age^2+Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use}
+    else{formula=BMI ~ Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use}
     message("model.matrix")
     X <- model.matrix(formula,data=dat)
     qr_fit_dat <- rq( BMI ~ X - 1, data=dat, tau = tau)
@@ -59,10 +60,13 @@ dat_pred_ready=function(dat,index,tau){
     }else if(index==2){
         dat_pred <- data.frame(expand.grid(x5_pred, x2_pred, x3_pred, x4_pred))
         names(dat_pred) <- c("Total_chol", "Race", "Gender", "Cholesterol_Drug_Use" )
-    }else { message(" pred")
+    }else if(index==3) { message(" pred")
         dat_pred <- data.frame(expand.grid(age_pred, x2_pred, x3_pred, x4_pred,x5_pred))
         names(dat_pred) <- c( "Age","Race", "Gender", "Cholesterol_Drug_Use","Total_chol" )
-    }
+    } else{
+        dat_pred <- data.frame(expand.grid(age_pred, x2_pred, x3_pred, x4_pred,x5_pred))
+        names(dat_pred) <- c( "Age","Race", "Gender", "Cholesterol_Drug_Use","Total_chol" )
+        }
     
     
     dat_pred$Gender=recode(dat_pred$Gender, "1" = "Male", "2" = "Female" )
@@ -75,8 +79,10 @@ dat_pred_ready=function(dat,index,tau){
         
     }else if(index==2){
         X_pred <- model.matrix(~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use,data=dat_pred)
-    }else { message("pred.model.matrix")
+    }else if (index==3) { message("pred.model.matrix")
[…]

### 2021-04-16 exploratory-data-analysis_JRT.R

@@ -10,7 +10,7 @@ library(quantreg)
 library(splines)
 
 
-bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
+bmi.data<- read.csv(here::here("BMI/data", "ldl2.csv"),header=TRUE, sep=",")
 
 #remove duplicated rows and remove na data.
 bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
@@ -78,7 +78,7 @@ fig
 
 
 
-png(file = here::here("images", "exploratory.png"),
+png(file = here::here("BMI/images", "exploratory.png"),
     res = 400, height = 9, width = 16, units = "in")
 print(fig)
 dev.off()
@@ -115,7 +115,7 @@ Age_10 <- as.factor(temp)
 dat <- cbind(dat,Age_10)
 dat=na.omit(dat)
 
-png(file = here::here("images", "base_box_plot.png"),
+png(file = here::here("BMI/images", "base_box_plot.png"),
     res = 400, height = 14, width = 20, units = "in")
 
 p<-ggplot(dat, aes(x=Age_10, y=BMI, color=Cholesterol_Drug_Use)) +
@@ -149,7 +149,7 @@ fig3=ggplot(dat, aes(Age ,BMI, group = Cholesterol_Drug_Use)) +
     facet_grid(Gender ~ Type_glu)+
     theme_bw()+
     ggtitle("90% Quatile")
-png(file = here::here("images", "quant90.png"),
+png(file = here::here("BMI/images", "quant90.png"),
     res = 400, height = 9, width = 16, units = "in")
 print(fig3)
 dev.off()
@@ -187,30 +187,30 @@ X_pred <- model.matrix( ~ bs(Age, df = 4) + Race + Gender+ Cholesterol_Drug_Use,
 
 
 
-dat_prediction <- list(X = X_pred)
-preds <- predict(qr_fit_dat, newdata =dat_prediction, interval = "confidence")
-dat_pred$preds  <- preds[, 1]
-dat_pred$lower  <- preds[, 2]
-dat_pred$higher <- preds[, 3]
-
-png(file = here::here("images", "exploratory2.png"),
-    res = 400, height = 9, width = 16, units = "in")
-fig2=dat_pred %>%
-    ggplot(aes(x = Age, y = preds, color = Cholesterol_Drug_Use)) +
-    geom_line() +
[…]

### 2021-04-16 ci_splin.R
update

@@ -104,6 +104,7 @@ dat_pred=dat_pred_ready(dat,index =1 ,tau =0.9 )
 dat_pred$Cholesterol_Drug_Use=recode(dat_pred$Cholesterol_Drug_Use, "0" = "No", "1" = "Yes" )
 
 ###############################################################################4
+
 fig2=dat_pred %>%
     ggplot(aes(x = Age, y = pred, color = Cholesterol_Drug_Use)) +
     geom_line() +
@@ -144,6 +145,32 @@ fig3=dat_pred %>%filter(Total_chol<375)%>%
 png(file = here::here("images", "TC_splin.png"),
     res = 400, height = 9, width = 16, units = "in")
 print(fig3) 
+dev.off()
+
+###########################
+
+dat_pred=dat_pred_ready(dat,index =4 ,tau =0.9 )
+
+dat_pred$Cholesterol_Drug_Use=recode(dat_pred$Cholesterol_Drug_Use, "0" = "No", "1" = "Yes" )
+
+# plot for splines on total cholestrol
+fig4=dat_pred %>%filter(Total_chol<375)%>%
+    ggplot(aes(x = Total_chol, y = pred, color = Cholesterol_Drug_Use)) +
+    geom_line() +
+    #geom_quantile(formula = y ~ bs(x,intercept=FALSE,df=5), quantiles = 0.25)+
+    geom_ribbon(aes(x =Total_chol  , ymin = lower, ymax = higher, fill = Cholesterol_Drug_Use), alpha = 0.1) +
+    scale_color_viridis_d(end = 0.7) +
+    scale_fill_viridis_d(end = 0.7)+
+    #ylim(c(30,70))+
+    xlim(c(100,375))+
+    theme_bw(base_size = 15)+
+    #geom_point(data=dat, aes(x=Total_chol,y=BMI),inherit.aes = FALSE,alpha=0.05)+
+    facet_grid(Race~Gender)
+
+
+png(file = here::here("images", "Total_chol_poly.png"),
+    res = 400, height = 9, width = 16, units = "in")
+print(fig4) 
 dev.off()
 
 

### 2021-04-16 manuscript/manuscript.Rmd
update

@@
 header-includes:
-    - \usepackage{setspace} 
+    - \usepackage{setspace}\doublespacing 
     - \usepackage{float}
@@
 ---
-\setstretch{4}
+<!-- \setstretch{4} -->
 \section{introduction}
@@
 \subsection{splines}
-   A continuous predictor can be linear, say $X$, or nonlinear, say $X^2$ depends on the relationship with the response variable.
+   A continuous predictor can be modeled as linear, say $X$, or nonlinear term, say $X^2$ depends on the relationship with the response variable.
 Most of the relations between the responses and predictors variables are complicated to the point that linear regressions are not suitable to model these relationships[@bruce2020].
@@
 The  heterogeneity can also be seen in gender ?, for the Hispanic female population, the cholesterol medication is taken by the population with lower BMI if compared to the population that does not take cholesterol medication.
+
 ```{r data, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
@@
 
-```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+```{r, out.width = "80%", fig.align = "center", fig.cap = "A 90th quantile of BMI ploted with repect to age.
+The population grouped with repect gender and fasting blood glucose level: prediabetes nad diabetes", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 ```
+
 \section{Results}
@@
 
-```{r resu1, out.width = "100%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+```{r resu1, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted f for fifferent marginal effects. The predictors modeled using quadratic terms ", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 
-```{r resu12, out.width = "100%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+```{r resu12, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted f for fifferent marginal effects. The predictors modeled using splines ", echo = FALSE}
 # Created by file exploratory-data-analysis.R

### 2021-04-16 manuscript/manuscript2.Rmd
update

@@
 
-Least square method expresses conditional mean of y given x as $\mu(x)=x^T\beta$ and it solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.$$ Quantile regression expresses conditional quantile function $Q_y(\tau|x)=x^T \beta ({\tau)}$ and solve $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.$$This minimization problem can be reformulated to a linear programming problem $$ \underset{\beta\in \mathcal{R}^p}{\text{min}} $$
+Least square method expresses conditional mean of y given x as $\mu(x)=x^T\beta$ and it solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.$$ Quantile regression expresses conditional quantile function $Q_y(\tau|x)=x^T \beta ({\tau)}$ and solve $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.$$This minimization problem can be reformulated to a linear programming problem
+
+<!-- $$ \underset{\beta\in \mathcal{R}^p}{\text{min}} $$ -->
 
@@
 
-```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
-# Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "exploratory2.png"))) {
-    source(here::here("exploratory-data-analysis_JRT.R"))
-}
-knitr::include_graphics(here::here("images", "exploratory2.png"))
-```
-
-So,
-
-```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+```{r, out.width = "80%", fig.align = "center", fig.cap = "A 90th quantile of BMI ploted with repect to age.
+The population grouped with repect gender and fasting blood glucose level: prediabetes nad diabetes", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 
-```{r resu12, out.width = "100%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
+```{r resu12, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted f for fifferent marginal effects. The predictors modeled using splines ", echo = FALSE}
 # Created by file exploratory-data-analysis.R
 if (!file.exists(here::here("images", "newfig11.png"))) {
-    source(here::here("Q_reg_plot2.R"))
+    source(here::here("exploratory-data-analysis_JRT.R"))
 }
 knitr::include_graphics(here::here("images", "newfig11.png"))
-```
-
-```{r resu122, out.width = "80%", fig.align = "center", fig.cap = "Using Cubic splines", echo = FALSE}
-# Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "newfig111.png"))) {
-    source(here::here("exploratory-data-analysis_JRT.R"))
-}
-knitr::include_graphics(here::here("images", "newfig111.png"))
 ```
@@
 # Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "p_age_effect.png"))) {
-    source(here::here("exploratory-data-analysis_JRT.R"))
+if (!file.exists(here::here("images", "Age_poly.png"))) {
+    source(here::here("ci_splin.R"))
 }
-knitr::include_graphics(here::here("images", "p_age_effect.png"))
+knitr::include_graphics(here::here("images", "Age_poly.png"))
 ```
@@
 # Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "s-age_effect.png")))
-knitr::include_graphics(here::here("images", "s_age_effect.png"))
+if (!file.exists(here::here("images", "Age_splin.png")))
+knitr::include_graphics(here::here("images", "Age_splint.png"))
 ```
 
-Using splines
-
-```{r resu33g, out.width = "80%", fig.align = "center", fig.cap = "Age effect modeled using bsplines, ggplot plot ", echo = FALSE}
-# Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "Age_splin.png"))) {
-
-}
-knitr::include_graphics(here::here("images", "Age_splin.png"))
-```
-
-\ref{fig:resu33g}
 Marginal quadratic cholesterol effect
@@
 # Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "p_TC_effect.png"))) {
-    source(here::here("exploratory-data-analysis_JRT.R"))
+if (!file.exists(here::here("images", "Total_chol_poly.png"))) {
+    source(here::here("ci_splin.R"))
 }
-knitr::include_graphics(here::here("images", "p_TC_effect.png"))
+knitr::include_graphics(here::here("images", "Total_chol_poly.png"))
 ```
@@
 ```{r resu330, out.width = "80%", fig.align = "center", fig.cap = " Illustration of marginal cholestrol effect modeled as B splines.  The ", echo = FALSE}
-# Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "s_TC_effect")))  
-knitr::include_graphics(here::here("images", "s_TC_effect.png"))
-```
-
-```{r resu3330, out.width = "80%", fig.align = "center", fig.cap = " Illustration of marginal cholestrol effect modeled as B splines using ggplot.  The ", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 \section{References}
+---
+nocite: '@*'
+...

### 2021-04-16 Q_reg_plot.R

@@ -76,7 +76,7 @@ cols <- c("black","red", "blue","LightSkyBlue1", "green", "light pink")
 #pdf("newfig.pdf",width=8.5,height=7)
 #pdf("./images/newfig.pdf",width=15,height=13)
 png(file = here::here("images", "newfig.png"),
-    res = 400, height = 9, width = 16, units = "in")
+    res = 400, height = 16, width = 16, units = "in")
 p <- dim(fit3)[1]
 blab <- c("Intercept","Male ","RaceMexican", "RaceOther", "RaceOther_Hispanic ", "White ", " Cholesterol_Drug_Use","Age","Age^2","Total cholesterol","Total cholestrol^2")
 

### 2021-04-16 Q_reg_plot2.R

@@ -36,7 +36,7 @@ cols <- c("black","red", "blue","LightSkyBlue1", "green", "light pink")
 #pdf("newfig.pdf",width=8.5,height=7)
 #pdf("./images/newfig.pdf",width=15,height=13)
 png(file = here::here("images", "newfig11.png"),
-    res = 400, height = 9, width = 16, units = "in")
+    res = 400, height = 16, width = 16, units = "in")
 p <- dim(fit3)[1]
 #blab <- c("Intercept","Male ","Age","RaceMexican", "RaceOther", "RaceOther_Hispanic ", "White ", "BMI", " Cholesterol_Drug_Use","Age Suqared","BMI^2","Total cholesterol","Total cholestrol^2","Waist Circumference")
 blab <- c("Intercept","Male ","RaceMexican", "RaceOther", "RaceOther_Hispanic ", "White ", " Cholesterol_Drug_Use" ,

### 2021-04-16 ci_splin.R

@@ -147,6 +147,34 @@ png(file = here::here("images", "TC_splin.png"),
 print(fig3) 
 dev.off()
 
+
+########################
+
+dat_pred=dat_pred_ready(dat,index =3 ,tau =0.9 )
+
+dat_pred$Cholesterol_Drug_Use=recode(dat_pred$Cholesterol_Drug_Use, "0" = "No", "1" = "Yes" )
+
+# plot for splines on total cholestrol
+fig3=dat_pred %>%filter(Total_chol<375)%>%
+    ggplot(aes(x = Age, y = pred, color = Cholesterol_Drug_Use)) +
+    geom_line() +
+    #geom_quantile(formula = y ~ bs(x,intercept=FALSE,df=5), quantiles = 0.25)+
+    geom_ribbon(aes(x =Total_chol  , ymin = lower, ymax = higher, fill = Cholesterol_Drug_Use), alpha = 0.1) +
+    scale_color_viridis_d(end = 0.7) +
+    scale_fill_viridis_d(end = 0.7)+
+    #ylim(c(30,70))+
+    xlim(c(100,375))+
+    theme_bw(base_size = 15)+
+    #geom_point(data=dat, aes(x=Total_chol,y=BMI),inherit.aes = FALSE,alpha=0.05)+
+    facet_grid(Race~Gender)
+
+
+png(file = here::here("images", "Age_poly.png"),
+    res = 400, height =9, width = 16, units = "in")
+print(fig3) 
+dev.off()
+
+
 ###########################
 
 dat_pred=dat_pred_ready(dat,index =4 ,tau =0.9 )
@@ -178,110 +206,110 @@ dev.off()
 
 
 
-
-################################################################################################
-
-fit <- rq(BMI ~ bs(Age,df=4)+Race+Gender+Cholesterol_Drug_Use+bs(Total_chol,df=4),0.9 ,data = dat)
-#fit <- rq(BMI ~ Age+Race+Gender+Cholesterol_Drug_Use+Total_chol,0.5 ,data = dat)
-
-
-
-library(ggplot2)
-mydf <- ggpredict(fit, terms ="Total_chol[all]")
-mydf=cbind(mydf,dat)
-ggplot(mydf, aes(x, y=predicted)) +
-    geom_line() +
[…]

### 2021-04-17 manuscript/manuscript2.Rmd
update

@@
 
-base_box_plot
-
 ```{r box, out.width = "100%", fig.align = "center", fig.cap = "Illustration of data distribution using a box plot.
@@
 ```
- So,
 
@@
 
-Marginal quadratic cholesterol effect
-
-```{r resu4, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic cholestrol effect on BMI leveles for four different quantiles of the conditional BMI distribution.
-The ", echo = FALSE}
+```{r resu4, out.width = "80%", fig.align = "center", fig.cap = "Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled as  quadratic .", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 
-Splines modeling
-
-```{r resu330, out.width = "80%", fig.align = "center", fig.cap = " Illustration of marginal cholestrol effect modeled as B splines.  The ", echo = FALSE}
+```{r resu330, out.width = "80%", fig.align = "center", fig.cap = " Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled  as B splines. ", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 
- tota people who have TC levels around 190 mg/dL have the lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile, the optimal cholesterol level is around 200 mg/dL.
+ total people who have TC levels around 190 mg/dL have the lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile, the optimal cholesterol level is around 200 mg/dL.
 Moreover,

### 2021-04-17 ci_splin.R

@@ -31,7 +31,7 @@ dat$Age=as.numeric(dat$Age)
 fit_rq=function(dat,index,tau){
     if (index==1) {formula=BMI ~ bs(Age, df = 3) + Race + Gender + Cholesterol_Drug_Use}
     else if(index ==2) {formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use}
-    else if (index==3) {formula=BMI ~ Age+Age^2+Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use}
+    else if (index==3) {formula=BMI ~ Age+Age^2+ Race + Gender + Cholesterol_Drug_Use}
     else{formula=BMI ~ Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use}
     message("model.matrix")
     X <- model.matrix(formula,data=dat)
@@ -80,7 +80,7 @@ dat_pred_ready=function(dat,index,tau){
     }else if(index==2){
         X_pred <- model.matrix(~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use,data=dat_pred)
     }else if (index==3) { message("pred.model.matrix")
-        X_pred <- model.matrix(~Age+Age^2+Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use,data=dat_pred)
+        X_pred <- model.matrix(~Age+Age^2+ Race + Gender + Cholesterol_Drug_Use,data=dat_pred)
     } else{X_pred <- model.matrix(~Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use,data=dat_pred)
     
     }
@@ -155,15 +155,14 @@ dat_pred=dat_pred_ready(dat,index =3 ,tau =0.9 )
 dat_pred$Cholesterol_Drug_Use=recode(dat_pred$Cholesterol_Drug_Use, "0" = "No", "1" = "Yes" )
 
 # plot for splines on total cholestrol
-fig3=dat_pred %>%filter(Total_chol<375)%>%
+fig3=dat_pred %>% 
     ggplot(aes(x = Age, y = pred, color = Cholesterol_Drug_Use)) +
     geom_line() +
     #geom_quantile(formula = y ~ bs(x,intercept=FALSE,df=5), quantiles = 0.25)+
[…]

### 2021-04-23 manuscript/manuscript.tex
update

--- 2020-11-09 manuscript/manuscript.tex
@@
-\documentclass[]{article}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  12pt,
+]{article}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
+\IfFileExists{microtype.sty}{% use microtype if available
   \usepackage[]{microtype}
@@
 }{}
-\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
-\usepackage[unicode=true]{hyperref}
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \hypersetup{
-            pdftitle={BMI-manuscript},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  pdftitle={Quantile Regression Analysis for Statin Effects on Body mass Index},
+  pdfkeywords={My keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
 \usepackage{longtable,booktabs}
-% Fix footnotes in tables (requires footnote package)
-\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 \setcounter{secnumdepth}{5}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+\usepackage{setspace}\doublespacing
+\usepackage{float}
 
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-\title{BMI-manuscript}
+\title{Quantile Regression Analysis for Statin Effects on Body mass Index}
 \author{}
-\date{\vspace{-2.5em}}
+\date{\vspace{-2.5em}April 22, 2021}
 
@@
 \maketitle
+\begin{abstract}
+My abstract
+\end{abstract}
 
@@
 
-Body Mass Index (BMI) plays an important rule in predicting heart
-disease risk(Katzmarzyk et al. 2012). Our goal is to compare 90th
-quatile regrission for BMI in Diabtese and prediabtes population.
+High BMI has negative impact on public health.
+Due to high cost of obesity, it is crucial to get better understanding of the underlying risk factor for obesity.
+This can help decision makers to create a new regulation that help to prevent and to stop the dramatic increase in the BMI index.
 
-(Van de Kassteele et al. 2012)
+Body Mass Index (BMI) plays an important role in predicting heart disease risk(Katzmarzyk et al.
+2012).
+Approximately, 18 million deaths annually per year are caused by cardiovascular diseases(CVD), and similar to this number of nonfatal cardiovascular events (Hay et al.
+2017).
+In 2011, annual costs for CVD and stroke were \(\$320.1\) billion, which is more than cancer cost.
+This cost includes \$195.6 billion in direct costs (healthcare costs), and the cost of future productivity loss is \$124.5 (Mozaffarian et al.
+2015).
+Important factors associated with CVD are high body mass index (BMI) and abnormal lipid ratio (Yusuf et al.
+2004), (Anderson et al.
+1991).
+Lowering low-density lipoprotein (LDL) by using statin or other drugs reduces the risk of cardiovascular diseases even with a population with no CVD (Yusuf et al.
+2016).
+Ferrieres et al.~(Ferrières et al.
+2018) studied the effect of BMI on the choice of lipid-lowering treatment.
+It is been found that statin intensity increases with the high level of BMI(\(\rho=0.13\)).
+\begin{equation}
+y_{i}=  
+ \left\{
+\begin{array}{ll}
+ \beta_{01}+\beta_{11}x_i+\beta_{21}x_i^2+ \beta_{31}x_i^3+\eps_i & \mbox{if } x_i< c \\
+ \beta_{02} & \mbox{if } x_i \geq c
+\end{array}
+\right.
+\end{equation}
+Taking cholesterol drug medication associates with a high risk of elevating BMI level.
+It is been shown that statin users consume 192 additional calories per day which causes gaining a 6 lb to 11 lb.
+in a year.
+Statin users gain 1.3 units in the BMI measure while non-staining users gain 0.4 unit.
+Moreover, consumption of fat in statin users raised by 14.4\%(Sugiyama et al.
+2014).
 
-\section{methods}
+Logistic regression helps us to find out the group that has a higher odd of obesity, and ordinary least squares (OLS) regression helps us to study the effects of predictors on the average mean of the response.
+For example, estimating the association of different factors like a lipid-lowering drug with the conditional mean of BMI using OLS or logistic regression model(Ferrières et al.
+2018).
+Both of these approaches do not give us insight into the predictor's effects on different quantiles of the responses.
 
-prevalence and incidence as a function of age (18 -- 84 years in 1-year
-intervals), race/ethnicity (non-Hispanic white, non-Hispanic black,
-Hispanic, or other), sex, and BMI (underweight, 18.5 kg/m2; normal
-weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/ m2; obese, 30 to 35
-kg/m2; and very From the figure we see
+Quantile regression is used to investigate the heterogeneity in the association of the \(\tau\)th quantile of BMI with a set of independent predictors, that is investigate the effects of a specific predictors on the various quantiles of the BMI.
+BMI departs normality because of the skewness on the right and left tails (Flegal 1999).
+Estimation of underweight and overweight can be affected by the violation of normality.
+Quantile regression is a crucial tool used to estimate BMI with the dispersion of the association with predictors.
 
-\section{Quantile regression}
+Quantile regression has many successful applications in ecology where different factors interact in a complicated way that produces different variations of one factor for different levels of another variable (Cade and Noon 2003).
+The association between BMI and the set of predictors; low childhood socioeconomic position, high maternal weight, low childhood general cognition is stronger in the upper end of BMI quantile.
+This trend is found in the UK population(Bann, Fitzsimons, and Johnson 2020).
+One cause of this heterogeneity is that risk factors may have stronger effect on patients with worse health, and these effects may diminishes when conditional mean of the BMI is studied.
 
-Quantile regression is an important tool used to regress the dependent
-variable with high variance over the independent variables.
+We found that spline regressions produce a different estimate than polynomial regressions.
+Polynomial regression using the quadratic term of predictors forces the response to take convex or concave shape, see Figure 1.12 (Koenker 2005).
+This is because the limit of quadratic functions approach \(\pm\infty\) as \(x\rightarrow\pm\infty.\) However, when we model the predictor as splines the response is not forced to take a specific shape.
+In the latter case, different polynomials are constructed for the different regions in the range of predictors.
 
-For a random variable \(X\), the comulative distrubution function (CDF)
-is \[F(X)=P(X\leq x)\], and the \(\tau\)th quantile of \(X\) is defined
-by \[ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} \] where \(0<\tau<1\)
+\section{Quantile Regression}
 
-\section{Data}\label{data}
+Quantile regression is a tool used to regress the dependent variable with high variance over the independent variables.
+QR is developed to study the relationships between variables that have week or no-relationships between their means.
+One of the advantages of using QR over OLS is QR is robust for outliers.
 
-The data used in this study is National Health and Nutrition Examination
-Survey data (NHANES)(Disease Control and (CDC) 2018)
+For a random variable \(X\), the cumulative distribution function (CDF) is \[F(X)=P(X\leq x),\] and the \(\tau\)th quantile of \(X\) is defined by \[ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} \] where \(0<\tau<1\).
+Let the loss function is defined by \[\rho_{\tau}(u)= u(\tau-I_{(u<0)})\] where \(I\) is the indicator function (Koenker 2005).
+The quantile estimator is the value that minimizes the expected loss function
+
+\[E\rho_{\tau}(X-\hat{x})=(\tau-1)\int_{-\infty}^{\hat{x}} (x-\hat{x})dF(x)+\tau\int_{\hat{x}}^{-\infty} (x-\hat{x})dF(x).\]
+Differentiating with respect to \(\hat{x}\), we get
+\[ 0  =(\tau-1)\int_{-\infty}^{\hat{x}} dF(x)+\tau\int_{\hat{x}}^{-\infty} dF(x)
+=F(\hat{x})-\tau.\]
+Due to the monotonicity of the cumulative distribution function, any solution that satisfies \(\{x:F(x)=\tau \}\) is a minimizing for the expected loss function.
+
+Least square method expresses conditional mean of y given x as \(\mu(x)=x^T\beta\) and it solves \[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.\] Quantile regression expresses conditional quantile function \(Q_y(\tau|x)=x^T \beta ({\tau)}\) and solve \[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.\]This minimization problem can be reformulated to a linear programming problem \[ \underset{\beta\in \mathcal{R}^p}{\text{min}} \]
+
+\subsection{Quantile Regression Technique }
+
+\subsection{splines}
+
+A continuous predictor can be modeled as linear, say \(X\), or nonlinear term, say \(X^2\) depends on the relationship with the response variable.
+Most of the relations between the responses and predictors variables are complicated to the point that linear regressions are not suitable to model these relationships(Bruce, Bruce, and Gedeck 2020).
+For example, the response to different levels of drug doses is not a linear relationship.
+Linear regressions can be generalized to deal with nonlinear effects.
+One approach is through including polynomial terms in the regression equation.
+This approach is called Polynomial regression.
+The mathematical model for \(n\) degree polynomial regression is shown in the Eq\eqref{non}
+\begin{equation}\label{non}
+ y=\beta_0+\beta_1 X+\beta_2 X^2+\cdots+\beta_nX^n.
+ \end{equation}
+
+One of the limitations of using polynomial regression is the curvature that can be captured is limited with low order terms.
+However, including higher-order terms has a negative impact on the model by introducing undesirable ``wiggliness'' in the regression equation.
+Another robust approach to model nonlinear relationships is splines.
+It is similar to a technique used by draftsmen in plotting curves.
+The spline is a process of constructing a set of piece-wise continuous
+polynomials that are smoothly connected at a set of points in the range of the predictor variable.
+The connection points are called knots i.e.~splines are used to smoothly interpolate between certain points.
+Let \(a,b\) ,and \(c\) are the endpoints of the \(x\)-axis intervals.
+A smooth cubic spline function is defined by the following equation.
+\begin{equation}
+f(X)=X\beta=\beta_{0}+\beta_{1}X+\beta_2X^2+\beta_{3}X^{3}+\beta_{4}(X-a)_{+}^3+\beta_{5}(X-b)_{+}^3+\beta_6(X-c)_{+}^3,
+\end{equation}
+
+where \[(u)_{+}=  
+ \left\{
+\begin{array}{ll}
+u  & \mbox{if } u > 0 \\
+0 & \mbox{if } u \leq 0
+\end{array}
+\right. \]
+
+\section{Methods}
+
+A multivariate quantile regression model is used to assess the characteristics of the association variability in different quantiles of the conditional distribution of the body mass index.
+
+The independent variables in our model are gender, race, age, total cholesterol, cholesterol drug use (yes or no).
+All types of cholesterol drugs are used including statins.
+The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.
+
+\section{Numerical Example}
+\subsection{Data}
+
+The data used in this study is National Health and Nutrition Examination Survey data (NHANES)(Disease Control and (CDC) 2018).
+The survey examines a nationally representative sample of the U.S.
+population.
+It focuses on a variety of health and nutrition measurements.
+The survey data are released every two years cycle.
+In this study, we accumulated 6 cycles of NHANES data (2007--2018).
+We used two data files: One contains demographic variables, such as age, sex, race, income, etc., and the other contains data that are related to body measurements, such as BMI, head circumference, etc.
+These files are merged by using the respondent sequence number (SEQN)
+There are around 12,000 records. We selected a population age between 20 and 80.
+BMI are classified into different categories according to underweight, 18.5 kg/m2; normal weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/m2; obese, 30 to 35 kg/m2; and very obese more than 35 kg/m2.
+
+\begin{longtable}[]{@{}lcr@{}}
+\toprule
+Syntax & Male & Female\tabularnewline
+\midrule
+\endhead
+count & 5990 & 6416\tabularnewline
+Mean of Age & 49.9 & 49.73\tabularnewline
+BMI & 28.549 & 29.379\tabularnewline
+TC & &\tabularnewline
+Statin use (ratio) & 0.198 & 0.181\tabularnewline
+\bottomrule
+\end{longtable}
+
+base\_box\_plot
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/exploratory}
+{\centering \includegraphics[width=1\linewidth]{/home/mabdulsa/BMI/images/base_box_plot}
+
+}
+
+\caption{Illustration of data distribution using a box plot. The plot compares cholesterol drug users vs non-cholesterol drug users}\label{fig:box}
+\end{figure}
+
+Figure \ref{fig:box} shows the association between age and BMI with respect to cholesterol drug is inconsistent.
+At the early age, the correlation is positive while at the middle age the correlation is almost flat, and at the old age the correlation is negative.
+Moreover, at low age cholesterol medications are described only for a population with high BMI, but at a higher age, the difference in term of the BMI for a population that takes cholesterol medication and without cholesterol medication decreases until it diminishes as in the white population.
+The heterogeneity can also be seen in gender ?, for the Hispanic female population, the cholesterol medication is taken by the population with lower BMI if compared to the population that does not take cholesterol medication.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/exploratory}
+
+}
+
+\caption{A better figure caption}\label{fig:data}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/exploratory2}
 
@@
 
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
+So,
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/quant90}
+
+}
+
+\caption{A 90th quantile of BMI ploted with repect to age. The population grouped with repect gender and fasting blood glucose level: prediabetes nad diabetes}\label{fig:unnamed-chunk-2}
+\end{figure}
+
+\section{Results}
+
+The resulting estimate of effects on conditional mean of BMI level may not reflect the size and nature of these effects on lower or upper quantile.
+For example, in Figure \ref{fig:resu1}, the conditional mean effect of gender on BMI level is about -1, that is on average male's BMI is less than a female's BMI by one unit.
+However, the disparity of the gender effects on lower tails is much larger which is about 1, but the disparity is lower for the upper tail of the distribution somewhat around -3 unit.
+
+From the OLS it is obvious cholesterol drug users have on average higher BMI levels if compared to non-cholesterol drug users which are around 1.75.
+The disparity in BMI level for cholesterol drug users vs non-cholesterol drug users is almost the same for different Quantiles.
+cholesterol drug use seems to be associated with rather large effects on BMI levels somewhat around 1.5 to 1.7.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{/home/mabdulsa/BMI/images/newfig}
+
+}
+
+\caption{Quantile regression of BMI ploted f for fifferent marginal effects. The predictors modeled using quadratic terms }\label{fig:resu1}
+\end{figure}
+
+So,
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{/home/mabdulsa/BMI/images/newfig11}
+
+}
+
+\caption{Quantile regression of BMI ploted f for fifferent marginal effects. The predictors modeled using splines }\label{fig:resu12}
+\end{figure}
+
+Age effect modeled as a quadratic factor.
+The age effect is concave in general, see Figure \ref{fig:resu3}.
+At the lower quantile, BMI increases from age 20 to around age 50, and it starts to decrease after that.
+In the 55th quantile, the concavity is stronger at age 50 if compared to the left or right tail.
+The quadratic effect of age is reflected in the hyperbolic shape.
+However, the age effect modeled as b spline behaves in a different way.
+Age effect on BMI increases from age 20 to around age 36 and then start to decrease up to around age 63 then move up again and then decreases up to age 80, see Fig.\ref{fig:resu33}.
+The BMI trend in this modeling is close to the trend shown in (Chen 2005) by using a complicated polynomial and log transformation for the response.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/p_age_effect}
+
+}
+
+\caption{Illustration of the quadratic age effect on BMI leveles for four different quantiles of the conditional BMI distribution.  The }\label{fig:resu3}
+\end{figure}
+
+Using splines
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/s_age_effect}
+
+}
+
+\caption{Age effect modeled using bsplines }\label{fig:resu33}
+\end{figure}
+
+Marginal quadratic cholesterol effect
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/p_TC_effect}
+
+}
+
+\caption{Illustration of the quadratic cholestrol effect on BMI leveles for four different quantiles of the conditional BMI distribution.  The }\label{fig:resu4}
+\end{figure}
+
+Splines modeling
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/s_TC_effect}
+
+}
+
+\caption{ Illustration of marginal cholestrol effect modeled as B splines.  The }\label{fig:resu330}
+\end{figure}
+
+The quadratic effect of total cholesterol on the conditional distribution of BMI is convex.
+At the lower tail, the correlation is positive that is as cholesterol increases the BMI increases.
+decreasing glucose level by somewhat around 1.4 up to around 180 Cholesterol level.
+However, at higher quantile the association become negative that is as cholesterol level increases the BMI decreases, see Figure \ref{fig:resu4}.
+The relation between total cholesterol and fasting glucose has been studied in (Tsaousis 2014),(Chang et al.
+2011).
+They found that there is a positive correlation between the two groups on average.
+
+On the other hand, when we use splines to modeled the total cholesterol, there is a huge difference in the shape of the association expect at the higher quantile there is some similarity.
+At the lower quantile, there is negative correlation between total cholesterol and BMI for total cholesterol in the range less than 160, then the correlation becomes positive for total cholesterol in the range of (170, 250).
+at the 55th quantile, the correlation is positive for low cholesterol level and then becomes almost flat for the rest cholesterol values.
+At a higher qunatile, the correlation becomes negative at cholesterol level in the range (160,300), see Figure \ref{resu330}.
+
+\section{Conclusion}
+
+Multivariate quantile regression is used to study the effects of different risk factors on the BMI levels.
+Cholesterol drug effects on BMI is negligible at low quantile but at higher quantile cholesterol medication effects on BMI is larger.
+This study showed that the association between BMI and total cholesterol is varying with repect to different quantile.
+
+tota people who have TC levels around 190 mg/dL have the lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile, the optimal cholesterol level is around 200 mg/dL.
+Moreover,
+
+It is recommended to investigate why the effect estimates are varying across different BMI quantiles.
+
+\newpage
+\section{References}
 
 \hypertarget{refs}{}
-\hypertarget{ref-NHANES}{}
-Disease Control, Centers for, and Prevention (CDC). 2018. ``National
-Health and Nutrition Examination Survey Data (Nhanes.''
+\leavevmode\hypertarget{ref-anderson1991}{}%
+Anderson, Keaven M, Patricia M Odell, Peter WF Wilson, and William B Kannel. 1991. ``Cardiovascular Disease Risk Profiles.'' \emph{American Heart Journal} 121 (1): 293--98.
 
-\hypertarget{ref-katbody}{}
-Katzmarzyk, Peter T, Bruce A Reeder, Susan Elliott, Michel R Joffres,
-Punam Pahwa, Kim D Raine, Susan A Kirkland, and Gilles Paradis. 2012.
-``Body Mass Index and Risk of Cardiovascular Disease, Cancer and
-All-Cause Mortality.'' \emph{Canadian Journal of Public Health} 103 (2).
-Springer: 147--51.
+\leavevmode\hypertarget{ref-balkau2004prediction}{}%
+Balkau, Beverley, Gang Hu, Qing Qiao, Jaakko Tuomilehto, Knut Borch-Johnsen, K Pyorala, DECODE Study Group, European Diabetes Epidemiology Group, and others.
+2004.
+``Prediction of the Risk of Cardiovascular Mortality Using a Score That Includes Glucose as a Risk Factor.
+The Decode Study.'' \emph{Diabetologia} 47 (12): 2118.
 
-\hypertarget{ref-van2012estimating}{}
-Van de Kassteele, Jan, RT Hoogenveen, PM Engelfriet, PHM Van Baal, and
-HC Boshuizen. 2012. ``Estimating Net Transition Probabilities from
-Cross-Sectional Data with Application to Risk Factors in Chronic Disease
-Modeling.'' \emph{Statistics in Medicine} 31 (6). Wiley Online Library:
-533--43.
+\leavevmode\hypertarget{ref-bann2020}{}%
+Bann, David, Emla Fitzsimons, and William Johnson.
+2020.
+``Determinants of the Population Health Distribution: An Illustration Examining Body Mass Index.'' \emph{International Journal of Epidemiology} 49 (3): 731--37.
+
+\leavevmode\hypertarget{ref-bruce2020}{}%
+Bruce, Peter, Andrew Bruce, and Peter Gedeck. 2020. \emph{Practical Statistics for Data Scientists: 50+ Essential Concepts Using R and Python}. O'Reilly Media.
+
+\leavevmode\hypertarget{ref-cade2003}{}%
+Cade, Brian S, and Barry R Noon. 2003. ``A Gentle Introduction to Quantile Regression for Ecologists.'' \emph{Frontiers in Ecology and the Environment} 1 (8): 412--20.
+
+\leavevmode\hypertarget{ref-castro2016}{}%
+Castro, M Regina, Gyorgy Simon, Stephen S Cha, Barbara P Yawn, L Joseph Melton, and Pedro J Caraballo.
+2016.
+``Statin Use, Diabetes Incidence and Overall Mortality in Normoglycemic and Impaired Fasting Glucose Patients.'' \emph{Journal of General Internal Medicine} 31 (5): 502--8.
+
+\leavevmode\hypertarget{ref-chang2011}{}%
+Chang, Jin-Biou, Nain-Feng Chu, Jhu-Ting Syu, An-Tsz Hsieh, and Yi-Ren Hung.
+2011.
+``Advanced Glycation End Products (Ages) in Relation to Atherosclerotic Lipid Profiles in Middle-Aged and Elderly Diabetic Patients.'' \emph{Lipids in Health and Disease} 10 (1): 228.
+
+\leavevmode\hypertarget{ref-chen2005}{}%
+Chen, Colin. 2005. ``Growth Charts of Body Mass Index (Bmi) with Quantile Regression.'' \emph{AMCS} 5: 114--20.
+
+\leavevmode\hypertarget{ref-NHANES}{}%
+Disease Control, Centers for, and Prevention (CDC). 2018. ``National Health and Nutrition Examination Survey Data (Nhanes.''
+
+\leavevmode\hypertarget{ref-ferrieres2018}{}%
+Ferrières, Jean, Dominik Lautsch, Anselm K Gitt, Gaetano De Ferrari, Hermann Toplak, Moses Elisaf, Heinz Drexel, et al.
+2018.
+``Body Mass Index Impacts the Choice of Lipid-Lowering Treatment with No Correlation to Blood Cholesterol--Findings from 52 916 Patients in the Dyslipidemia International Study (Dysis).'' \emph{Diabetes, Obesity and Metabolism} 20 (11): 2670--4.
+
+\leavevmode\hypertarget{ref-flegal1999}{}%
+Flegal, Katherine M. 1999. ``The Obesity Epidemic in Children and Adults: Current Evidence and Research Issues.'' \emph{Medicine and Science in Sports and Exercise} 31 (11 Suppl): S509--14.
+
+\leavevmode\hypertarget{ref-hay2017gbd}{}%
+Hay, Simon I, Sudha P Jayaraman, Alejandra G Contreras Manzano, Anoushka Millear, Laura Kemmer, Brent Bell, Juan Jesus Carrero, et al.
+2017.
+``GBD 2015 Risk Factors Collaborators.
+Global, Regional, and National Comparative Risk Assessment of 79 Behavioural, Environmental and Occupational, and Metabolic Risks or Clusters of Risks, 1990-2015: A Systematic Analysis for the Global Burden of Disease Study 2015 (Vol 388, Pg 1659, 2016).'' \emph{Lancet} 389 (10064): E1--E1.
+
+\leavevmode\hypertarget{ref-katbody}{}%
+Katzmarzyk, Peter T, Bruce A Reeder, Susan Elliott, Michel R Joffres, Punam Pahwa, Kim D Raine, Susan A Kirkland, and Gilles Paradis.
+2012.
+``Body Mass Index and Risk of Cardiovascular Disease, Cancer and All-Cause Mortality.'' \emph{Canadian Journal of Public Health} 103 (2): 147--51.
+
+\leavevmode\hypertarget{ref-koenker2005}{}%
+Koenker, Roger. 2005. ``Quantile Regression, Volume 38 of.'' \emph{Econometric Society Monographs}.
+
+\leavevmode\hypertarget{ref-mozaffarian2015executive}{}%
+Mozaffarian, Dariush, Emelia J Benjamin, Alan S Go, Donna K Arnett, Michael J Blaha, Mary Cushman, Sarah De Ferranti, et al.
+2015.
+``Executive Summary: Heart Disease and Stroke Statistics---2015 Update: A Report from the American Heart Association.'' \emph{Circulation} 131 (4): 434--41.
+
+\leavevmode\hypertarget{ref-pandya2015}{}%
+Pandya, Ankur, Stephen Sy, Sylvia Cho, Milton C Weinstein, and Thomas A Gaziano.
+2015.
+``Cost-Effectiveness of 10-Year Risk Thresholds for Initiation of Statin Therapy for Primary Prevention of Cardiovascular Disease.'' \emph{Jama} 314 (2): 142--50.
+
+\leavevmode\hypertarget{ref-ridker2012}{}%
+Ridker, Paul M, Aruna Pradhan, Jean G MacFadyen, Peter Libby, and Robert J Glynn.
+2012.
+``Cardiovascular Benefits and Diabetes Risks of Statin Therapy in Primary Prevention: An Analysis from the Jupiter Trial.'' \emph{The Lancet} 380 (9841): 565--71.
+
+\leavevmode\hypertarget{ref-sugiyama2014}{}%
+Sugiyama, Takehiro, Yusuke Tsugawa, Chi-Hong Tseng, Yasuki Kobayashi, and Martin F Shapiro.
+2014.
+``Different Time Trends of Caloric and Fat Intake Between Statin Users and Nonusers Among Us Adults: Gluttony in the Time of Statins?'' \emph{JAMA Internal Medicine} 174 (7): 1038--45.
+
+\leavevmode\hypertarget{ref-tsaousis2014}{}%
+Tsaousis, Konstantinos T.
+2014.
+``Blood Glucose and Cholesterol Concentrations in a Mediterranean Rural Population of Andros Island, Greece.'' \emph{International Journal of Preventive Medicine} 5 (11): 1464.
+
+\leavevmode\hypertarget{ref-van2012estimating}{}%
+Van de Kassteele, Jan, RT Hoogenveen, PM Engelfriet, PHM Van Baal, and HC Boshuizen.
+2012.
+``Estimating Net Transition Probabilities from Cross-Sectional Data with Application to Risk Factors in Chronic Disease Modeling.'' \emph{Statistics in Medicine} 31 (6): 533--43.
+
+\leavevmode\hypertarget{ref-yusuf2016}{}%
+Yusuf, Salim, Jackie Bosch, Gilles Dagenais, Jun Zhu, Denis Xavier, Lisheng Liu, Prem Pais, et al.
+2016.
+``Cholesterol Lowering in Intermediate-Risk Persons Without Cardiovascular Disease.'' \emph{New England Journal of Medicine} 374 (21): 2021--31.
+
+\leavevmode\hypertarget{ref-yusuf2004effect}{}%
+Yusuf, Salim, Steven Hawken, Stephanie Ôunpuu, Tony Dans, Alvaro Avezum, Fernando Lanas, Matthew McQueen, et al.
+2004.
+``Effect of Potentially Modifiable Risk Factors Associated with Myocardial Infarction in 52 Countries (the Interheart Study): Case-Control Study.'' \emph{The Lancet} 364 (9438): 937--52.
 

### 2021-04-23 manuscript/manuscript2.Rmd
update

@@
 The spline is a process of constructing a set of piece-wise continuous
-polynomials that are smoothly connected at a set of points in the range of the predictor variable.
+<!-- polynomials that are smoothly connected at a set of points in the range of the predictor variable.
 The connection points are called knots i.e.
 splines are used to smoothly interpolate between certain points.
-Let $a,b$ ,and $c$ are the endpoints of the $x$-axis intervals.
-A smooth cubic spline function is defined by the following equation.
+Let $a,b$ ,and $c$ are the endpoints of the $x-$axis intervals.
+A transformation for some or all of predictors is needed to capture the nonlinearity in the model.
+The family of transformation of the predictors that can be fit together to built the model's shape is known as a basis function.
+the basis functions are $b_1(x),b_2(x), \cdots,\b_k(x),$ and the estimation of $y_i$ is computed as follows: -->
+
+<!-- \begin{equation} -->
+<!-- y_i=\beta_0+\beta_1 b_1(x_i)+\beta_2 b_2(x_i)+\cdots+ \beta_k b_k(x_i) -->
+<!-- \end{equation} -->
+<!-- This concept of a family of transformations that can fit together to capture general shapes is called a basis function.
+In this case, our objects are functions: $ b_1 (X ), b_2 (X ),\cdots , b_K (X ).$ In a more general way to represent a value of $y=f(X)$ using a peacewise cubic polybomials with a singl knote $c.$  -->
+
 \begin{equation}
-f(X)=X\beta=\beta_{0}+\beta_{1}X+\beta_2X^2+\beta_{3}X^{3}+\beta_{4}(X-a)_{+}^3+\beta_{5}(X-b)_{+}^3+\beta_6(X-c)_{+}^3,
-\end{equation}
-
-where $$(u)_{+}=  
+y_{i}=  
  \left\{
 \begin{array}{ll}
-u  & \mbox{if } u > 0 \\
-0 & \mbox{if } u \leq 0
+ \beta_{01}+\beta_{11}x_i+\beta_{21}x_i^2+ \beta_{31}x_i^3+	\epsilon_i & \mbox{if } x_i< c \\
+ \beta_{02}+\beta_{12}x_i+\beta_{22}x_i^2+ \beta_{23}x_i^3+	\epsilon_i& \mbox{if } x_i \geq c
 \end{array}
-\right. $$
+\right.
+\end{equation}
+Imposing a continuty condition  and first, and second derivative at $c$ are equal in the two sides, we get a cubic splines. 
+<!-- \begin{equation} -->
+<!-- f(X)=X\beta=\beta_{0}+\beta_{1}X+\beta_2X^2+\beta_{3}X^{3}+\beta_{4}(X-a)_{+}^3+\beta_{5}(X-b)_{+}^3+\beta_6(X-c)_{+}^3, -->
+<!-- \end{equation} -->
+
+<!-- where $$(u)_{+}=   -->
+<!--  \left\{ -->
+<!-- \begin{array}{ll} -->
+<!-- u  & \mbox{if } u > 0 \\ -->
+<!-- 0 & \mbox{if } u \leq 0 -->
+<!-- \end{array} -->
+<!-- \right. $$ -->
 
@@
 The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.
+The following formulas represents the different model that presented in the result.
+
+ \begin{equation}
+ \hat{BMI}= bs(Age, df = 5) + Race + Gender + Cholesterol Drug Use
+ \end{equation}
+
+ \begin{equation}
+ \hat{BMI}= bs(Total chol, df=5)+ Race + Gender + Cholesterol Drug Use
+ \end{equation}
+
+ \begin{equation}
+ \hat{BMI}= Age+Age^2+ Race + Gender + Cholesterol Drug Use 
+ \end{equation}
+
+ \begin{equation}
+ \hat{BMI}= Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use
+ \end{equation}
 
@@
 ```{r resu3, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic age effect on BMI leveles for four different quantiles of the conditional BMI distribution.
-The ", echo = FALSE}
+", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 # Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "Age_splin.png")))
-knitr::include_graphics(here::here("images", "Age_splint.png"))
+if (!file.exists(here::here("images", "Age_splin.png"))) {}
+knitr::include_graphics(here::here("images", "Age_splin.png"))
 ```

### 2021-04-23 manuscript/manuscript2.tex
update

--- 2021-04-23 manuscript/manuscript.tex
@@
 It is been found that statin intensity increases with the high level of BMI(\(\rho=0.13\)).
-\begin{equation}
-y_{i}=  
- \left\{
-\begin{array}{ll}
- \beta_{01}+\beta_{11}x_i+\beta_{21}x_i^2+ \beta_{31}x_i^3+\eps_i & \mbox{if } x_i< c \\
- \beta_{02} & \mbox{if } x_i \geq c
-\end{array}
-\right.
-\end{equation}
+
 Taking cholesterol drug medication associates with a high risk of elevating BMI level.
@@
 
-Least square method expresses conditional mean of y given x as \(\mu(x)=x^T\beta\) and it solves \[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.\] Quantile regression expresses conditional quantile function \(Q_y(\tau|x)=x^T \beta ({\tau)}\) and solve \[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.\]This minimization problem can be reformulated to a linear programming problem \[ \underset{\beta\in \mathcal{R}^p}{\text{min}} \]
+Least square method expresses conditional mean of y given x as \(\mu(x)=x^T\beta\) and it solves \[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.\] Quantile regression expresses conditional quantile function \(Q_y(\tau|x)=x^T \beta ({\tau)}\) and solve \[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.\]This minimization problem can be reformulated to a linear programming problem
 
@@
 The spline is a process of constructing a set of piece-wise continuous
-polynomials that are smoothly connected at a set of points in the range of the predictor variable.
-The connection points are called knots i.e.~splines are used to smoothly interpolate between certain points.
-Let \(a,b\) ,and \(c\) are the endpoints of the \(x\)-axis intervals.
-A smooth cubic spline function is defined by the following equation.
+
 \begin{equation}
-f(X)=X\beta=\beta_{0}+\beta_{1}X+\beta_2X^2+\beta_{3}X^{3}+\beta_{4}(X-a)_{+}^3+\beta_{5}(X-b)_{+}^3+\beta_6(X-c)_{+}^3,
-\end{equation}
-
-where \[(u)_{+}=  
+y_{i}=  
  \left\{
 \begin{array}{ll}
-u  & \mbox{if } u > 0 \\
-0 & \mbox{if } u \leq 0
+ \beta_{01}+\beta_{11}x_i+\beta_{21}x_i^2+ \beta_{31}x_i^3+ \epsilon_i & \mbox{if } x_i< c \\
+ \beta_{02}+\beta_{12}x_i+\beta_{22}x_i^2+ \beta_{23}x_i^3+ \epsilon_i& \mbox{if } x_i \geq c
 \end{array}
-\right. \]
+\right.
+\end{equation}
+Imposing a continuty condition and first, and second derivative at \(c\) are equal in the two sides, we get a cubic splines.
 
@@
 The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.
+The following formulas represents the different model that presented in the result.
+
+\begin{equation}
+ \hat{BMI}= bs(Age, df = 5) + Race + Gender + Cholesterol Drug Use
+ \end{equation}
+
+\begin{equation}
+ \hat{BMI}= bs(Total chol, df=5)+ Race + Gender + Cholesterol Drug Use
+ \end{equation}
+
+\begin{equation}
+ \hat{BMI}= Age+Age^2+ Race + Gender + Cholesterol Drug Use 
+ \end{equation}
+
+\begin{equation}
+ \hat{BMI}= Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use
+ \end{equation}
 
@@
 
-base\_box\_plot
-
 \begin{figure}
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/exploratory2}
-
-}
-
-\caption{A better figure caption}\label{fig:unnamed-chunk-1}
-\end{figure}
-
-So,
-
-\begin{figure}
-
 {\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/quant90}
@@
 
-\caption{A 90th quantile of BMI ploted with repect to age. The population grouped with repect gender and fasting blood glucose level: prediabetes nad diabetes}\label{fig:unnamed-chunk-2}
+\caption{A 90th quantile of BMI ploted with repect to age. The population grouped with repect gender and fasting blood glucose level: prediabetes nad diabetes}\label{fig:unnamed-chunk-1}
 \end{figure}
@@
 
-So,
-
 \begin{figure}
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/p_age_effect}
+{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/Age_poly}
 
@@
 
-\caption{Illustration of the quadratic age effect on BMI leveles for four different quantiles of the conditional BMI distribution.  The }\label{fig:resu3}
+\caption{Illustration of the quadratic age effect on BMI leveles for four different quantiles of the conditional BMI distribution. }\label{fig:resu3}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/s_age_effect}
+{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/Age_splin}
 
@@
 
-Marginal quadratic cholesterol effect
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/Total_chol_poly}
+
+}
+
+\caption{Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled as  quadratic .}\label{fig:resu4}
+\end{figure}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/p_TC_effect}
+{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/TC_splin}
 
@@
 
-\caption{Illustration of the quadratic cholestrol effect on BMI leveles for four different quantiles of the conditional BMI distribution.  The }\label{fig:resu4}
-\end{figure}
-
-Splines modeling
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/s_TC_effect}
-
-}
-
-\caption{ Illustration of marginal cholestrol effect modeled as B splines.  The }\label{fig:resu330}
+\caption{ Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled  as B splines. }\label{fig:resu330}
 \end{figure}
@@
 
-tota people who have TC levels around 190 mg/dL have the lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile, the optimal cholesterol level is around 200 mg/dL.
+total people who have TC levels around 190 mg/dL have the lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile, the optimal cholesterol level is around 200 mg/dL.
 Moreover,

### 2021-04-23 ci_splin.R

@@ -29,7 +29,7 @@ dat$Age=as.numeric(dat$Age)
 
 
 fit_rq=function(dat,index,tau){
-    if (index==1) {formula=BMI ~ bs(Age, df = 3) + Race + Gender + Cholesterol_Drug_Use}
+    if (index==1) {formula=BMI ~ bs(Age, df = 5) + Race + Gender + Cholesterol_Drug_Use}
     else if(index ==2) {formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use}
     else if (index==3) {formula=BMI ~ Age+Age^2+ Race + Gender + Cholesterol_Drug_Use}
     else{formula=BMI ~ Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use}

### 2021-05-01 manuscript/manuscript.Rmd
update

@@
 header-includes:
-    - \usepackage{setspace}\doublespacing 
+    - \usepackage{setspace}
     - \usepackage{float}
@@
 ---
-<!-- \setstretch{4} -->
+\setstretch{4}
 \section{introduction}

### 2021-05-01 manuscript/manuscript2.Rmd
update

@@
 
-```{r resu1, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted f for fifferent marginal effects. The predictors modeled using quadratic terms ", echo = FALSE}
+```{r resu1, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted  for different marginal effects. The predictors modeled using quadratic terms ", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 
-```{r resu12, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted f for fifferent marginal effects. The predictors modeled using splines ", echo = FALSE}
+```{r resu12, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted  for different marginal effects. The predictors modeled using splines ", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 
+```{r resu1000, out.width = "100%", fig.align = "center", fig.cap = " Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled  as B splines. ", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "comp_age")))  
+knitr::include_graphics(here::here("images", "comp_age.png"))
+```
+
+```{r resu1010, out.width = "100%", fig.align = "center", fig.cap = " ", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "comp_tc")))  
+knitr::include_graphics(here::here("images", "comp_tc.png"))
+```
+
 The quadratic effect of total cholesterol on the conditional distribution of BMI is convex.

### 2021-05-01 ci_splin.R

@@ -36,6 +36,7 @@ fit_rq=function(dat,index,tau){
     message("model.matrix")
     X <- model.matrix(formula,data=dat)
     qr_fit_dat <- rq( BMI ~ X - 1, data=dat, tau = tau)
+    #qr_fit_dat <- rq( formula, data=dat, tau = tau)
     return(qr_fit_dat)
 }
 
@@ -312,3 +313,12 @@ dev.off()
 # grid.arrange(fig[1],fig[2],fig[3],fig[4],fig[5], ncol=3, nrow = 2)
 # dev.off()
 # 
+
+
+################
+#ggeffect plot
+
+ggpredict(fit,"Age [all]")
+df=ggpredict(fit,"Age [all]")
+ggplot(df,aes(x,predicted))+geom_line()+geom_ribbon(aes(ymin=conf.low,ymax=conf.high),alpha=0.1)
+

### 2021-05-01 ci_splin_marg_effect.R

@@ -1,0 +1,142 @@
+
+#Marginal effect on BMI with splines
+#Plot for the confidence interval of BMI regressed on splines of Age, 
+#race, gender,and cholesterol medications use.
+
+
+library(quantreg)
+library(splines)
+library(tidyverse)
+library(ggeffects)
+library(gridExtra)
+
+
+
+
+dat=readRDS(file = "bmi.data.rds")
+#dat=dat[dat$BMI<28,]
+dat=filter(dat,Cholesterol_Drug_Use!='9')
+#levels(dat$Cholesterol_Drug_Use) <- c('1','2')
+dat$Cholesterol_Drug_Use <- factor(dat$Cholesterol_Drug_Use)
+dat$Age=as.numeric(dat$Age)
+
+#formula 1
+#formula=BMI ~ bs(Age, df = 5) + Race + Gender + Cholesterol_Drug_Use+Total_chol
+#formula 2
+#formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use
+# formula 3 
+#formula=BMI ~ Age+Age^2+Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use
+
+
+fit_rq=function(dat,index,tau){
+    if (index==1) {formula=BMI ~ bs(Age, df = 5) + Race + Gender + Cholesterol_Drug_Use}
+    else if(index ==2) {formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use}
+    else if (index==3) {formula=BMI ~ Age+Age^2+ Race + Gender + Cholesterol_Drug_Use}
+    else{formula=BMI ~ Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use}
+    message("model.matrix")
+    X <- model.matrix(formula,data=dat)
+    # qr_fit_dat <- rq( BMI ~ X - 1, data=dat, tau = tau)
+    qr_fit_dat <- rq( formula, data=dat, tau = tau)
+    return(qr_fit_dat)
+}
+
+#index= 1 bsplines age and total cholesterol, Index=2 bspline total choles, 
+#and index=3 polynomial age and total choles.
+fit=fit_rq(dat,index=1,tau=0.9)
+
+
+#ggeffect plot
+
+ggpredict(fit,"Age [all]")
[…]

### 2021-05-10 manuscript/manuscript2.Rmd
Update

--- 2021-04-23 manuscript/manuscript2.Rmd
@@
 In 2011, annual costs for CVD and stroke were $\$320.1$ billion, which is more than cancer cost.
-This cost includes \$195.6  billion in direct costs (healthcare costs), and the cost of future productivity loss is  \$124.5 [@mozaffarian2015executive].
+This cost includes \$195.6  billion in direct costs (health-care costs), and the cost of future productivity loss is  \$124.5 [@mozaffarian2015executive].
 Important factors associated with CVD are high body mass index (BMI) and abnormal lipid ratio  [@yusuf2004effect], [@anderson1991].
@@
 \end{equation}
-Imposing a continuty condition  and first, and second derivative at $c$ are equal in the two sides, we get a cubic splines. 
+Imposing a continuity condition  and first, and second derivative at $c$ are equal in the two sides, we get a cubic splines. 
 <!-- \begin{equation} -->
@@
  \begin{equation}
- \hat{BMI}= Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use
+ \hat{BMI}= Total chol+ Total chol^2+ Race + Gender + Cholesterol Drug_Use
  \end{equation}
@@
 \subsection{Data}
- The data used in this study is National Health and Nutrition Examination Survey data (NHANES)[@NHANES].
+ The data used in this study is the National Health and Nutrition Examination Survey data (NHANES)[@NHANES].
 The survey examines a nationally representative sample of the U.S.
@@
 
+```{r resu1000, out.width = "100%", fig.align = "center", fig.cap = "  An illustration of  marginal effects of age on different BMI quantiles.
+The predictors modeled using quadratic terms and splines.", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "comp_age_mixed")))  
+knitr::include_graphics(here::here("images", "comp_age_mixed.png"))
+```
+
+```{r resu1010, out.width = "100%", fig.align = "center", fig.cap = " An illustration of  marginal effects of total cholesterol  on different BMI quantiles.
+The predictors modeled using quadratic terms and splines.", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "comp_tot_mixed")))  
+knitr::include_graphics(here::here("images", "comp_tot_mixed.png"))
+```
+
 The quadratic effect of total cholesterol on the conditional distribution of BMI is convex.
@@
 at the 55th quantile, the correlation is positive for low cholesterol level and then becomes almost flat for the rest cholesterol values.
-At a higher qunatile, the correlation becomes negative at cholesterol level in the range (160,300), see Figure \@ref(resu330).
+At a higher quntile, the correlation becomes negative at cholesterol level in the range (160,300), see Figure \@ref(resu330).
 
@@
 Cholesterol drug effects on BMI is negligible at low quantile but at higher quantile cholesterol medication  effects on BMI is larger.
-This study showed that the association between BMI and total cholesterol is varying with repect to different quantile.
+This study showed that the association between BMI and total cholesterol is varying with respect to different quantile.
 

### 2021-05-10 manuscript/manuscript2.tex
Update

@@
 \author{}
-\date{\vspace{-2.5em}April 22, 2021}
+\date{\vspace{-2.5em}May 10, 2021}
 
@@
 In 2011, annual costs for CVD and stroke were \(\$320.1\) billion, which is more than cancer cost.
-This cost includes \$195.6 billion in direct costs (healthcare costs), and the cost of future productivity loss is \$124.5 (Mozaffarian et al.
+This cost includes \$195.6 billion in direct costs (health-care costs), and the cost of future productivity loss is \$124.5 (Mozaffarian et al.
 2015).
@@
 \end{equation}
-Imposing a continuty condition and first, and second derivative at \(c\) are equal in the two sides, we get a cubic splines.
+Imposing a continuity condition and first, and second derivative at \(c\) are equal in the two sides, we get a cubic splines.
 
@@
 \begin{equation}
- \hat{BMI}= Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use
+ \hat{BMI}= Total chol+ Total chol^2+ Race + Gender + Cholesterol Drug_Use
  \end{equation}
@@
 
-The data used in this study is National Health and Nutrition Examination Survey data (NHANES)(Disease Control and (CDC) 2018).
+The data used in this study is the National Health and Nutrition Examination Survey data (NHANES)(Disease Control and (CDC) 2018).
 The survey examines a nationally representative sample of the U.S.
@@
 
-\caption{Quantile regression of BMI ploted f for fifferent marginal effects. The predictors modeled using quadratic terms }\label{fig:resu1}
+\caption{Quantile regression of BMI ploted  for different marginal effects. The predictors modeled using quadratic terms }\label{fig:resu1}
 \end{figure}
@@
 
-\caption{Quantile regression of BMI ploted f for fifferent marginal effects. The predictors modeled using splines }\label{fig:resu12}
+\caption{Quantile regression of BMI ploted  for different marginal effects. The predictors modeled using splines }\label{fig:resu12}
 \end{figure}
@@
 
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{/home/mabdulsa/BMI/images/comp_age_mixed}
+
+}
+
+\caption{  An illustration of  marginal effects of age on different BMI quantiles. The predictors modeled using quadratic terms and splines.}\label{fig:resu1000}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{/home/mabdulsa/BMI/images/comp_tot_mixed}
+
+}
+
+\caption{ An illustration of  marginal effects of total cholesterol  on different BMI quantiles. The predictors modeled using quadratic terms and splines.}\label{fig:resu1010}
+\end{figure}
+
 The quadratic effect of total cholesterol on the conditional distribution of BMI is convex.
@@
 at the 55th quantile, the correlation is positive for low cholesterol level and then becomes almost flat for the rest cholesterol values.
-At a higher qunatile, the correlation becomes negative at cholesterol level in the range (160,300), see Figure \ref{resu330}.
+At a higher quntile, the correlation becomes negative at cholesterol level in the range (160,300), see Figure \ref{resu330}.
 
@@
 Cholesterol drug effects on BMI is negligible at low quantile but at higher quantile cholesterol medication effects on BMI is larger.
-This study showed that the association between BMI and total cholesterol is varying with repect to different quantile.
+This study showed that the association between BMI and total cholesterol is varying with respect to different quantile.
 

### 2021-05-10 ci_splin.R

@@ -29,7 +29,7 @@ dat$Age=as.numeric(dat$Age)
 
 
 fit_rq=function(dat,index,tau){
-    if (index==1) {formula=BMI ~ bs(Age, df = 5) + Race + Gender + Cholesterol_Drug_Use}
+    if (index==1) {formula=BMI ~ bs(Age, df = 3) + Race + Gender + Cholesterol_Drug_Use}
     else if(index ==2) {formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use}
     else if (index==3) {formula=BMI ~ Age+Age^2+ Race + Gender + Cholesterol_Drug_Use}
     else{formula=BMI ~ Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use}

### 2021-05-10 ci_splin_marg_effect.R

@@ -83,22 +83,15 @@ ggplot(df,aes(x,predicted))+
 
 
 #####
-png(file = here::here("images", "comp_tc.png"),
-    res = 400, height = 9, width = 16, units = "in")
 
-blab <- c("Intercept","Male ","RaceMexican", "RaceOther", "RaceOther_Hispanic ", "White ", " Cholesterol_Drug_Use","Age","Age^2","Total cholesterol","Total cholestrol^2")
-
-par(mfrow=c(2,2))
-#Comparison plot
-taus=c(0.2,0.5,0.75,0.90)
-for(i in 1:4) {
-fit=fit_rq(dat,index=1,tau=taus[i])
+ 
+fit=fit_rq(dat,index=1,tau=0.9)
 fit1=ggpredict(fit,"Age [all]") 
-fit=fit_rq(dat,index=2,tau=taus[i])
+fit=fit_rq(dat,index=2,tau=0.9)
 fit2=ggpredict(fit,"Total_chol [all]")
-fit=fit_rq(dat,index=3,tau=taus[i])
+fit=fit_rq(dat,index=3,tau=0.9)
 fit3=ggpredict(fit,"Age")
-fit=fit_rq(dat,index=4,tau=taus[i])
+fit=fit_rq(dat,index=4,tau=0.9)
 fit4=ggpredict(fit,"Total_chol")
 
 dat1 <- rbind(
@@ -108,35 +101,237 @@ dat1 <- rbind(
         mutate(model = "Quadratic"))
 
 
-  ggplot(dat1, aes(x = x, y = predicted, group = model, color = model, fill = model)) +
+ tot1= ggplot(dat1, aes(x = x, y = predicted, group = model, color = model, fill = model)) +
     geom_line() +
     geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
     xlab("Age")+
     ylab("BMI")
-
-  #print(tot1) 
- 
+ png(file = here::here("images", "comp_age.png"),
+     res = 400, height = 9, width = 16, units = "in")
+  print(tot1) 
+ dev.off()
 
 ##############
+#10%
+ 
+ fit=fit_rq(dat,index=1,tau=0.1)
+ fit1=ggpredict(fit,"Age [all]") 
+ fit=fit_rq(dat,index=3,tau=0.1)
+ fit3=ggpredict(fit,"Age")
+ 
+ 
+ dat1 <- rbind(
+   fit1 %>%
[…]

### 2021-06-10 manuscript/manuscript2.Rmd
Update

@@
     - \usepackage{float}
+    - \floatplacement{figure}{H}
 abstract: "My abstract"
@@
 <!-- \setstretch{4} -->
-\section{introduction}
+\section{Introduction}
 
-  High BMI has negative impact on public health.
-Due to high cost of obesity, it is crucial to get better understanding of the underlying risk factor for obesity.
-This can help decision makers to create a new regulation that help to prevent and to stop the dramatic increase in the BMI index.
+  High body mass index (BMI) has a negative impact on public health.
+Due to high cost of obesity, it is crucial to get better understanding of the underlying risk factors for obesity.
+This can help decision makers to create  new recommendations that help to prevent and stop the dramatic increase in BMI.
 
-  Body Mass Index (BMI) plays an important role in predicting heart disease risk[@katbody].
-Approximately, 18 million deaths annually per year are caused by cardiovascular diseases(CVD), and similar to this number of nonfatal cardiovascular events [@hay2017gbd].
-In 2011, annual costs for CVD and stroke were $\$320.1$ billion, which is more than cancer cost.
-This cost includes \$195.6  billion in direct costs (health-care costs), and the cost of future productivity loss is  \$124.5 [@mozaffarian2015executive].
-Important factors associated with CVD are high body mass index (BMI) and abnormal lipid ratio  [@yusuf2004effect], [@anderson1991].
-Lowering low-density lipoprotein (LDL) by using statin or other drugs reduces the risk of cardiovascular diseases even with a population with no CVD  [@yusuf2016].
-Ferrieres et al.
-[@ferrieres2018] studied the effect of BMI on the choice of lipid-lowering treatment.
-It is been found that statin intensity increases with the high level of BMI($\rho=0.13$).
-
-Taking cholesterol drug medication  associates with a high risk of elevating BMI level.
+  BMI plays an important role in predicting heart disease risk[@katbody].
+Approximately 18 million deaths annually per year world wide are caused by cardiovascular diseases(CVD) , and this number is similar to this number of nonfatal cardiovascular events [@hay2017gbd].
+In 2011, annual costs for CVD and stroke were estimated at $\$320.1$ billion, which is more than spending on cancer.
+The total CVD cost includes \$195.6  billion in direct costs (health-care costs) and \$124.5 billion of future productivity loss [@mozaffarian2015executive].
+Important risk factors associated with CVD are high BMI and abnormal lipid ratio  [@yusuf2004effect], [@anderson1991].
+There are some drugs the are used reducce CVD risks by lowering low-density lipoprotein (LDL) like statin.
+Statin use  reduces the risk of cardiovascular diseases, even with a population with no CVD risks  [@yusuf2016].
+On the other hand, statin uses have negative side effects on health conditions, such as elevating glucose levels [@castro2016].
+The effect of BMI on the choice of lipid-lowering treatment has been studied by [@ferrieres2018].
+They found that there is a positive  correlation ($\rho=0.13$) between statin does levels and  BMI levels.
+Additionaly, taking cholesterol drug medication  associates with a high risk of elevating BMI level.
 It is been shown that statin users consume 192 additional calories per day which causes gaining a 6 lb to 11 lb.
@@
 Moreover, consumption of fat in statin users raised by 14.4%[@sugiyama2014].
+This study gives as insight about the association between cholesterol druge uses and condition means.
+An important question to ask is, are there  an associations between cholesterol drug uses and different BMI quantiles?
+This question helps us to understand cholesterol drug uses effect on the  obese, overweight population, so that a decision maker take an optimal action about treatment policy.
 
- Logistic regression helps us to find out the group that has a higher odd of obesity, and ordinary least squares (OLS) regression helps us to study the effects of predictors on the average mean of the response.
-For example, estimating the association of different factors like a lipid-lowering drug with the conditional mean of BMI using OLS or logistic regression model[@ferrieres2018].
-Both of these approaches do not give us insight into the predictor's effects on different quantiles of the responses.
+  Ordinary least squares (OLS) regression helps us to study the effects of predictors on the mean of the response.
+For example, estimating the association of different factors like a lipid-lowering drug with the conditional mean of BMI [@ferrieres2018].
+OLS approaches does not give us insight into the predictor's effects on different quantiles of the responses.
+  Hosever, quantile regression (QR) is used to investigate the heterogeneity in the association of the $\tau$th.
+quantile $0<\tau<1$ of BMI with a set of independent predictors to investigate the effects of a specific predictors on the various quantiles of the BMI.
+Estimation of underweight and overweight regressed on age could be hard because of the trend change and nonlinearity behavior of the BMI with respect to age, as it is shown in [@flegal1999] BMI departs normality because of the skewness on the right and left tails.
+Therefore, QR is an appropriate method used to estimate the differences in the  association of the BMI with predictors.
 
-  Quantile regression is used to investigate the heterogeneity in the association of the $\tau$th quantile of BMI with a set of independent predictors, that is investigate the effects of a specific predictors on the various quantiles of the BMI.
-BMI departs normality because of the skewness on the right and left tails [@flegal1999].
-Estimation of underweight and overweight can be affected by the violation of normality.
-Quantile regression is a crucial tool used to estimate BMI with the dispersion of the association with predictors.
+QR has a wide range of applications.
+For example, it is used to study the association between BMI and the set of predictors; low childhood socioeconomic position, high maternal weight, low childhood general cognition  is stronger in the upper end of BMI quantile in the UK population[@bann2020].
+One cause of this heterogeneity is that risk factors may have stronger effect on patients with worse health, and these effects may diminishes when conditional distribution of the BMI is studied.
+Moreover, another application of using QR is in ecology where different factors interact in a complicated way that produces different variations of one factor for different levels of another variable [@cade2003].
 
-  Quantile regression has many successful applications in ecology where different factors interact in a complicated way that produces different variations of one factor for different levels of another variable [@cade2003].
-The association between BMI and the set of predictors; low childhood socioeconomic position, high maternal weight, low childhood general cognition  is stronger in the upper end of BMI quantile.
-This trend  is found in the UK population[@bann2020].
-One cause of this heterogeneity is that risk factors may have stronger effect on patients with worse health, and these effects may diminishes when conditional mean of the BMI is studied.
-
-  We found that spline regressions produce a different estimate than polynomial regressions.
+ We compare two approaches to study the QR of BMI regressed on age and total cholesterol (TC) levels.
+One approch is called quantile polynomial regression.
+It is defined as a way to model the non-relationship between predictors and distribution of the  response as an $n$th degree polynomial in the predictors.
   Polynomial regression using the quadratic term of predictors forces the response to take convex or concave shape, see Figure 1.12 [@koenker2005].
-This is because the limit of quadratic functions approach $\pm\infty$ as $x\rightarrow\pm\infty.$ However, when we model the predictor as splines the response is not forced to take a specific shape.
-In the latter case, different polynomials are constructed for the different regions in the range of predictors.
+This is because the limit of the response variable $y$, when modeled as a quadratic function of the predictor variable $x$,  approach $\pm\infty$ ( i.e.,as $x \rightarrow\pm\infty,$ $y\rightarrow\pm\infty.$ However, when we model the the reponse variable using a spline basis expansion of the predictor variable the response is not forced to take a specific shape.
+In the latter case, different polynomials are constructed for the different regions in the range of predictors that satisfy continuity and smoothness conditions at the knots.
+  Because of the above issue in the polynomial regression, we found that spline regressions produce a different estimate than polynomial regressions.
 
  \section{Quantile Regression}
-Quantile regression is a tool used to regress the dependent variable with high variance over the independent variables.
-QR is developed to study the relationships between variables that have week or no-relationships between their means.
-One of the advantages of using QR over OLS is QR is robust for outliers.
-
-For a random variable $X$, the cumulative distribution function (CDF) is $$F(X)=P(X\leq x),$$ and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} $$ where $0<\tau<1$.
-Let the loss function is defined by $$\rho_{\tau}(u)= u(\tau-I_{(u<0)})$$ where $I$ is the indicator function  [@koenker2005].
+QR is a tool used to regress the dependent variable with high variance over the independent variables.
+QR is developed to study the relationships between predictors and the response when characteristics other than conditional mean of the response are of interest.
+Also, QR is a valuable tool to study association between predictors and response when we have a week or no-relationships between predictors and the conditional mean of the response.
+Moreover, one of the advantages of using QR over OLS is QR is robust for outliers.
+A brief description of qunatile regression is introduced in the following paragraphs.
+For a continuous random variable $X$, the cumulative distribution function (CDF) is $$F(X)=P(X\leq x),$$ and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\}, $$ where $0<\tau<1$.
+Let the loss function of interest be defined by $$\rho_{\tau}(u)= u(\tau-I_{(u<0)}),$$ where $I$ is the indicator function  [@koenker2005].
 The quantile estimator is the value that minimizes the expected loss function
@@
 =F(\hat{x})-\tau.$$
-Due to the monotonicity of the cumulative distribution function, any solution that satisfies $\{x:F(x)=\tau \}$ is a minimizing for the expected loss function.
+Due to the monotonicity of the cumulative distribution function, any solution that satisfies $\{x:F(x)=\tau \}$ is a minimizer for the expected loss function.
 
-Least square method expresses conditional mean of y given x as $\mu(x)=x^T\beta$ and it solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.$$ Quantile regression expresses conditional quantile function $Q_y(\tau|x)=x^T \beta ({\tau)}$ and solve $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.$$This minimization problem can be reformulated to a linear programming problem
+OLS method expresses the conditional mean of $y$ given $x$ as $\mu(x)=x^T\beta$ and it solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.$$ On the other hand, QR expresses the conditional quantile function $Q_y(\tau|x)=x^T \beta ({\tau)}$ and solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.$$This minimization problem can be reformulated to a linear programming problem and solved using standard statistical software.
 
@@
 
-\subsection{Quantile Regression Technique }
+<!-- \subsection{Quantile Regression Technique } -->
 
-\subsection{splines}
-   A continuous predictor can be modeled as linear, say $X$, or nonlinear term, say $X^2$ depends on the relationship with the response variable.
+\section{Splines Verses Polynomials}
     Most of the relations between the responses and predictors variables are complicated to the point that linear regressions are not suitable to model these relationships[@bruce2020].
@@
 One approach is through including polynomial terms in the regression equation.
-This approach is called Polynomial regression.
+A continuous predictor can be modeled as a linear, say $x$, or nonlinear term, say $x^2$ depending on the relationship with the response variable.
     The mathematical model for $n$ degree polynomial regression is shown in the Eq\eqref{non}
@@
  One of the limitations of using polynomial regression is the curvature that can be captured is limited with low order terms.
-However, including higher-order terms has a negative impact on the model by introducing undesirable "wiggliness" in the regression equation.
+However, including higher-order terms has a negative impact on the model by introducing undesirable "wiggliness" in the regression equation especially near the boundaries of the data.
 Another robust approach to model nonlinear relationships is splines.
 It is similar to a technique used by draftsmen in plotting curves.
-The spline is a process of constructing a set of piece-wise continuous
-<!-- polynomials that are smoothly connected at a set of points in the range of the predictor variable.
+ The spline is a process of constructing a set of piece-wise continuous polynomials that are smoothly connected at a set of points in the range of the predictor variable.
 The connection points are called knots i.e.
@@
 The family of transformation of the predictors that can be fit together to built the model's shape is known as a basis function.
-the basis functions are $b_1(x),b_2(x), \cdots,\b_k(x),$ and the estimation of $y_i$ is computed as follows: -->
+the basis functions are $b_1(x),b_2(x), \cdots,b_k(x),$ and the estimation of $y_i$ is computed as follows:
 
-<!-- \begin{equation} -->
-<!-- y_i=\beta_0+\beta_1 b_1(x_i)+\beta_2 b_2(x_i)+\cdots+ \beta_k b_k(x_i) -->
-<!-- \end{equation} -->
-<!-- This concept of a family of transformations that can fit together to capture general shapes is called a basis function.
-In this case, our objects are functions: $ b_1 (X ), b_2 (X ),\cdots , b_K (X ).$ In a more general way to represent a value of $y=f(X)$ using a peacewise cubic polybomials with a singl knote $c.$  -->
+\begin{equation}
+y_i=\beta_0+\beta_1 b_1(x_i)+\beta_2 b_2(x_i)+\cdots+ \beta_k b_k(x_i)
+\end{equation}
+This concept of a family of transformations that can fit together to capture general shapes is called a basis function.
+In this case, our objects are functions: $b_1 (X ), b_2 (X ),\cdots , b_K (X ).$ In a more general way to represent a value of $y=f(X)$ using a peacewise cubic polybomials with a singl knote $c.$
 
@@
 
-```{r resu4, out.width = "80%", fig.align = "center", fig.cap = "Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled as  quadratic .", echo = FALSE}
+```{r resu4, out.width = "80%", fig.align = "center", fig.cap = "Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled as  quadratic.", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 
-```{r resu330, out.width = "80%", fig.align = "center", fig.cap = " Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled  as B splines. ", echo = FALSE}
+```{r resu330, out.width = "80%", fig.align = "center", fig.cap = " Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled  using splines. ", echo = FALSE}
 # Created by file exploratory-data-analysis.R

### 2021-06-10 manuscript/manuscript2.tex
Update

@@
 \usepackage{float}
+\floatplacement{figure}{H}
 
@@
 \author{}
-\date{\vspace{-2.5em}May 10, 2021}
+\date{\vspace{-2.5em}June 09, 2021}
 
@@
 }
-\section{introduction}
+\section{Introduction}
 
-High BMI has negative impact on public health.
-Due to high cost of obesity, it is crucial to get better understanding of the underlying risk factor for obesity.
-This can help decision makers to create a new regulation that help to prevent and to stop the dramatic increase in the BMI index.
+High body mass index (BMI) has a negative impact on public health.
+Due to high cost of obesity, it is crucial to get better understanding of the underlying risk factors for obesity.
+This can help decision makers to create new recommendations that help to prevent and stop the dramatic increase in BMI.
 
-Body Mass Index (BMI) plays an important role in predicting heart disease risk(Katzmarzyk et al.
+BMI plays an important role in predicting heart disease risk(Katzmarzyk et al.
 2012).
-Approximately, 18 million deaths annually per year are caused by cardiovascular diseases(CVD), and similar to this number of nonfatal cardiovascular events (Hay et al.
+Approximately 18 million deaths annually per year world wide are caused by cardiovascular diseases(CVD) , and this number is similar to this number of nonfatal cardiovascular events (Hay et al.
 2017).
-In 2011, annual costs for CVD and stroke were \(\$320.1\) billion, which is more than cancer cost.
-This cost includes \$195.6 billion in direct costs (health-care costs), and the cost of future productivity loss is \$124.5 (Mozaffarian et al.
+In 2011, annual costs for CVD and stroke were estimated at \(\$320.1\) billion, which is more than spending on cancer.
+The total CVD cost includes \$195.6 billion in direct costs (health-care costs) and \$124.5 billion of future productivity loss (Mozaffarian et al.
 2015).
-Important factors associated with CVD are high body mass index (BMI) and abnormal lipid ratio (Yusuf et al.
+Important risk factors associated with CVD are high BMI and abnormal lipid ratio (Yusuf et al.
 2004), (Anderson et al.
 1991).
-Lowering low-density lipoprotein (LDL) by using statin or other drugs reduces the risk of cardiovascular diseases even with a population with no CVD (Yusuf et al.
+There are some drugs the are used reducce CVD risks by lowering low-density lipoprotein (LDL) like statin.
+Statin use reduces the risk of cardiovascular diseases, even with a population with no CVD risks (Yusuf et al.
 2016).
-Ferrieres et al.~(Ferrières et al.
-2018) studied the effect of BMI on the choice of lipid-lowering treatment.
-It is been found that statin intensity increases with the high level of BMI(\(\rho=0.13\)).
-
-Taking cholesterol drug medication associates with a high risk of elevating BMI level.
+On the other hand, statin uses have negative side effects on health conditions, such as elevating glucose levels (Castro et al.
+2016).
+The effect of BMI on the choice of lipid-lowering treatment has been studied by (Ferrières et al.
+2018).
+They found that there is a positive correlation (\(\rho=0.13\)) between statin does levels and BMI levels.
+Additionaly, taking cholesterol drug medication associates with a high risk of elevating BMI level.
 It is been shown that statin users consume 192 additional calories per day which causes gaining a 6 lb to 11 lb.
@@
 2014).
+This study gives as insight about the association between cholesterol druge uses and condition means.
+An important question to ask is, are there an associations between cholesterol drug uses and different BMI quantiles?
+This question helps us to understand cholesterol drug uses effect on the obese, overweight population, so that a decision maker take an optimal action about treatment policy.
 
-Logistic regression helps us to find out the group that has a higher odd of obesity, and ordinary least squares (OLS) regression helps us to study the effects of predictors on the average mean of the response.
-For example, estimating the association of different factors like a lipid-lowering drug with the conditional mean of BMI using OLS or logistic regression model(Ferrières et al.
+Ordinary least squares (OLS) regression helps us to study the effects of predictors on the mean of the response.
+For example, estimating the association of different factors like a lipid-lowering drug with the conditional mean of BMI (Ferrières et al.
 2018).
-Both of these approaches do not give us insight into the predictor's effects on different quantiles of the responses.
+OLS approaches does not give us insight into the predictor's effects on different quantiles of the responses.\\
+Hosever, quantile regression (QR) is used to investigate the heterogeneity in the association of the \(\tau\)th.
+quantile \(0<\tau<1\) of BMI with a set of independent predictors to investigate the effects of a specific predictors on the various quantiles of the BMI.
+Estimation of underweight and overweight regressed on age could be hard because of the trend change and nonlinearity behavior of the BMI with respect to age, as it is shown in (Flegal 1999) BMI departs normality because of the skewness on the right and left tails.
+Therefore, QR is an appropriate method used to estimate the differences in the association of the BMI with predictors.
 
-Quantile regression is used to investigate the heterogeneity in the association of the \(\tau\)th quantile of BMI with a set of independent predictors, that is investigate the effects of a specific predictors on the various quantiles of the BMI.
-BMI departs normality because of the skewness on the right and left tails (Flegal 1999).
-Estimation of underweight and overweight can be affected by the violation of normality.
-Quantile regression is a crucial tool used to estimate BMI with the dispersion of the association with predictors.
+QR has a wide range of applications.
+For example, it is used to study the association between BMI and the set of predictors; low childhood socioeconomic position, high maternal weight, low childhood general cognition is stronger in the upper end of BMI quantile in the UK population(Bann, Fitzsimons, and Johnson 2020).
+One cause of this heterogeneity is that risk factors may have stronger effect on patients with worse health, and these effects may diminishes when conditional distribution of the BMI is studied.
+Moreover, another application of using QR is in ecology where different factors interact in a complicated way that produces different variations of one factor for different levels of another variable (Cade and Noon 2003).
 
-Quantile regression has many successful applications in ecology where different factors interact in a complicated way that produces different variations of one factor for different levels of another variable (Cade and Noon 2003).
-The association between BMI and the set of predictors; low childhood socioeconomic position, high maternal weight, low childhood general cognition is stronger in the upper end of BMI quantile.
-This trend is found in the UK population(Bann, Fitzsimons, and Johnson 2020).
-One cause of this heterogeneity is that risk factors may have stronger effect on patients with worse health, and these effects may diminishes when conditional mean of the BMI is studied.
-
+Polynomial regression using the quadratic term of predictors forces the response to take convex or concave shape, see Figure 1.12 (Koenker 2005).
+This is because the limit of the response variable \(y\), when modeled as a quadratic function of the predictor variable \(x\), approach \(\pm\infty\) ( i.e.,as \(x \rightarrow\pm\infty,\) \(y\rightarrow\pm\infty.\) However, when we model the the reponse variable using a spline basis expansion of the predictor variable the response is not forced to take a specific shape.
+In the latter case, different polynomials are constructed for the different regions in the range of predictors the satisfies continuity and smoothness conditions at the knots.
 We found that spline regressions produce a different estimate than polynomial regressions.
-Polynomial regression using the quadratic term of predictors forces the response to take convex or concave shape, see Figure 1.12 (Koenker 2005).
-This is because the limit of quadratic functions approach \(\pm\infty\) as \(x\rightarrow\pm\infty.\) However, when we model the predictor as splines the response is not forced to take a specific shape.
-In the latter case, different polynomials are constructed for the different regions in the range of predictors.
 
@@
 The spline is a process of constructing a set of piece-wise continuous
+polynomials that are smoothly connected at a set of points in the range of the predictor variable.
+The connection points are called knots i.e.~splines are used to smoothly interpolate between certain points.
+Let \(a,b\) ,and \(c\) are the endpoints of the \(x-\)axis intervals.
+A transformation for some or all of predictors is needed to capture the nonlinearity in the model.
+The family of transformation of the predictors that can be fit together to built the model's shape is known as a basis function.
+the basis functions are \(b_1(x),b_2(x), \cdots,b_k(x),\) and the estimation of \(y_i\) is computed as follows:
+
+\begin{equation}
+y_i=\beta_0+\beta_1 b_1(x_i)+\beta_2 b_2(x_i)+\cdots+ \beta_k b_k(x_i)
+\end{equation}
+This concept of a family of transformations that can fit together to capture general shapes is called a basis function.
+In this case, our objects are functions: \(b_1 (X ), b_2 (X ),\cdots , b_K (X ).\) In a more general way to represent a value of \(y=f(X)\) using a peacewise cubic polybomials with a singl knote \(c.\)
 
@@
 
-\caption{Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled as  quadratic .}\label{fig:resu4}
+\caption{Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled as  quadratic.}\label{fig:resu4}
 \end{figure}
@@
 
-\caption{ Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled  as B splines. }\label{fig:resu330}
+\caption{ Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled  using splines. }\label{fig:resu330}
 \end{figure}

### 2021-06-10 ci_splin.R

@@ -29,7 +29,7 @@ dat$Age=as.numeric(dat$Age)
 
 
 fit_rq=function(dat,index,tau){
-    if (index==1) {formula=BMI ~ bs(Age, df = 3) + Race + Gender + Cholesterol_Drug_Use}
+    if (index==1) {formula=BMI ~ bs(Age, df = 5) + Race + Gender + Cholesterol_Drug_Use}
     else if(index ==2) {formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use}
     else if (index==3) {formula=BMI ~ Age+Age^2+ Race + Gender + Cholesterol_Drug_Use}
     else{formula=BMI ~ Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use}
@@ -76,7 +76,7 @@ dat_pred_ready=function(dat,index,tau){
     dat_pred$Race=recode(dat_pred$Race, "1" = "Mexican", "2" = "Other_Hispanic","3"="White","4"="Black","5"="Other" )
     
     if(index==1){
-        X_pred <- model.matrix( ~ bs(Age, df = 3) + Race + Gender+ Cholesterol_Drug_Use , data = dat_pred)
+        X_pred <- model.matrix( ~ bs(Age, df = 5) + Race + Gender+ Cholesterol_Drug_Use , data = dat_pred)
         
     }else if(index==2){
         X_pred <- model.matrix(~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use,data=dat_pred)
@@ -320,5 +320,7 @@ dev.off()
 
 ggpredict(fit,"Age [all]")
 df=ggpredict(fit,"Age [all]")
-ggplot(df,aes(x,predicted))+geom_line()+geom_ribbon(aes(ymin=conf.low,ymax=conf.high),alpha=0.1)
+ggplot(df,aes(x,predicted))+
+    geom_line()+
+    geom_ribbon(aes(ymin=conf.low,ymax=conf.high),alpha=0.1)
 

### 2021-06-10 ci_splin_marg_effect.R

@@ -132,7 +132,7 @@ dat1 <- rbind(
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
    xlab("Age")+
    ylab("BMI")+
-   ggtitle("Age effect on BMI 0.01 Quantile ")
+   ggtitle("Age effect on BMI 0.1 Quantile ")
  
 #####################
 # 0.5% 
@@ -154,7 +154,7 @@ dat1 <- rbind(
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
    xlab("Age")+
    ylab("BMI")+
-   ggtitle("Age effect on BMI 0.05 Quantile ")
+   ggtitle("Age effect on BMI 0.5 Quantile ")
  
  
  ##########################
@@ -202,7 +202,7 @@ dat1 <- rbind(
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
    xlab("Age")+
    ylab("BMI")+
-   ggtitle("Age effect on BMI 0.09 Quantile ")
+   ggtitle("Age effect on BMI 0.9 Quantile ")
  
  
  ############

### 2021-07-30 manuscript/manuscript2.Rmd
update

@@
 
-  BMI plays an important role in predicting heart disease risk[@katbody].
-Approximately 18 million deaths annually per year world wide are caused by cardiovascular diseases(CVD) , and this number is similar to this number of nonfatal cardiovascular events [@hay2017gbd].
+  BMI plays an important role in predicting heart disease risk [@katbody].
+Approximately 18 million deaths annually per year world wide are caused by cardiovascular diseases(CVD), and this number is similar to the number of nonfatal cardiovascular events [@hay2017gbd].
 In 2011, annual costs for CVD and stroke were estimated at $\$320.1$ billion, which is more than spending on cancer.
 The total CVD cost includes \$195.6  billion in direct costs (health-care costs) and \$124.5 billion of future productivity loss [@mozaffarian2015executive].
-Important risk factors associated with CVD are high BMI and abnormal lipid ratio  [@yusuf2004effect], [@anderson1991].
-There are some drugs the are used reducce CVD risks by lowering low-density lipoprotein (LDL) like statin.
+Important risk factors associated with CVD are high BMI and abnormal lipid ratio  [@yusuf2004effect;@anderson1991].
+There are some drugs that are used reducce CVD risks by lowering low-density lipoprotein (LDL) like statin.
 Statin use  reduces the risk of cardiovascular diseases, even with a population with no CVD risks  [@yusuf2016].
@@
 in a year.
-Statin users gain 1.3 units in the BMI measure while non-staining users gain 0.4 unit.
+Statin users gain 1.3 units in the BMI measure while non-staining users gain 0.4 BMI unit.
 Moreover, consumption of fat in statin users raised by 14.4%[@sugiyama2014].
-This study gives as insight about the association between cholesterol druge uses and condition means.
+This study gives us insight about the association between cholesterol drug uses and condition means of the BMI.
+
 An important question to ask is, are there  an associations between cholesterol drug uses and different BMI quantiles?
@@
 OLS approaches does not give us insight into the predictor's effects on different quantiles of the responses.
-  Hosever, quantile regression (QR) is used to investigate the heterogeneity in the association of the $\tau$th.
-quantile $0<\tau<1$ of BMI with a set of independent predictors to investigate the effects of a specific predictors on the various quantiles of the BMI.
-Estimation of underweight and overweight regressed on age could be hard because of the trend change and nonlinearity behavior of the BMI with respect to age, as it is shown in [@flegal1999] BMI departs normality because of the skewness on the right and left tails.
+  However, quantile regression (QR) is used to investigate the heterogeneity in the association of the $\tau$th quantile $0<\tau<1$ of BMI with a set of independent predictors to investigate the effects of a specific predictors on the various quantiles of the BMI.
+Estimation of underweight and overweight regressed on age could be hard because of the trend change and nonlinearity behavior of the BMI with respect to age, as it is shown in [@flegal1999].
+  <!-- BMI departs normality because of the skewness on the right and left tails. -->
   Therefore, QR is an appropriate method used to estimate the differences in the  association of the BMI with predictors.
@@
  We compare two approaches to study the QR of BMI regressed on age and total cholesterol (TC) levels.
-One approch is called quantile polynomial regression.
+One approach is called quantile polynomial regression.
 It is defined as a way to model the non-relationship between predictors and distribution of the  response as an $n$th degree polynomial in the predictors.
+And the other approach is using a spline basis expansion of the predictors.
   Polynomial regression using the quadratic term of predictors forces the response to take convex or concave shape, see Figure 1.12 [@koenker2005].
@@
 
-\begin{equation}
-y_{i}=
- \left\{
-\begin{array}{ll}
- \beta_{01}+\beta_{11}x_i+\beta_{21}x_i^2+ \beta_{31}x_i^3+	\epsilon_i & \mbox{if } x_i< c \\
- \beta_{02}+\beta_{12}x_i+\beta_{22}x_i^2+ \beta_{23}x_i^3+	\epsilon_i& \mbox{if } x_i \geq c
-\end{array}
-\right.
-\end{equation}
+<!-- \begin{equation} -->
+<!-- y_{i}= -->
+<!--  \left\{ -->
+<!-- \begin{array}{ll} -->
+<!--  \beta_{01}+\beta_{11}x_i+\beta_{21}x_i^2+ \beta_{31}x_i^3+	\epsilon_i & \mbox{if } x_i< c \\ -->
+<!--  \beta_{02}+\beta_{12}x_i+\beta_{22}x_i^2+ \beta_{23}x_i^3+	\epsilon_i& \mbox{if } x_i \geq c -->
+<!-- \end{array} -->
+<!-- \right. -->
+<!-- \end{equation} -->
 Imposing a continuity condition  and first, and second derivative at $c$ are equal in the two sides, we get a cubic splines.
@@
 
- The independent variables in our model are gender, race, age, total cholesterol, cholesterol drug use (yes or no).
+ The independent variables in our model are gender, race, age, total cholesterol and cholesterol drug use (yes or no).
 All types of cholesterol drugs are used including statins.
 The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.
-The following formulas represents the different model that presented in the result.
+The following formulas represents the different QR models that fit conditional distribution of BMI on :
 
- \begin{equation}
- \hat{BMI}= bs(Age, df = 5) + Race + Gender + Cholesterol Drug Use
- \end{equation}
+ \begin{itemize}
+ \item Model I: Age enters the model as spline basis expansion, Race, Gender, and cholesterol drug use (Yes or No).
+ \item Model II: TC enters the model as spline basis expansion, Race, Gender, and cholesterol drug use.
+ \item Model III: Age enters the model as a quadratic factor, Race, Gender, and cholesterol drug use.
+ \item Model IV: TC enters the model as a quadratic factor, Race, Gender, and cholesterol drug use. 
+ \end{itemize}
 
- \begin{equation}
- \hat{BMI}= bs(Total chol, df=5)+ Race + Gender + Cholesterol Drug Use
- \end{equation}
+ <!-- \begin{equation} -->
+ <!-- \hat{BMI}= bs(Age, df = 5) + Race + Gender + Cholesterol Drug Use -->
+ <!-- \end{equation} -->
 
- \begin{equation}
- \hat{BMI}= Age+Age^2+ Race + Gender + Cholesterol Drug Use 
- \end{equation}
+ <!-- \begin{equation} -->
+ <!-- \hat{BMI}= bs(Total chol, df=5)+ Race + Gender + Cholesterol Drug Use -->
+ <!-- \end{equation} -->
 
- \begin{equation}
- \hat{BMI}= Total chol+ Total chol^2+ Race + Gender + Cholesterol Drug_Use
- \end{equation}
+ <!-- \begin{equation} -->
+ <!-- \hat{BMI}= Age+Age^2+ Race + Gender + Cholesterol Drug Use  -->
+ <!-- \end{equation} -->
+
+ <!-- \begin{equation} -->
+ <!-- \hat{BMI}= Total chol+ Total chol^2+ Race + Gender + Cholesterol Drug_Use -->
+ <!-- \end{equation} -->
 
@@
 The survey examines a nationally representative sample of the U.S.
-population.
-It focuses on a variety of health and nutrition measurements.
-The survey data are released every two years cycle.
+population focusing on a variety of health and nutrition measurements releasing two year cycle.
 In this study, we accumulated 6 cycles of NHANES data (2007–2018).
-We used two data files: One contains demographic variables, such as age, sex, race, income, etc., and the other contains data that are related to body measurements, such as BMI, head circumference, etc.
-These files are merged by using the respondent sequence number (SEQN)
- There are around 12,000 records. We selected a population age between 20 and 80.
+We used two data files: One contains demographic variables, such as age, sex, race, income, etc.
+and the other contains data that are related to body measurements, such as BMI, head circumference, etc.
+These files are merged by using the respondent sequence number (SEQN) resulting in a around 12,000 records.
+We selected a population age between 20 and 80.
  BMI are classified into different categories according to underweight, 18.5 kg/m2; normal weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/m2; obese, 30 to 35 kg/m2; and very obese more than 35 kg/m2.
@@
 
-Figure \@ref(fig:box) shows the association between age and BMI with respect to cholesterol drug is inconsistent.
-At the early age, the correlation is positive while at the middle age the correlation is almost flat, and at the old age the correlation is negative.
+Figure \@ref(fig:box) shows the association between age and BMI with respect to cholesterol drug changes based on age.
+At the younger ages, the correlation is positive while at the middle age the correlation is almost flat, and at the old age the correlation is negative.
 Moreover, at low age cholesterol medications are  described only for a population with high BMI, but at a higher age, the difference in term of the BMI for a population that takes cholesterol medication and without cholesterol medication decreases until it diminishes as in the white population.
 The  heterogeneity can also be seen in gender ?, for the Hispanic female population, the cholesterol medication is taken by the population with lower BMI if compared to the population that does not take cholesterol medication.
-
-```{r data, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
-# Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "exploratory.png"))) {
-    source(here::here("exploratory-data-analysis.R"))
-}
-knitr::include_graphics(here::here("images", "exploratory.png"))
-```
 
@@
 \section{Results}
-The resulting estimate of effects on conditional mean of BMI level may not reflect the size and nature of these effects on lower or upper quantile.
-For example, in Figure \@ref(fig:resu1), the conditional mean effect of gender on BMI level is about -1, that is on average male's BMI is less than a female's BMI by one unit.
-However, the disparity of the gender effects on lower tails is much larger which is about 1, but the disparity is lower for the upper tail of the distribution somewhat around -3 unit.
+Figures \@ref(fig:resu1) and \@ref(fig:resu12) illustrate marginal effects of predictors on different quantiles, where in the first plot age and total cholesterol entered the model as quadratic terms while in the second plot, spline basis expansion is used to model age and total cholesterol.
+First, we look at the differences in the plot that is due to using OLS vs QR, then we look at the differences due to the using quadratic term to model predictors vs spline basis expansion.
+
+From Figures \@ref(fig:resu1), we can see the effects on conditional mean of BMI level may not reflect the size and nature of these effects on lower or upper quantiles.
+For example, the conditional mean effect of gender on BMI level is about -1 BMI unite, that is, on average a male BMI is less than  female BMI by one BMI unit.
+However, at the lower quantiles males have higher BMI by 1 BMI unite.
+Then, the differences start to diminish up to 0 at 40th quantile.
+At higher quantiles, a male BMI is less than a female BMI.
+For example, at 60th quantile a male BMI is less than a female BMI by 1 unite, and it continue to increase up to 3 BMI unites at 90th quantile.
 
 From the OLS it is obvious cholesterol drug users have on average higher BMI levels if compared to non-cholesterol drug users which are around 1.75.
-The disparity in BMI level for cholesterol drug users vs non-cholesterol drug users is almost the same for different Quantiles.
-cholesterol drug use seems to be associated with rather large effects on BMI levels somewhat around 1.5 to 1.7.
+The disparity is almost regular through different BMI quantiles.
+For example, in the lower quantiles of the distribution the cholesterol drug users have higher BMI value by about 1.5 units, but around at 50 th percentile of the conditional distribution the difference is 1.8 BMI units.
+Overall,  cholesterol drug use seems to be associated with rather large effects on BMI levels somewhat between  1 to 2 BMI units.
 
@@
 
- Age effect modeled as a quadratic factor.
-The age effect is concave in general, see Figure \@ref(fig:resu3).
-At the lower quantile, BMI increases from age 20 to around age 50, and it starts to decrease after that.
-In the 55th quantile, the concavity is stronger at age 50 if compared to the left or right tail.
-The quadratic effect of age is reflected in the hyperbolic shape.
-However, the age effect modeled as b spline behaves in a different way.
-Age effect on BMI increases from age 20 to around age 36 and then start to decrease up to around age 63 then move up again and then decreases up to age 80, see Fig.\@ref(fig:resu33).
-The BMI trend in this modeling is close to the trend shown in [@chen2005] by using a complicated polynomial and log transformation for the response.
+Figure \@ref(fig:resu1000) illustrate the differences in modeling Age in two different ways (Model I; spline basis expansion) and (Model III; quadratic factor ).  
+ Model I shows, at the lower quantile, the marginal age effects on BMI increase from age 20 to around age 75, and it starts to decrease after that.
+While model III shows there is a positive relationship in general.
+In the 50th quantile, model I shows age effect on BMI almost consistent result with the 0.1th quntile, but model III shows age effects approximately has flat effects.
+At a $(\tau=0.75)$ quantile of the conditional BMI distribution, model I shows a strong positive relationship between age and BMI for the age period from 20 to 33, and after that a negative  relationship, while model III shows a mild negative relationship in general.
+At a higher quantile $(\tau=0.9)$ of the conditional BMI distribution, we have a similar behavior as in 0.75th quantile except the relationship is stronger.The BMI trend in this modeling is close to the trend shown in [@chen2005] by using a complicated polynomial and log transformation for the response.
+Our conclusion from Figure \@ref(fig:resu1000) is that the marginal age effects on BMI is different on different quantiles.
+Moreover, modeling age as quadratic term or as spline basis expansion produce different effect with respect to differnt  quantile of the conditional BMI distribution.
 
-```{r resu3, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic age effect on BMI leveles for four different quantiles of the conditional BMI distribution.
-", echo = FALSE}
+```{r resu1000, out.width = "100%", fig.align = "center", fig.cap = "  An illustration of  marginal effects of age on different BMI quantiles.
+The predictors modeled using quadratic terms and basis splines expension.", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "comp_age_mixed")))  
+knitr::include_graphics(here::here("images", "comp_age_mixed.png"))
+```
+
+Next, we will investigate marginal effect of TC on four different quntiles of the conditional distribution of the BMI. 
+The quadratic effect of total cholesterol on the conditional distribution of BMI is convex.
+At the lower tail, the correlation is positive that is as cholesterol increases the BMI increases.
+decreasing glucose level by somewhat around 1.4 up to around 180 Cholesterol level.
+However, at higher quantile the association become negative that is as cholesterol level increases the BMI decreases, see  Figure \@ref(fig:resu4).
+The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014],[@chang2011].
+They found that there is a positive correlation between the two groups on average.
+
+On the other hand, when we use splines to modeled the total cholesterol, there is a huge difference in the shape of the association expect at the higher quantile there is some similarity.
+At the lower quantile, there is negative correlation between total cholesterol and BMI for total cholesterol in the range less than 160, then the correlation becomes positive for total cholesterol in the range of (170, 250).
+at the 55th quantile, the correlation is positive for low cholesterol level and then becomes almost flat for the rest cholesterol values.
+At a higher quntile, the correlation becomes negative at cholesterol level in the range (160,300), see Figure \@ref(fig:resu1010).
+
+```{r resu1010, out.width = "100%", fig.align = "center", fig.cap = " An illustration of  marginal effects of total cholesterol  on different BMI quantiles.
+The predictors modeled using quadratic terms and splines.", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "comp_tot_mixed")))  
+knitr::include_graphics(here::here("images", "comp_tot_mixed.png"))
+```
+
+Figure \@ref(fig:resu3) illustrates age effects on 90th BMI quantile, where age modeled as a quadratic term.
+There is a clear association between age and BMI.
+For example, at early ages for a non cholesterol drug users female Mexican, age effects is around 40 BMI unite, but it decreases later up to 35 at age 80 years.
+The effects of age is higher for cholesterol drug users which is about 2 BMI units.
+Moreover,  male Mexicans have higher BMI than femals by about 2 BMI unites.
+The lowest age effects on 90th BMI quantile is found in the white race.
+Figure \@ref(fig:resu33) prsents age effect
+```{r resu3, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic age effect on 90th BMI quantile for different race ethnacity groups.", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 ```
-Using splines
-```{r resu33, out.width = "80%", fig.align = "center", fig.cap = "Age effect modeled using bsplines ", echo = FALSE}
+
+```{r resu33, out.width = "80%", fig.align = "center", fig.cap = "Illusteration of the age effect on the 90th BMI quantile, where age modeled using spline basis expension.
+The effect shown for diiferent race/ethenicity groups and gender.", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 
-```{r resu1000, out.width = "100%", fig.align = "center", fig.cap = "  An illustration of  marginal effects of age on different BMI quantiles.
-The predictors modeled using quadratic terms and splines.", echo = FALSE}
-# Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "comp_age_mixed")))  
-knitr::include_graphics(here::here("images", "comp_age_mixed.png"))
-```
-
-```{r resu1010, out.width = "100%", fig.align = "center", fig.cap = " An illustration of  marginal effects of total cholesterol  on different BMI quantiles.
-The predictors modeled using quadratic terms and splines.", echo = FALSE}
-# Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "comp_tot_mixed")))  
-knitr::include_graphics(here::here("images", "comp_tot_mixed.png"))
-```
-
-The quadratic effect of total cholesterol on the conditional distribution of BMI is convex.
-At the lower tail, the correlation is positive that is as cholesterol increases the BMI increases.
-decreasing glucose level by somewhat around 1.4 up to around 180 Cholesterol level.
-However, at higher quantile the association become negative that is as cholesterol level increases the BMI decreases, see  Figure \@ref(fig:resu4).
-The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014],[@chang2011].
-They found that there is a positive correlation between the two groups on average.
-
-On the other hand, when we use splines to modeled the total cholesterol, there is a huge difference in the shape of the association expect at the higher quantile there is some similarity.
-At the lower quantile, there is negative correlation between total cholesterol and BMI for total cholesterol in the range less than 160, then the correlation becomes positive for total cholesterol in the range of (170, 250).
-at the 55th quantile, the correlation is positive for low cholesterol level and then becomes almost flat for the rest cholesterol values.
-At a higher quntile, the correlation becomes negative at cholesterol level in the range (160,300), see Figure \@ref(resu330).
-
 \section{Conclusion}

### 2021-07-30 Q_reg_plot.R

@@ -133,7 +133,7 @@ for(i in c(6,9,15,22)){
 }
 dev.off()
 
-#Total cholestrol effects on glucose.
+#Total cholesterol effects on glucose.
 
 png(file = here::here("images", "p_TC_effect.png"),
     res = 400, height = 9, width = 16, units = "in")

### 2021-07-30 Q_reg_plot2.R

@@ -79,7 +79,7 @@ for(i in c(1:17)){
 }
 dev.off()
 
-
+attr(bs(bmi.data$Age,intercept=FALSE,df=5), "knots")
 
 ###########################
 #Or we can get this plot using quant regression summary plot.

### 2021-07-30 ci_splin.R

@@ -31,8 +31,8 @@ dat$Age=as.numeric(dat$Age)
 fit_rq=function(dat,index,tau){
     if (index==1) {formula=BMI ~ bs(Age, df = 5) + Race + Gender + Cholesterol_Drug_Use}
     else if(index ==2) {formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use}
-    else if (index==3) {formula=BMI ~ Age+Age^2+ Race + Gender + Cholesterol_Drug_Use}
-    else{formula=BMI ~ Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use}
+    else if (index==3) {formula=BMI ~poly(Age,2)+ Race + Gender + Cholesterol_Drug_Use}
+    else{formula=BMI ~ poly(Total_chol,2)+ Race + Gender + Cholesterol_Drug_Use}
     message("model.matrix")
     X <- model.matrix(formula,data=dat)
     qr_fit_dat <- rq( BMI ~ X - 1, data=dat, tau = tau)
@@ -81,14 +81,14 @@ dat_pred_ready=function(dat,index,tau){
     }else if(index==2){
         X_pred <- model.matrix(~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use,data=dat_pred)
     }else if (index==3) { message("pred.model.matrix")
-        X_pred <- model.matrix(~Age+Age^2+ Race + Gender + Cholesterol_Drug_Use,data=dat_pred)
-    } else{X_pred <- model.matrix(~Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use,data=dat_pred)
+        X_pred <- model.matrix(~poly(Age,2)+ Race + Gender + Cholesterol_Drug_Use,data=dat_pred)
+    } else{X_pred <- model.matrix(~poly(Total_chol,2)+ Race + Gender + Cholesterol_Drug_Use,data=dat_pred)
     
     }
     
     
     fit=fit_rq(dat,index,tau)
-    message("fit.model.matrix")
+     
     dat_prediction <- list(X = X_pred)
     message("A")
     pred <- predict(fit, newdata =dat_prediction, interval = "confidence")
@@ -181,7 +181,7 @@ dat_pred=dat_pred_ready(dat,index =4 ,tau =0.9 )
 
[…]

### 2021-07-30 ci_splin_marg_effect.R

@@ -31,8 +31,8 @@ dat$Age=as.numeric(dat$Age)
 fit_rq=function(dat,index,tau){
     if (index==1) {formula=BMI ~ bs(Age, df = 5) + Race + Gender + Cholesterol_Drug_Use}
     else if(index ==2) {formula=BMI ~ bs(Total_chol, df=5)+ Race + Gender + Cholesterol_Drug_Use}
-    else if (index==3) {formula=BMI ~ Age+Age^2+ Race + Gender + Cholesterol_Drug_Use}
-    else{formula=BMI ~ Total_chol+ Total_chol^2+ Race + Gender + Cholesterol_Drug_Use}
+    else if (index==3) {formula=BMI ~ poly(Age,2)+ Race + Gender + Cholesterol_Drug_Use}
+    else{formula=BMI ~ poly(Total_chol,2)+ Race + Gender + Cholesterol_Drug_Use}
     message("model.matrix")
     X <- model.matrix(formula,data=dat)
     # qr_fit_dat <- rq( BMI ~ X - 1, data=dat, tau = tau)
@@ -91,6 +91,7 @@ fit=fit_rq(dat,index=2,tau=0.9)
 fit2=ggpredict(fit,"Total_chol [all]")
 fit=fit_rq(dat,index=3,tau=0.9)
 fit3=ggpredict(fit,"Age")
+#fit33=ggpredict(fit,~Age+Age^2)
 fit=fit_rq(dat,index=4,tau=0.9)
 fit4=ggpredict(fit,"Total_chol")
 

### 2021-07-30 exploratory-data-analysis_JRT.R

@@ -10,7 +10,7 @@ library(quantreg)
 library(splines)
 
 
-bmi.data<- read.csv(here::here("BMI/data", "ldl2.csv"),header=TRUE, sep=",")
+bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
 
 #remove duplicated rows and remove na data.
 bmi.data=bmi.data[!duplicated(bmi.data[ , c("SEQN")]),]
@@ -92,7 +92,7 @@ print(bmi.data %>%
 ########################################################
 
 dat=data.frame(bmi.data$Age,as.factor(bmi.data$Race),as.factor(bmi.data$Gender),as.factor(bmi.data$Cholesterol_Drug_Use),bmi.data$BMI,bmi.data$Type_glu)
-colnames(dat) <- c("Age","Race","Gender","Cholesterol_Drug_Use","BMI","Type_glu")
+colnames(dat) <- c("Age","Race","Gender","Drug_Use","BMI","Type_glu")
 dat$Cholesterol_Drug_Use=recode(dat$Cholesterol_Drug_Use, "1" = "Yes", "0" = "No" )
 ggplot(dat, aes(y=BMI  ,x=Age)) +
     geom_point()
@@ -115,10 +115,10 @@ Age_10 <- as.factor(temp)
 dat <- cbind(dat,Age_10)
 dat=na.omit(dat)
 
-png(file = here::here("BMI/images", "base_box_plot.png"),
+png(file = here::here("images", "base_box_plot.png"),
     res = 400, height = 14, width = 20, units = "in")
 
-p<-ggplot(dat, aes(x=Age_10, y=BMI, color=Cholesterol_Drug_Use)) +
+p<-ggplot(dat, aes(x=Age_10, y=BMI, color=Drug_Use)) +
     geom_boxplot(notch = FALSE, fill = "lightgray" )+
     stat_summary(fun = mean, geom = "point",
                  shape = 18, size = 2.5, color = "#FC4E07")+
@@ -141,15 +141,15 @@ dev.off()
 ##
 #### quantile regression 
 ## 
-fig3=ggplot(dat, aes(Age ,BMI, group = Cholesterol_Drug_Use)) + 
+fig3=ggplot(dat, aes(Age ,BMI, group = Drug_Use)) + 
     #geom_point() + 
     #geom_quantile(aes(color = Cholesterol_Drug_Use), quantiles = 0.8) +
[…]

### 2021-08-27 manuscript/manuscript2.Rmd
Update

@@
     - \floatplacement{figure}{H}
-abstract: "My abstract"
+abstract: "Body Mass index plays an important role in predicting cardioviscalr diseases, strokes, diabetes and many others.
+In this article we use quantile regression to study the effects of age, total cholesterol, cholesterol drug use on the conditional distribution of BMI and it is been compared to the result obtained by ordinary least squares approach.
+The national health and nutrition examination survey (NHANES) data is used in this study.
+The differences between using quadratic terms and spline basis expansion for the predictors is also presented.
+"
 keywords: "My keywords"
@@
 <!-- \setstretch{4} -->
+\newpage
 \section{Introduction}
 
-  High body mass index (BMI) has a negative impact on public health.
+  High body mass index (BMI) has a negative impact on public health[@nuttall2015body].
+There is a positive relation between the risk of death from all causes, cardiovascular disease, cancer, or other diseases and BMI for both genders[@calle1999body].
 Due to high cost of obesity, it is crucial to get better understanding of the underlying risk factors for obesity.
@@
 Statin use  reduces the risk of cardiovascular diseases, even with a population with no CVD risks  [@yusuf2016].
-On the other hand, statin uses have negative side effects on health conditions, such as elevating glucose levels [@castro2016].
+On the other hand, statin uses associate with negative side effects on health conditions, for example, BMI.
 The effect of BMI on the choice of lipid-lowering treatment has been studied by [@ferrieres2018].
@@
   Polynomial regression using the quadratic term of predictors forces the response to take convex or concave shape, see Figure 1.12 [@koenker2005].
-This is because the limit of the response variable $y$, when modeled as a quadratic function of the predictor variable $x$,  approach $\pm\infty$ ( i.e.,as $x \rightarrow\pm\infty,$ $y\rightarrow\pm\infty.$ However, when we model the the reponse variable using a spline basis expansion of the predictor variable the response is not forced to take a specific shape.
+This is because the limit of the response variable $y$, when modeled as a quadratic function of the predictor variable $x$,  approach $\pm\infty$ ( i.e., as $x \rightarrow\pm\infty,$ $y\rightarrow\pm\infty).$ However, when we model the the response variable using a spline basis expansion of the predictor variable the response is not forced to take a specific shape.
 In the latter case, different polynomials are constructed for the different regions in the range of predictors that satisfy continuity and smoothness conditions at the knots.
@@
 
-OLS method expresses the conditional mean of $y$ given $x$ as $\mu(x)=x^T\beta$ and it solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.$$ On the other hand, QR expresses the conditional quantile function $Q_y(\tau|x)=x^T \beta ({\tau)}$ and solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.$$This minimization problem can be reformulated to a linear programming problem and solved using standard statistical software.
+OLS method expresses the conditional mean of $y$ given $x$ as $\mu(x)=x^T\beta$ and it solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.$$ 
+The above equation represent the loss function for the OLS regression.By solving this equation for the minimum values for $\beta,$ we get regression equation, which is $\hat{y}=x_i^T\beta$.
+On the other hand, QR expresses the conditional quantile function $Q_y(\tau|x)=x^T \beta ({\tau)}$ and solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.$$
+The above This minimization problem can be reformulated to a linear programming problem and it can be solved using standard statistical software.
 
@@
 All types of cholesterol drugs are used including statins.
-The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.
+The included races are non-Hispanic white, non-Hispanic black, Hispanic, and others.
+The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014],[@chang2011].
+They found that there is a positive correlation between the two groups on average.
+Therefore, fasting glucose level is not included to avoid collinearity.
 The following formulas represents the different QR models that fit conditional distribution of BMI on :
@@
 The survey examines a nationally representative sample of the U.S.
-population focusing on a variety of health and nutrition measurements releasing two year cycle.
+population focusing on a variety of health and nutrition measurements released in two year cycle.
 In this study, we accumulated 6 cycles of NHANES data (2007–2018).
@@
 These files are merged by using the respondent sequence number (SEQN) resulting in a around 12,000 records.
+The missing values are deleted.
 We selected a population age between 20 and 80.
- BMI are classified into different categories according to underweight, 18.5 kg/m2; normal weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/m2; obese, 30 to 35 kg/m2; and very obese more than 35 kg/m2.
+ BMI are classified into different categories according to underweight, 18.5 $kg/m^2$; normal weight, 18.5 to 25 $kg/m^2$; overweight, 25 to 30 $kg/m^2$; obese, 30 to 35 $kg/m^2$; and very obese more than 35 $kg/m^2$.
 
@@
 From Figures \@ref(fig:resu1), we can see the effects on conditional mean of BMI level may not reflect the size and nature of these effects on lower or upper quantiles.
-For example, the conditional mean effect of gender on BMI level is about -1 BMI unite, that is, on average a male BMI is less than  female BMI by one BMI unit.
-However, at the lower quantiles males have higher BMI by 1 BMI unite.
+For example, the conditional mean effect of gender on BMI level is about -1 $kg/m^2$, that is, on average a male BMI is less than  female BMI by 1 $kg/m^2$.
+However, at the lower quantiles males have higher BMI by 1 $kg/m^2$.
 Then, the differences start to diminish up to 0 at 40th quantile.
 At higher quantiles, a male BMI is less than a female BMI.
-For example, at 60th quantile a male BMI is less than a female BMI by 1 unite, and it continue to increase up to 3 BMI unites at 90th quantile.
+For example, at 60th quantile a male BMI is less than a female BMI by 1 $kg/m^2$, and it continue to increase up to 3$kg/m^2$ at 90th quantile.
 
@@
 The disparity is almost regular through different BMI quantiles.
-For example, in the lower quantiles of the distribution the cholesterol drug users have higher BMI value by about 1.5 units, but around at 50 th percentile of the conditional distribution the difference is 1.8 BMI units.
-Overall,  cholesterol drug use seems to be associated with rather large effects on BMI levels somewhat between  1 to 2 BMI units.
+For example, in the lower quantiles of the distribution the cholesterol drug users have higher BMI value by about 1.5 $kg/m^2$, but around at 50 th percentile of the conditional distribution the difference is 1.8 BMI units.
+Overall,  cholesterol drug use seems to be associated with rather large effects on BMI levels somewhat between  1 to 2 $kg/m^2$.
 
@@
 Figure \@ref(fig:resu1000) illustrate the differences in modeling Age in two different ways (Model I; spline basis expansion) and (Model III; quadratic factor ).  
- Model I shows, at the lower quantile, the marginal age effects on BMI increase from age 20 to around age 75, and it starts to decrease after that.
-While model III shows there is a positive relationship in general.
-In the 50th quantile, model I shows age effect on BMI almost consistent result with the 0.1th quntile, but model III shows age effects approximately has flat effects.
-At a $(\tau=0.75)$ quantile of the conditional BMI distribution, model I shows a strong positive relationship between age and BMI for the age period from 20 to 33, and after that a negative  relationship, while model III shows a mild negative relationship in general.
-At a higher quantile $(\tau=0.9)$ of the conditional BMI distribution, we have a similar behavior as in 0.75th quantile except the relationship is stronger.The BMI trend in this modeling is close to the trend shown in [@chen2005] by using a complicated polynomial and log transformation for the response.
+ Model I shows, at the lower quantile, the marginal age effects on BMI increases from age 20 to around age 42, and then it stays flat up to age 70 but it starts to decrease after that.
+While model III shows that there is positive relationship between Age and BMI in the age range between 20 and 50.
+Then age effects stay flat in the age range between 50 and 60 years old and decreases after that.
+
+ At the 50th quantile, model I shows the highest age effect on BMI occurs earlier by 10 years when compares to the lower quantile, but model III shows maximum effect occurs at around age 50, which is similar to the age effect at lower quantiles.
+The age effects start to decrease using Model I at around 70 years old while model III shows the decay starts at  around age 60.
+ At higher quantiles $\tau=75$, using Model I, the maximum age effects occurs earlier by three years, but Model III shows the highest age effects occurs at around age 50.
+The decay starts at around  .
+Convex behavior of the quadratic term has a clear pattern in formulating age effects on the BMI.
+The box plot (Fig.
+\@ref(fig:box))   supports Model I results because the highest mean and inter quantile range occurs at age 30.
+
+Using Model I, at the 90th quantile of the conditional BMI distribution, we have a similar behavior as in 0.75th quantile except the relationship is stronger, i.e, for example, the age effects at age 20 is 37 $kg/m^2$ while at the later the effect is 30 BMI unit.
+The BMI trend in this modeling is close to the trend shown in [@chen2005], which computed using a complicated polynomial and log transformation for the response.
 Our conclusion from Figure \@ref(fig:resu1000) is that the marginal age effects on BMI is different on different quantiles.
-Moreover, modeling age as quadratic term or as spline basis expansion produce different effect with respect to differnt  quantile of the conditional BMI distribution.
+Moreover, modeling age as quadratic term or as spline basis expansion produce different effect with respect to different  quantiles of the conditional BMI distribution.
 
@@
 
-Next, we will investigate marginal effect of TC on four different quntiles of the conditional distribution of the BMI. 
-The quadratic effect of total cholesterol on the conditional distribution of BMI is convex.
-At the lower tail, the correlation is positive that is as cholesterol increases the BMI increases.
-decreasing glucose level by somewhat around 1.4 up to around 180 Cholesterol level.
-However, at higher quantile the association become negative that is as cholesterol level increases the BMI decreases, see  Figure \@ref(fig:resu4).
-The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014],[@chang2011].
-They found that there is a positive correlation between the two groups on average.
+Next, we will investigate marginal effect of TC on four different quantiles of the conditional distribution of the BMI. 
+The quadratic effect of total cholesterol on the conditional distribution of BMI is convex in general.
+At the lower tail ($\tau=0.1$), for TC less than 300 mg$\setminus$dl, we have positive association, that is, as TC increases the BMI increase.
+When TC passes this level, spline basis expansion modeling of TC presents negative correlation between TC and BMI while quadratic modeling of TC shows positive correlation.
+
+At the 50th quantile of BMI, the two ways of modeling TC shows almost a same trend through whole TC range.   
+ At higher quantiles $(\tau=75)$, for TC values less than 350, the association is negative that is as TC cholesterol level increases the BMI decreases, for both ways of modeling TC.
+However, the two models differ after TC passes this value.
+The quadratic term force the the TC effect to take convex shape.
+ At a higher quantile $(\tau=90),$  both ways of modeling TC shows BMI take a convex shape, but quadratic way of modeling BMI is more convex than the other.
+When TC passes 380 mg$\setminus$dL, where TC modeled using spline basis expansion, the BMI starts to decreas slow if compared to the quadratic way for modeling BMI,, see  Figure \@ref(fig:resu4).
 
  On the other hand, when we use splines to modeled the total cholesterol, there is a huge difference in the shape of the association expect at the higher quantile there is some similarity.
-At the lower quantile, there is negative correlation between total cholesterol and BMI for total cholesterol in the range less than 160, then the correlation becomes positive for total cholesterol in the range of (170, 250).
-at the 55th quantile, the correlation is positive for low cholesterol level and then becomes almost flat for the rest cholesterol values.
-At a higher quntile, the correlation becomes negative at cholesterol level in the range (160,300), see Figure \@ref(fig:resu1010).
+At the lower quantile, there is negative correlation between total cholesterol and BMI for total cholesterol in the range less than 160.
+Then the correlation becomes positive for total cholesterol in the range of (170, 250).
+At the 55th quantile, the correlation is positive for low cholesterol level and then becomes almost flat for the rest cholesterol values.
 
 ```{r resu1010, out.width = "100%", fig.align = "center", fig.cap = " An illustration of  marginal effects of total cholesterol  on different BMI quantiles.
-The predictors modeled using quadratic terms and splines.", echo = FALSE}
+The predictors modeled using quadratic terms and splines.
+The BMI quantiles $\tau= 0.1, 0.5, 0.75, 0.90$ coressponds to  21.5,  27.9,  32.4, 37.7 BMI units, respectively.
+", echo = FALSE}
 # Created by file exploratory-data-analysis.R

### 2021-08-27 ci_splin.R

@@ -129,7 +129,7 @@ dat_pred=dat_pred_ready(dat,index =2 ,tau =0.9 )
 dat_pred$Cholesterol_Drug_Use=recode(dat_pred$Cholesterol_Drug_Use, "0" = "No", "1" = "Yes" )
 
 # plot for splines on total cholestrol
-fig3=dat_pred %>%filter(Total_chol<375)%>%
+fig3=dat_pred %>%filter(Total_chol<400)%>%
     ggplot(aes(x = Total_chol, y = pred, color = Cholesterol_Drug_Use)) +
     geom_line() +
     #geom_quantile(formula = y ~ bs(x,intercept=FALSE,df=5), quantiles = 0.25)+
@@ -182,7 +182,7 @@ dat_pred=dat_pred_ready(dat,index =4 ,tau =0.9 )
 dat_pred$Cholesterol_Drug_Use=recode(dat_pred$Cholesterol_Drug_Use, "0" = "No", "1" = "Yes" )
 
 # plot for splines on total cholesterol
-fig4=dat_pred %>%filter(Total_chol<375)%>%
+fig4=dat_pred %>%filter(Total_chol<400)%>%
     ggplot(aes(x = Total_chol, y = pred, color = Cholesterol_Drug_Use)) +
     geom_line() +
     #geom_quantile(formula = y ~ bs(x,intercept=FALSE,df=5), quantiles = 0.25)+

### 2021-08-27 ci_splin_marg_effect.R

@@ -17,6 +17,10 @@ dat=readRDS(file = "bmi.data.rds")
 #dat=dat[dat$BMI<28,]
 dat=filter(dat,Cholesterol_Drug_Use!='9')
 #levels(dat$Cholesterol_Drug_Use) <- c('1','2')
+
+# to find xth percentile
+quantile(dat$BMI, probs = c(0.10,0.50,0.75,0.90))
+
 dat$Cholesterol_Drug_Use <- factor(dat$Cholesterol_Drug_Use)
 dat$Age=as.numeric(dat$Age)
 
@@ -236,7 +240,7 @@ dev.off()
 ##### Grid for Total cholesterol
 #
 
-
+dat=dat %>%filter(100<Total_chol&Total_chol <400)
 fit=fit_rq(dat,index=2,tau=0.1)
 fit2=ggpredict(fit,"Total_chol [all]")
 fit=fit_rq(dat,index=4,tau=0.1)
@@ -252,7 +256,7 @@ dat2 <- rbind(
 
 tot_chol01= ggplot(dat2, aes(x = x, y = predicted, group = model, color = model, fill = model)) +
   geom_line() +
-  ylim(c(15,50))+
+  #ylim(c(15,50))+
   geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
   xlab("Total Cholesterol")+
   ylab("BMI")+
@@ -276,7 +280,7 @@ dat2 <- rbind(
 
 tot_chol05= ggplot(dat2, aes(x = x, y = predicted, group = model, color = model, fill = model)) +
   geom_line() +
-  ylim(c(20,50))+
+  #ylim(c(20,50))+
   geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
   xlab("Total Cholesterol")+
   ylab("BMI")+
@@ -300,7 +304,7 @@ dat2 <- rbind(
 
 tot_chol075= ggplot(dat2, aes(x = x, y = predicted, group = model, color = model, fill = model)) +
   geom_line() +
-  ylim(c(20,50))+
+  #ylim(c(20,50))+
   geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
   xlab("Total Cholesterol")+
   ylab("BMI")+
@@ -324,7 +328,7 @@ dat2 <- rbind(
 
[…]

### 2021-08-27 exploratory-data-analysis_JRT.R

@@ -93,7 +93,7 @@ print(bmi.data %>%
 
 dat=data.frame(bmi.data$Age,as.factor(bmi.data$Race),as.factor(bmi.data$Gender),as.factor(bmi.data$Cholesterol_Drug_Use),bmi.data$BMI,bmi.data$Type_glu)
 colnames(dat) <- c("Age","Race","Gender","Drug_Use","BMI","Type_glu")
-dat$Cholesterol_Drug_Use=recode(dat$Cholesterol_Drug_Use, "1" = "Yes", "0" = "No" )
+dat$Drug_Use=recode(dat$Drug_Use, "1" = "Yes", "0" = "No" )
 ggplot(dat, aes(y=BMI  ,x=Age)) +
     geom_point()
 ggplot(dat, aes(Age ,BMI )) +

### 2021-08-30 manuscript/manuscript2.Rmd
update

@@
     - \floatplacement{figure}{H}
-abstract: "Body Mass index plays an important role in predicting cardioviscalr diseases, strokes, diabetes and many others.
+abstract: "Body Mass index plays an important role in predicting cardiovascular  diseases, strokes, diabetes and many others.
 In this article we use quantile regression to study the effects of age, total cholesterol, cholesterol drug use on the conditional distribution of BMI and it is been compared to the result obtained by ordinary least squares approach.
+We study age and total cholesterol effect on the BMI in two different ways: quadratic terms and spline basis expansions.
 The national health and nutrition examination survey (NHANES) data is used in this study.
@@
 Important risk factors associated with CVD are high BMI and abnormal lipid ratio  [@yusuf2004effect;@anderson1991].
-There are some drugs that are used reducce CVD risks by lowering low-density lipoprotein (LDL) like statin.
+There are some drugs that are used reduce CVD risks by lowering low-density lipoprotein (LDL) like statin.
 Statin use  reduces the risk of cardiovascular diseases, even with a population with no CVD risks  [@yusuf2016].
@@
 They found that there is a positive  correlation ($\rho=0.13$) between statin does levels and  BMI levels.
-Additionaly, taking cholesterol drug medication  associates with a high risk of elevating BMI level.
+Additionally, taking cholesterol drug medication  associates with a high risk of elevating BMI level.
 It is been shown that statin users consume 192 additional calories per day which causes gaining a 6 lb to 11 lb.
 in a year.
-Statin users gain 1.3 units in the BMI measure while non-staining users gain 0.4 BMI unit.
+Statin users gain 1.3 units in the BMI measure while non-staining users gain 0.4 $kg/m^2$.
 Moreover, consumption of fat in statin users raised by 14.4%[@sugiyama2014].
@@
   Polynomial regression using the quadratic term of predictors forces the response to take convex or concave shape, see Figure 1.12 [@koenker2005].
-This is because the limit of the response variable $y$, when modeled as a quadratic function of the predictor variable $x$,  approach $\pm\infty$ ( i.e., as $x \rightarrow\pm\infty,$ $y\rightarrow\pm\infty).$ However, when we model the the response variable using a spline basis expansion of the predictor variable the response is not forced to take a specific shape.
+This is because the limit of the response variable $y$, when modeled as a quadratic function of the predictor variable $x$,  approach $\pm\infty$ ( i.e., as $x \rightarrow\pm\infty,$ $y\rightarrow\pm\infty).$ However, when we model the response variable using a spline basis expansion of the predictor variable the response is not forced to take a specific shape.
 In the latter case, different polynomials are constructed for the different regions in the range of predictors that satisfy continuity and smoothness conditions at the knots.
@@
 Moreover, one of the advantages of using QR over OLS is QR is robust for outliers.
-A brief description of qunatile regression is introduced in the following paragraphs.
+A brief description of quantile regression is introduced in the following paragraphs.
 For a continuous random variable $X$, the cumulative distribution function (CDF) is $$F(X)=P(X\leq x),$$ and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\}, $$ where $0<\tau<1$.
@@
 This concept of a family of transformations that can fit together to capture general shapes is called a basis function.
-In this case, our objects are functions: $b_1 (X ), b_2 (X ),\cdots , b_K (X ).$ In a more general way to represent a value of $y=f(X)$ using a peacewise cubic polybomials with a singl knote $c.$
+In this case, our objects are functions: $b_1 (X ), b_2 (X ),\cdots , b_K (X ).$ In a more general way to represent a value of $y=f(X)$ using a peacewise cubic polynomials with a single knot $c.$
 
@@
 The included races are non-Hispanic white, non-Hispanic black, Hispanic, and others.
-The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014],[@chang2011].
+The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014; @chang2011].
 They found that there is a positive correlation between the two groups on average.
@@
  \item Model II: TC enters the model as spline basis expansion, Race, Gender, and cholesterol drug use.
- \item Model III: Age enters the model as a quadratic factor, Race, Gender, and cholesterol drug use.
- \item Model IV: TC enters the model as a quadratic factor, Race, Gender, and cholesterol drug use. 
+ \item Model III: Age enters the model as a quadratic term, Race, Gender, and cholesterol drug use.
+ \item Model IV: TC enters the model as a quadratic term, Race, Gender, and cholesterol drug use. 
  \end{itemize}
@@
 The disparity is almost regular through different BMI quantiles.
-For example, in the lower quantiles of the distribution the cholesterol drug users have higher BMI value by about 1.5 $kg/m^2$, but around at 50 th percentile of the conditional distribution the difference is 1.8 BMI units.
+For example, in the lower quantiles of the distribution the cholesterol drug users have higher BMI value by about 1.5 $kg/m^2$, but around at 50 th percentile of the conditional distribution the difference is 1.8 $kg/m^2$.
 Overall,  cholesterol drug use seems to be associated with rather large effects on BMI levels somewhat between  1 to 2 $kg/m^2$.
 
-```{r resu1, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted  for different marginal effects. The predictors modeled using quadratic terms ", echo = FALSE}
+```{r resu1, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted  for different marginal effects. The predictors modeled using quadratic terms. ", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 
-```{r resu12, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted  for different marginal effects. The predictors modeled using splines ", echo = FALSE}
+```{r resu12, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted  for different marginal effects. The predictors modeled using splines. ", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 
-Figure \@ref(fig:resu1000) illustrate the differences in modeling Age in two different ways (Model I; spline basis expansion) and (Model III; quadratic factor ).  
+\subsection{Age effects Analysis}
+
+Figure \@ref(fig:resu1000) illustrate the differences in modeling Age in two different ways (Model I; spline basis expansion) and (Model III; quadratic term ).  
  Model I shows, at the lower quantile, the marginal age effects on BMI increases from age 20 to around age 42, and then it stays flat up to age 70 but it starts to decrease after that.
@@
  At higher quantiles $\tau=75$, using Model I, the maximum age effects occurs earlier by three years, but Model III shows the highest age effects occurs at around age 50.
-The decay starts at around  .
+The decay, according to Model I, starts at around age 70 years old, but Model III shows the decay starts earlier at around 70 years old.
 Convex behavior of the quadratic term has a clear pattern in formulating age effects on the BMI.
@@
 
-Using Model I, at the 90th quantile of the conditional BMI distribution, we have a similar behavior as in 0.75th quantile except the relationship is stronger, i.e, for example, the age effects at age 20 is 37 $kg/m^2$ while at the later the effect is 30 BMI unit.
+Using Model I, at the 90th quantile of the conditional BMI distribution, we have a similar behavior as in 0.75th quantile except the relationship is stronger, i.e, for example, the age effects at age 20 is 37 $kg/m^2$ while at the later the effect is 30 $kg/m^2$.
 The BMI trend in this modeling is close to the trend shown in [@chen2005], which computed using a complicated polynomial and log transformation for the response.
@@
 
-```{r resu1000, out.width = "100%", fig.align = "center", fig.cap = "  An illustration of  marginal effects of age on different BMI quantiles.
-The predictors modeled using quadratic terms and basis splines expension.", echo = FALSE}
+```{r resu1000, out.width = "100%", fig.align = "center", fig.cap = "  An illustration for the differences in modeling the age effects on different BMI quantiles.
+The predictors (Age) modeled using quadratic terms and basis splines expension.", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 ```
+\subsection{TC effects Analysis}
+Next, we investigate marginal effect of TC on four different quantiles of the conditional distribution of the BMI. 
+The quadratic effect of total cholesterol on the conditional distribution of BMI is convex in general when age is modeled using quadratic term.
+However, age effect on the BMI is different when age is modeled using spline basis expansion.
+The disparity is due to the same reason mentioned earlier, which is as
+TC$\rightarrow\pm\infty,$ BMI$\rightarrow 0).$ At the lower tail ($\tau=0.1$), for TC less than 300 mg$\setminus$dl, we have positive association, that is, when TC increases, the BMI increases also.
+Moreover, when TC passes this level, spline basis expansion modeling of TC presents negative correlation between TC and BMI while quadratic modeling of TC shows positive correlation.
 
-Next, we will investigate marginal effect of TC on four different quantiles of the conditional distribution of the BMI. 
-The quadratic effect of total cholesterol on the conditional distribution of BMI is convex in general.
-At the lower tail ($\tau=0.1$), for TC less than 300 mg$\setminus$dl, we have positive association, that is, as TC increases the BMI increase.
-When TC passes this level, spline basis expansion modeling of TC presents negative correlation between TC and BMI while quadratic modeling of TC shows positive correlation.
-
-At the 50th quantile of BMI, the two ways of modeling TC shows almost a same trend through whole TC range.   
+At the 50th quantile of BMI, the two methods of modeling TC shows almost the same trend through whole TC range.   
  At higher quantiles $(\tau=75)$, for TC values less than 350, the association is negative that is as TC cholesterol level increases the BMI decreases, for both ways of modeling TC.
 However, the two models differ after TC passes this value.
-The quadratic term force the the TC effect to take convex shape.
+The quadratic term force the TC effect to take convex shape.
  At a higher quantile $(\tau=90),$  both ways of modeling TC shows BMI take a convex shape, but quadratic way of modeling BMI is more convex than the other.
-When TC passes 380 mg$\setminus$dL, where TC modeled using spline basis expansion, the BMI starts to decreas slow if compared to the quadratic way for modeling BMI,, see  Figure \@ref(fig:resu4).
+When TC passes 380 mg$\setminus$dL, where TC modeled using spline basis expansion, the BMI starts to decrease slow if compared to the quadratic way for modeling BMI, see  Figure \@ref(fig:resu1010).
 
- On the other hand, when we use splines to modeled the total cholesterol, there is a huge difference in the shape of the association expect at the higher quantile there is some similarity.
+ <!-- On the other hand, when we use splines to modeled the total cholesterol, there is a huge difference in the shape of the association expect at the higher quantile there is some similarity.
 At the lower quantile, there is negative correlation between total cholesterol and BMI for total cholesterol in the range less than 160.
@@
 At the 55th quantile, the correlation is positive for low cholesterol level and then becomes almost flat for the rest cholesterol values.
+-->
+
+ The population with low BMI, it is expected when TC increases (more than 200 mg$\setminus$dL), people start to reduce their BMI.
+However, this trend is captured by using spline basis expansion for the age but it was missed by using quadratic term for the age, see the upper left corner plot in Figure \@ref(fig:resu1010).
+In addition, he$/$she with high BMI reduces their weight to reduce him$/$her TC.
+The quadratic modeling of the TC shows a sharp decrease in the BMI if compared to spline basis expansion.
+This can be seen in the lower right corner of Figure \@ref(fig:resu1010).
+As it was shown in [@mc2020effects] the obese population has higher TC, this trend is not captured by quadratic term modeling for TC.
 
@@
 The predictors modeled using quadratic terms and splines.
-The BMI quantiles $\tau= 0.1, 0.5, 0.75, 0.90$ coressponds to  21.5,  27.9,  32.4, 37.7 BMI units, respectively.
+The BMI quantiles $\tau= 0.1, 0.5, 0.75, 0.90$ coressponds to  21.5,  27.9,  32.4, 37.7 $kg/m^2$, respectively.
 ", echo = FALSE}
@@
 
+\subsection{Analysing Race$\setminus$ Ethinicity effect on BMI}
+
 Figure \@ref(fig:resu3) illustrates age effects on 90th BMI quantile, where age modeled as a quadratic term.
 There is a clear association between age and BMI.
-For example, at early ages for a non cholesterol drug users female Mexican, age effects is around 40 BMI unite, but it decreases later up to 35 at age 80 years.
-The effects of age is higher for cholesterol drug users which is about 2 BMI units.
-Moreover,  male Mexicans have higher BMI than femals by about 2 BMI unites.
+For example, at early ages for a non cholesterol drug users female Mexican, age effects is around 40 $kg/m^2$, but it decreases later up to 35 at age 80 years.
+The effects of age is higher for cholesterol drug users which is about 2 $kg/m^2$.
+Moreover,  male Mexicans have higher age effect on BMI than females by about 2 $kg/m^2$.
 The lowest age effects on 90th BMI quantile is found in the white race.
-Figure \@ref(fig:resu33) prsents age effect
+In general age effect on BMI for males are higher than for females.  Figure \@ref(fig:resu33) presents age effect on BMI through using spline basis expansion. 
 ```{r resu3, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic age effect on 90th BMI quantile for different race ethnacity groups.", echo = FALSE}
@@
 ```
+
+ Figure \@ref(fig:resu4) and Figure \@ref(fig:resu330) present TC effect on BMI by modeling TC as a quadratic term and spline basis expansion, respectively. Male population have higher
 
@@
 \section{Conclusion}
- Multivariate quantile regression is used to study the effects of different risk factors on the BMI levels.
-Cholesterol drug effects on BMI is negligible at low quantile but at higher quantile cholesterol medication  effects on BMI is larger.
-This study showed that the association between BMI and total cholesterol is varying with respect to different quantile.
+ Multivariate quantile regression is used to study the effects of different risk factors on different BMI levels.
+our study shows that different risk factors for higher BMI have different effects on different quantiles.
+Moreover, predictors effect on BMI is subject to the methods used to represent it, which are quadratic modeling spline basis expansion.
+Quadratic term for the response to take a convex shape.
+This is different from spline basis expansions in which different polynomials have been used to model the predictors.
+Our results shows the turning point in the association between age and BMI is 30 years old.
+This is the age when people start to consider reducing weight.
+This trend is shown through the descriptive statistics and QR.
+However, quadratic modeling for the age is not able to detect this trend.
 
- total people who have TC levels around 190 mg/dL have the lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile, the optimal cholesterol level is around 200 mg/dL.
-Moreover,
+ The effects of TC on the BMI is studied with respect to two ways for modeling TC.
+The turning point for patients to start reducing their BMI is when TC hit around 200 mg$\setminus$dL.
+However, if TC hits 350, the association become positive.
+This is a sign where patients are losing their control on their TC  and BMI levels.
 

### 2021-08-30 Q_reg_plot2.R

@@ -42,7 +42,7 @@ p <- dim(fit3)[1]
 blab <- c("Intercept","Male ","RaceMexican", "RaceOther", "RaceOther_Hispanic ", "White ", " Cholesterol_Drug_Use" ,
           "Age1","Age2","Age3","Age4","Age5","TC1","TC2","TC3","TC4","TC5")
 
-par(mfrow=c(6,4))
+par(mfrow=c(6,3))
 for(i in c(1:17)){
   #if(i==1){#adjust intercept to be centercept
   #   Age.bar <- mean(bmi.data$Age)

### 2021-09-17 manuscript/manuscript2.Rmd
Update

@@
 ---
-title: " Quantile Regression Analysis for Statin Effects on Body mass Index"
+title: " Quantile Regression Analysis for Statin Effects on Body Mass Index"
 output:
@@
     - \floatplacement{figure}{H}
-abstract: "Body Mass index plays an important role in predicting cardiovascular  diseases, strokes, diabetes and many others.
-In this article we use quantile regression to study the effects of age, total cholesterol, cholesterol drug use on the conditional distribution of BMI and it is been compared to the result obtained by ordinary least squares approach.
+abstract: " An individuals body mass index (BMI) is an important predictor of a  cardiovascular  diseases, stroke, diabetes and many other medical conditions.
+In this article, we use quantile regression to study the effects of age, total cholesterol, and use of medication on the conditional distribution of BMI and compare these results to those obtained by ordinary least squares.
 We study age and total cholesterol effect on the BMI in two different ways: quadratic terms and spline basis expansions.
@@
 
-  High body mass index (BMI) has a negative impact on public health[@nuttall2015body].
-There is a positive relation between the risk of death from all causes, cardiovascular disease, cancer, or other diseases and BMI for both genders[@calle1999body].
-Due to high cost of obesity, it is crucial to get better understanding of the underlying risk factors for obesity.
-This can help decision makers to create  new recommendations that help to prevent and stop the dramatic increase in BMI.
+  High body mass index (BMI) has a negative impact on an individuals health [@nuttall2015body] because there is a positive relationship between the risk of death from all causes including cardiovascular disease, cancer, or other diseases and BMI for both genders [@calle1999body].
+Due to high cost of obesity on an individuals health, it is crucial to get better understanding of the underlying risk factors for obesity.
+Understanding the causes of obesity can help decision makers  create  new recommendations that help to prevent and stop the dramatic increase in BMI.
 
@@
 Approximately 18 million deaths annually per year world wide are caused by cardiovascular diseases(CVD), and this number is similar to the number of nonfatal cardiovascular events [@hay2017gbd].
-In 2011, annual costs for CVD and stroke were estimated at $\$320.1$ billion, which is more than spending on cancer.
+In 2011, annual costs for CVD and stroke were estimated at $\$320.1$ billion, which is more than what is spent on cancer.
 The total CVD cost includes \$195.6  billion in direct costs (health-care costs) and \$124.5 billion of future productivity loss [@mozaffarian2015executive].
 Important risk factors associated with CVD are high BMI and abnormal lipid ratio  [@yusuf2004effect;@anderson1991].
-There are some drugs that are used reduce CVD risks by lowering low-density lipoprotein (LDL) like statin.
-Statin use  reduces the risk of cardiovascular diseases, even with a population with no CVD risks  [@yusuf2016].
-On the other hand, statin uses associate with negative side effects on health conditions, for example, BMI.
+There are some medications that are used reduce CVD risks by lowering low-density lipoprotein (LDL) including statins.
+Statin use  reduces the risk of cardiovascular diseases, even with a population with no CVD risk factors [@yusuf2016].
+On the other hand, statin uses is associate with negative side effects on health conditions including increased BMI.
 The effect of BMI on the choice of lipid-lowering treatment has been studied by [@ferrieres2018].
-They found that there is a positive  correlation ($\rho=0.13$) between statin does levels and  BMI levels.
-Additionally, taking cholesterol drug medication  associates with a high risk of elevating BMI level.
-It is been shown that statin users consume 192 additional calories per day which causes gaining a 6 lb to 11 lb.
-in a year.
-Statin users gain 1.3 units in the BMI measure while non-staining users gain 0.4 $kg/m^2$.
-Moreover, consumption of fat in statin users raised by 14.4%[@sugiyama2014].
-This study gives us insight about the association between cholesterol drug uses and condition means of the BMI.
+Where they found that there is a positive  correlation ($\rho=0.13$) between statin does levels and  BMI levels.
+Additionally, it is been shown that statin users consume on average 192 additional calories per day which causes gaining on average  a 6 to 11 lbs in a year.
+Statin users gain on average 1.3 units in the BMI measure while non-staining users gain on average 0.4 $kg/m^2$.
+Moreover, consumption of fat in statin users raised on average by 14.4%[@sugiyama2014].
+This study gives us insight about the association between cholesterol medication uses and conditional means of the BMI.
 
-An important question to ask is, are there  an associations between cholesterol drug uses and different BMI quantiles?
-This question helps us to understand cholesterol drug uses effect on the  obese, overweight population, so that a decision maker take an optimal action about treatment policy.
+An important question to ask is, are there  an associations between cholesterol medication uses and different BMI quantiles?
+This question helps us to understand cholesterol medication uses effect on the  obese, overweight population, so that a decision maker take an optimal action about treatment policy.
 
   Ordinary least squares (OLS) regression helps us to study the effects of predictors on the mean of the response.
-For example, estimating the association of different factors like a lipid-lowering drug with the conditional mean of BMI [@ferrieres2018].
-OLS approaches does not give us insight into the predictor's effects on different quantiles of the responses.
-  However, quantile regression (QR) is used to investigate the heterogeneity in the association of the $\tau$th quantile $0<\tau<1$ of BMI with a set of independent predictors to investigate the effects of a specific predictors on the various quantiles of the BMI.
-Estimation of underweight and overweight regressed on age could be hard because of the trend change and nonlinearity behavior of the BMI with respect to age, as it is shown in [@flegal1999].
+For example, OLS is used to estimate the conditional mean of BMI given different factors like a lipid-lowering medications [@ferrieres2018].
+However, OLS approaches does not give us insight into the predictor's effects on different quantiles of the responses.
+  Instead, quantile regression (QR) is used to investigate the conditional relationship heterogeneity of the $\tau$th quantile $0<\tau<1$ of BMI given with a set of independent predictors.
+  <!-- to investigate the effects of a specific predictors on the various quantiles of the BMI. -->
+
   <!-- BMI departs normality because of the skewness on the right and left tails. -->
-  Therefore, QR is an appropriate method used to estimate the differences in the  association of the BMI with predictors.
 
@@
 
+Estimating the average age effects on BMI could be hard because the age effects is varying with respect to BMI levels.
+In addition, it is been found that the  BMI behaves nonlinear with respect to age [@flegal1999].
+ <!-- Therefore, QR is an appropriate method used to estimate the differences in the  association of the BMI with predictors.  -->
    We compare two approaches to study the QR of BMI regressed on age and total cholesterol (TC) levels.
-One approach is called quantile polynomial regression.
-It is defined as a way to model the non-relationship between predictors and distribution of the  response as an $n$th degree polynomial in the predictors.
+One approach is to model the conditional distribution of the BMI as a polynomial function of the age, which is called quantile polynomial regression.A quantile polynomial regression is defined as a way to model the non-linear relationship between predictors and distribution of the  response as an $n$th degree polynomial in the predictors.
 And the other approach is using a spline basis expansion of the predictors.
@@
 Also, QR is a valuable tool to study association between predictors and response when we have a week or no-relationships between predictors and the conditional mean of the response.
-Moreover, one of the advantages of using QR over OLS is QR is robust for outliers.
+Moreover, one of the advantages of using QR over OLS is QR is robust to outliers.
 A brief description of quantile regression is introduced in the following paragraphs.
-For a continuous random variable $X$, the cumulative distribution function (CDF) is $$F(X)=P(X\leq x),$$ and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\}, $$ where $0<\tau<1$.
-Let the loss function of interest be defined by $$\rho_{\tau}(u)= u(\tau-I_{(u<0)}),$$ where $I$ is the indicator function  [@koenker2005].
+For a continuous random variable $X$, we denote by $x$ for an instances of $X$, the cumulative distribution function (CDF) is $$F(X)=P(X\leq x),$$ and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\}, $$ where $0<\tau<1$.
+Let the loss function of interest be defined by $$\rho_{\tau}(u)= u(\tau-I_{(u<0)}),$$ where $I_{\cdots}$ is the indicator function  [@koenker2005].
 The quantile estimator is the value that minimizes the expected loss function
@@
 OLS method expresses the conditional mean of $y$ given $x$ as $\mu(x)=x^T\beta$ and it solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.$$ 
-The above equation represent the loss function for the OLS regression.By solving this equation for the minimum values for $\beta,$ we get regression equation, which is $\hat{y}=x_i^T\beta$.
+The above equation represent a function of the loss for the OLS regression. By solving this equation for $\beta,$ we get the estimated  regression equation  $\hat{y}=x_i^T\beta$.
 On the other hand, QR expresses the conditional quantile function $Q_y(\tau|x)=x^T \beta ({\tau)}$ and solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.$$
-The above This minimization problem can be reformulated to a linear programming problem and it can be solved using standard statistical software.
+The above minimization problem can be reformulated to a linear programming problem and it can be solved using standard statistical software.
 
@@
 
-\section{Splines Verses Polynomials}
-    Most of the relations between the responses and predictors variables are complicated to the point that linear regressions are not suitable to model these relationships[@bruce2020].
-For example, the response to different levels of drug doses is not a linear relationship.
-Linear regressions can be generalized to deal with nonlinear effects.
+\section{Accounting for a Nonlinear Functional Response}
+    Most of the relationships between the responses and predictors variables are nonlinear so that linear regressions are not suitable to model these relationships [@bruce2020].
+For example, the response to different levels of medication doses is not a linear relationship.
+Linear regressions can be generalized to deal with nonlinear responses in a variety of ways.
 One approach is through including polynomial terms in the regression equation.
-A continuous predictor can be modeled as a linear, say $x$, or nonlinear term, say $x^2$ depending on the relationship with the response variable.
+A continuous predictor can be modeled as a linear term (i.e.,$x$) or nonlinear term (i.e., $x^2$) depending on the relationship with the response variable.
     The mathematical model for $n$ degree polynomial regression is shown in the Eq\eqref{non}
  \begin{equation}\label{non}
- y=\beta_0+\beta_1 X+\beta_2 X^2+\cdots+\beta_nX^n.
+ y=\beta_0+\beta_1 x+\beta_2 x^2+\cdots+\beta_n x^n+\epsilon.
  \end{equation}
@@
  One of the limitations of using polynomial regression is the curvature that can be captured is limited with low order terms.
-However, including higher-order terms has a negative impact on the model by introducing undesirable "wiggliness" in the regression equation especially near the boundaries of the data.
-Another robust approach to model nonlinear relationships is splines.
-It is similar to a technique used by draftsmen in plotting curves.
- The spline is a process of constructing a set of piece-wise continuous polynomials that are smoothly connected at a set of points in the range of the predictor variable.
-The connection points are called knots i.e.
-splines are used to smoothly interpolate between certain points.
-Let $a,b$ ,and $c$ are the endpoints of the $x-$axis intervals.
- A transformation for some or all of predictors is needed to capture the nonlinearity in the model.
+However, including higher-order terms has a negative impact on the model by introducing undesirable "wiggliness" in the regression equation, especially near the boundaries of the data.
+Another robust approach to model nonlinear relationships is splines, which is similar to a technique used by draftsmen in plotting curves.
+ The spline is a process of constructing a set of piece-wise continuous polynomials that are smoothly connected at a set of points called knots in the range of the predictor variable and are used to smoothly interpolate between points.
 The family of transformation of the predictors that can be fit together to built the model's shape is known as a basis function.
@@
 \section{Methods}
-A multivariate quantile regression model is used to assess the characteristics of the association variability in different quantiles of the conditional distribution of the body mass index.
+A multivariate quantile regression model is used to assess the characteristics of the association variability in different quantiles of the conditional distribution of the BMI.
 
- The independent variables in our model are gender, race, age, total cholesterol and cholesterol drug use (yes or no).
-All types of cholesterol drugs are used including statins.
-The included races are non-Hispanic white, non-Hispanic black, Hispanic, and others.
-The relation between total cholesterol and fasting glucose has been studied in [@tsaousis2014; @chang2011].
-They found that there is a positive correlation between the two groups on average.
-Therefore, fasting glucose level is not included to avoid collinearity.
+ The independent variables in our model are gender, race, age, total cholesterol and cholesterol medication(yes or no).
+The "yes" response for the variable "cholesterol medication" refers to using any types of cholesterol medication including statin.
+The included races/ethnicity are non-Hispanic white, non-Hispanic black, Hispanic, and others.
+The relation between total cholesterol and fasting glucose was been studied in [@tsaousis2014; @chang2011].
+They found that there is a positive correlation between total cholesterol and fasting glucose on average.
+Therefore, fasting glucose level is not included in our analysis to avoid collinearity.
 The following formulas represents the different QR models that fit conditional distribution of BMI on :
@@
  \begin{itemize}
- \item Model I: Age enters the model as spline basis expansion, Race, Gender, and cholesterol drug use (Yes or No).
- \item Model II: TC enters the model as spline basis expansion, Race, Gender, and cholesterol drug use.
- \item Model III: Age enters the model as a quadratic term, Race, Gender, and cholesterol drug use.
- \item Model IV: TC enters the model as a quadratic term, Race, Gender, and cholesterol drug use. 
+ \item Model I: \textit{Age enters the model as a quadratic term, Race, Gender, and cholesterol medication use.}
+ \item Model II:\textit{TC enters the model as a quadratic term, Race, Gender, and cholesterol medication use.}
+ \item Model III:\textit{Age enters the model as spline basis expansion, Race, Gender, and cholesterol medication use (Yes or No).}
+ \item Model IV: \textit{TC enters the model as spline basis expansion, Race, Gender, and cholesterol medication use.}
  \end{itemize}
@@
 \subsection{Data}
- The data used in this study is the National Health and Nutrition Examination Survey data (NHANES)[@NHANES].
+ The data used in this study is from the National Health and Nutrition Examination Survey (NHANES, @NHANES).
 The survey examines a nationally representative sample of the U.S.
@@
 and the other contains data that are related to body measurements, such as BMI, head circumference, etc.
-These files are merged by using the respondent sequence number (SEQN) resulting in a around 12,000 records.
-The missing values are deleted.
-We selected a population age between 20 and 80.
+These files are merged by using the respondent sequence number (SEQN), resulting in  around 12,000 records after missing values are deleted.
+We selected an adult population aged between 20 and 80.
+On average, adults female population  have higher  BMI.
+The race/ethnicity variables denotes for Mexican American, Other Hispanic, Non-Hispanic White, Non-Hispanic Black, and Other Race - Including Multi-Racial.
  BMI are classified into different categories according to underweight, 18.5 $kg/m^2$; normal weight, 18.5 to 25 $kg/m^2$; overweight, 25 to 30 $kg/m^2$; obese, 30 to 35 $kg/m^2$; and very obese more than 35 $kg/m^2$.
 
-| Syntax      | Male  | Female     |
+|       | Male  | Female     |
 | :---        |    :----:   |          ---: |
@@
 | Mean of Age | 49.9       | 49.73   |
-| BMI        |  28.549    |  29.379  |
-| TC         |        |    |
+|  Mean of BMI        |  28.549    |  29.379  |
+| Mean of TC         |  189.641      |  195.977  |
 | Statin use (ratio) | 0.198       | 0.181   |
@@
 ```{r box, out.width = "100%", fig.align = "center", fig.cap = "Illustration of data distribution using a box plot.
-The plot compares cholesterol drug users vs non-cholesterol drug users", echo = FALSE}
+The plot compares cholesterol medicated users vs non-cholesterol medicated users", echo = FALSE}
 # Created by file exploratory-data-analysis.R
@@
 
-Figure \@ref(fig:box) shows the association between age and BMI with respect to cholesterol drug changes based on age.
-At the younger ages, the correlation is positive while at the middle age the correlation is almost flat, and at the old age the correlation is negative.
-Moreover, at low age cholesterol medications are  described only for a population with high BMI, but at a higher age, the difference in term of the BMI for a population that takes cholesterol medication and without cholesterol medication decreases until it diminishes as in the white population.
-The  heterogeneity can also be seen in gender ?, for the Hispanic female population, the cholesterol medication is taken by the population with lower BMI if compared to the population that does not take cholesterol medication.
+Figure \@ref(fig:box) shows how the association between age and BMI given cholesterol medication use changes based on age.
+At younger ages, the average BMI for black population increases as a function of age up to around age 30 years.
+For ages more than 40 years, the association becomes negative.
+This observation suggests that at around 30 year old people start to take care of their weights.
+Mexican Females  do not show significant reduction in the BMI as a function of age.
+For White Males, the association is flat at the middle ages and negative at older ages.
+Moreover, at lower ages, cholesterol medications are  prescribed only for a population with high varying BMI, but at  older ages, the difference in BMI given cholesterol medication status decreases until it diminishes as in the white population.
+The  heterogeneity can also be seen in gender, for the Hispanic female population, the cholesterol medication is taken by the population with lower BMI if compared to the population that does not take cholesterol medication.
 
@@
 
-From the OLS it is obvious cholesterol drug users have on average higher BMI levels if compared to non-cholesterol drug users which are around 1.75.
-The disparity is almost regular through different BMI quantiles.
-For example, in the lower quantiles of the distribution the cholesterol drug users have higher BMI value by about 1.5 $kg/m^2$, but around at 50 th percentile of the conditional distribution the difference is 1.8 $kg/m^2$.
-Overall,  cholesterol drug use seems to be associated with rather large effects on BMI levels somewhat between  1 to 2 $kg/m^2$.
+From the OLS it is obvious cholesterol medication users have on average higher BMI levels if compared to non-cholesterol medicated users which are around 1.75.
+The disparity is almost consistent throughout different BMI quantiles.
+For example, in the lower quantiles of the distribution the cholesterol medicated users have higher BMI value by about 1.5 $kg/m^2$ on average, but around at 50 th percentile of the conditional distribution the difference is on average 1.8 $kg/m^2$.
+Overall,  cholesterol medication use seems to be associated with rather large effects on BMI levels somewhat between  1 to 2 $kg/m^2$ on average.
 
@@
 
-Figure \@ref(fig:resu1000) illustrate the differences in modeling Age in two different ways (Model I; spline basis expansion) and (Model III; quadratic term ).  
- Model I shows, at the lower quantile, the marginal age effects on BMI increases from age 20 to around age 42, and then it stays flat up to age 70 but it starts to decrease after that.
-While model III shows that there is positive relationship between Age and BMI in the age range between 20 and 50.
+Figure \@ref(fig:resu1000) illustrate the differences in modeling age in two different ways (Model III; spline basis expansion) and (Model I; quadratic term ).  
+ Model III shows, at the lower quantile, the marginal age effects on BMI increases from age 20 to around age 42, and then it stays flat up to age 70 but it starts to decrease after that.
+While model I shows that there is positive relationship between Age and BMI in the age range between 20 and 50.
 Then age effects stay flat in the age range between 50 and 60 years old and decreases after that.
 
- At the 50th quantile, model I shows the highest age effect on BMI occurs earlier by 10 years when compares to the lower quantile, but model III shows maximum effect occurs at around age 50, which is similar to the age effect at lower quantiles.
-The age effects start to decrease using Model I at around 70 years old while model III shows the decay starts at  around age 60.
- At higher quantiles $\tau=75$, using Model I, the maximum age effects occurs earlier by three years, but Model III shows the highest age effects occurs at around age 50.
-The decay, according to Model I, starts at around age 70 years old, but Model III shows the decay starts earlier at around 70 years old.
+ At the 50th quantile, model III shows the highest age effect on BMI occurs earlier by 10 years when compares to the lower quantile, but model I shows maximum effect occurs at around age 50, which is similar to the age effect at lower quantiles.
+The age effects start to decrease using Model III at around 70 years old while model I shows the decay starts at  around age 60.
+ At higher quantiles ($\tau=75$) Model III shows the maximum age effects occurs at age around 32 years old, which is  earlier than the age at which the peak coccurs in  by three years than , but Model I shows the highest age effects occurs at around age 50.
+The decay, according to Model III, starts at around age 70 years old, but Model I shows the decay starts earlier at around 70 years old.
 Convex behavior of the quadratic term has a clear pattern in formulating age effects on the BMI.
 The box plot (Fig.
-\@ref(fig:box))   supports Model I results because the highest mean and inter quantile range occurs at age 30.
+\@ref(fig:box))   supports Model III results because the highest mean and inter quantile range occurs at age 30.
 
-Using Model I, at the 90th quantile of the conditional BMI distribution, we have a similar behavior as in 0.75th quantile except the relationship is stronger, i.e, for example, the age effects at age 20 is 37 $kg/m^2$ while at the later the effect is 30 $kg/m^2$.
+Using Model III, at the 90th quantile of the conditional BMI distribution, we have a similar behavior as in 0.75th quantile except the relationship is stronger, i.e, for example, the age effects at age 20 is 37 $kg/m^2$ while at the later the effect is 30 $kg/m^2$.
 The BMI trend in this modeling is close to the trend shown in [@chen2005], which computed using a complicated polynomial and log transformation for the response.
@@
 \subsection{TC effects Analysis}
-Next, we investigate marginal effect of TC on four different quantiles of the conditional distribution of the BMI. 
-The quadratic effect of total cholesterol on the conditional distribution of BMI is convex in general when age is modeled using quadratic term.
-However, age effect on the BMI is different when age is modeled using spline basis expansion.
+Figure \@ref(fig:resu1010) presents the marginal effect of TC for four different quantiles of the conditional distribution of the BMI. 
+The quadratic effect of total cholesterol on the conditional distribution of BMI is required to be convex when age is modeled using quadratic term.
+However, TC effect on the BMI is different when TC is modeled using spline basis expansion.
 The disparity is due to the same reason mentioned earlier, which is as
-TC$\rightarrow\pm\infty,$ BMI$\rightarrow 0).$ At the lower tail ($\tau=0.1$), for TC less than 300 mg$\setminus$dl, we have positive association, that is, when TC increases, the BMI increases also.
-Moreover, when TC passes this level, spline basis expansion modeling of TC presents negative correlation between TC and BMI while quadratic modeling of TC shows positive correlation.
+TC$\rightarrow\pm\infty,$ BMI$\rightarrow \pm\infty).$ At the lower tail ($\tau=0.1$), for TC less than 300 mg$\setminus$dl, we have positive association, that is, when TC increases, the BMI increases also, on average.
+Moreover, when TC passes 300 mg$\setminus$dl level, spline basis expansion modeling of TC presents negative correlation between TC and BMI while quadratic modeling of TC shows positive correlation.
+In addition, the confidence interval (CI) for quadratic modeling of age is larger than the CI for spline basis expansion modeling for the age.
+The CI for quadratic modeling of the age indicate poor fitting while spline basis expansion perform better.
 
 At the 50th quantile of BMI, the two methods of modeling TC shows almost the same trend through whole TC range.   
- At higher quantiles $(\tau=75)$, for TC values less than 350, the association is negative that is as TC cholesterol level increases the BMI decreases, for both ways of modeling TC.
-However, the two models differ after TC passes this value.
-The quadratic term force the TC effect to take convex shape.
- At a higher quantile $(\tau=90),$  both ways of modeling TC shows BMI take a convex shape, but quadratic way of modeling BMI is more convex than the other.
-When TC passes 380 mg$\setminus$dL, where TC modeled using spline basis expansion, the BMI starts to decrease slow if compared to the quadratic way for modeling BMI, see  Figure \@ref(fig:resu1010).
+ At higher quantiles $(\tau=75)$, for TC values less than 350 mg/dL, the association is negative that is as TC cholesterol level increases the BMI decreases, for both functional form for modeling TC.
+However, the two models differ after TC values passes 350 mg/dL because quadratic functional form forces the TC effect to take a convex shape.
+ At a higher quantile $(\tau=90),$  both the models for TC show BMI taking a convex shape, but quadratic way of modeling BMI is more parabolic than the spline model.
+When TC passes 380 mg$\setminus$dL, the TC model using the spline basis expansion shows the BMI starts to decrease more slowly  compared to the quadratic.
 
+ ```{r resu1010, out.width = "100%", fig.align = "center", fig.cap = " An illustration of  marginal effects of total cholesterol  on different BMI quantiles.
+The predictors modeled using quadratic terms and splines.
+The BMI quantiles $\tau=$ 0.1, 0.5, 0.75 and 0.90 coressponds to  21.5,  27.9,  32.4 and 37.7 $kg/m^2$, respectively.
+", echo = FALSE}
+# Created by file exploratory-data-analysis.R
+if (!file.exists(here::here("images", "comp_tot_mixed")))  
+knitr::include_graphics(here::here("images", "comp_tot_mixed.png"))
+```
  <!-- On the other hand, when we use splines to modeled the total cholesterol, there is a huge difference in the shape of the association expect at the higher quantile there is some similarity.
@@
 
- The population with low BMI, it is expected when TC increases (more than 200 mg$\setminus$dL), people start to reduce their BMI.
-However, this trend is captured by using spline basis expansion for the age but it was missed by using quadratic term for the age, see the upper left corner plot in Figure \@ref(fig:resu1010).
-In addition, he$/$she with high BMI reduces their weight to reduce him$/$her TC.
-The quadratic modeling of the TC shows a sharp decrease in the BMI if compared to spline basis expansion.
-This can be seen in the lower right corner of Figure \@ref(fig:resu1010).
-As it was shown in [@mc2020effects] the obese population has higher TC, this trend is not captured by quadratic term modeling for TC.
+ For a population with low BMI, it is expected when TC increases (more than 200 mg$\setminus$dL), individuals start to reduce their BMI, on average.
+However, this trend is captured by using spline basis expansion for the TC but it was missed by using quadratic model for TC ( upper left corner plot in Figure \@ref(fig:resu1010).) In addition, an individual with high BMI reduces their weight to reduce their TC.
+The quadratic modeling of the TC shows a sharp decrease in the BMI when compared to spline basis expansion at $\tau=0.9$ ( lower right corner of Figure \@ref(fig:resu1010).) As it was shown in [@mc2020effects] the obese population has a higher TC and this trend is not captured by quadratic term modeling for TC.
 
-```{r resu1010, out.width = "100%", fig.align = "center", fig.cap = " An illustration of  marginal effects of total cholesterol  on different BMI quantiles.
-The predictors modeled using quadratic terms and splines.
-The BMI quantiles $\tau= 0.1, 0.5, 0.75, 0.90$ coressponds to  21.5,  27.9,  32.4, 37.7 $kg/m^2$, respectively.
-", echo = FALSE}
-# Created by file exploratory-data-analysis.R
-if (!file.exists(here::here("images", "comp_tot_mixed")))  
-knitr::include_graphics(here::here("images", "comp_tot_mixed.png"))
-```
-
-\subsection{Analysing Race$\setminus$ Ethinicity effect on BMI}
+\subsection{Analysing Race/Ethinicity effect on BMI}
 
@@
 There is a clear association between age and BMI.
-For example, at early ages for a non cholesterol drug users female Mexican, age effects is around 40 $kg/m^2$, but it decreases later up to 35 at age 80 years.
-The effects of age is higher for cholesterol drug users which is about 2 $kg/m^2$.
-Moreover,  male Mexicans have higher age effect on BMI than females by about 2 $kg/m^2$.
+In general,  age effects on BMI, considering race ethnicity, behaves at a similar way as the whole population, which is a parabolic shape.
+For example, a young Mexican female not using cholesterol medication has an average BMI around 40 $kg/m^2$, but the BMI values decreases later up to 35 $kg/m^2$ at age 80 years.
+The effects of age is higher for cholesterol medicated users by an average of about about 2 $kg/m^2$.
+Moreover,  Mexican males have a higher average BMI  than females by about 2 $kg/m^2$ at $\tau =0.9$.
 The lowest age effects on 90th BMI quantile is found in the white race.
 In general age effect on BMI for males are higher than for females.  Figure \@ref(fig:resu33) presents age effect on BMI through using spline basis expansion.
+
 ```{r resu3, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic age effect on 90th BMI quantile for different race ethnacity groups.", echo = FALSE}
@@
 
- Figure \@ref(fig:resu4) and Figure \@ref(fig:resu330) present TC effect on BMI by modeling TC as a quadratic term and spline basis expansion, respectively. Male population have higher
+ Figure \@ref(fig:resu4) and Figure \@ref(fig:resu330) present TC effect on BMI with respect to different race/ethnicity groups by modeling TC as a quadratic term and spline basis expansion, respectively.
+Male population have higher
 

### 2021-09-17 ci_splin.R

@@ -93,7 +93,7 @@ dat_pred_ready=function(dat,index,tau){
     message("A")
     pred <- predict(fit, newdata =dat_prediction, interval = "confidence")
     message("B")
-    dat_pred$pred  <- pred[, 1]
+    dat_pred$BMI  <- pred[, 1]
     dat_pred$lower  <- pred[, 2]
     dat_pred$higher <- pred[, 3]
     return(dat_pred)
@@ -107,7 +107,7 @@ dat_pred$Cholesterol_Drug_Use=recode(dat_pred$Cholesterol_Drug_Use, "0" = "No", 
 ###############################################################################4
 
 fig2=dat_pred %>%
-    ggplot(aes(x = Age, y = pred, color = Cholesterol_Drug_Use)) +
+    ggplot(aes(x = Age, y = BMI, color = Cholesterol_Drug_Use)) +
     geom_line() +
     #geom_quantile(formula = y ~ bs(x,intercept=FALSE,df=5), quantiles = 0.25)+
     geom_ribbon(aes(x = Age, ymin = lower, ymax = higher, fill = Cholesterol_Drug_Use), alpha = 0.1) +
@@ -130,7 +130,7 @@ dat_pred$Cholesterol_Drug_Use=recode(dat_pred$Cholesterol_Drug_Use, "0" = "No", 
 
 # plot for splines on total cholestrol
 fig3=dat_pred %>%filter(Total_chol<400)%>%
-    ggplot(aes(x = Total_chol, y = pred, color = Cholesterol_Drug_Use)) +
+    ggplot(aes(x = Total_chol, y = BMI, color = Cholesterol_Drug_Use)) +
     geom_line() +
     #geom_quantile(formula = y ~ bs(x,intercept=FALSE,df=5), quantiles = 0.25)+
     geom_ribbon(aes(x =Total_chol  , ymin = lower, ymax = higher, fill = Cholesterol_Drug_Use), alpha = 0.1) +
@@ -157,7 +157,7 @@ dat_pred$Cholesterol_Drug_Use=recode(dat_pred$Cholesterol_Drug_Use, "0" = "No", 
 
 # plot for splines on total cholestrol
 fig3=dat_pred %>% 
-    ggplot(aes(x = Age, y = pred, color = Cholesterol_Drug_Use)) +
[…]

### 2021-09-17 ci_splin_marg_effect.R

@@ -109,8 +109,9 @@ dat1 <- rbind(
  tot1= ggplot(dat1, aes(x = x, y = predicted, group = model, color = model, fill = model)) +
     geom_line() +
     geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
+   facet_grid(Race~Gender)+
     xlab("Age")+
-    ylab("BMI")
+    ylab("BMI") 
  png(file = here::here("images", "comp_age.png"),
      res = 400, height = 9, width = 16, units = "in")
   print(tot1) 
@@ -135,6 +136,7 @@ dat1 <- rbind(
  tot01= ggplot(dat1, aes(x = x, y = predicted, group = model, color = model, fill = model)) +
    geom_line() +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
+   theme_bw(base_size = 22)+
    xlab("Age")+
    ylab("BMI")+
    ggtitle("Age effect on BMI 0.1 Quantile ")
@@ -157,6 +159,7 @@ dat1 <- rbind(
  tot05= ggplot(dat1, aes(x = x, y = predicted, group = model, color = model, fill = model)) +
    geom_line() +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
+   theme_bw(base_size = 22)+
    xlab("Age")+
    ylab("BMI")+
    ggtitle("Age effect on BMI 0.5 Quantile ")
@@ -181,6 +184,7 @@ dat1 <- rbind(
  tot075= ggplot(dat1, aes(x = x, y = predicted, group = model, color = model, fill = model)) +
    geom_line() +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
+   theme_bw(base_size = 22)+
    xlab("Age")+
    ylab("BMI")+
    ggtitle("Age effect on BMI 0.75 Quantile ")
@@ -206,6 +210,7 @@ dat1 <- rbind(
    geom_line() +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.1)+
    xlab("Age")+
+   theme_bw(base_size = 22)+
    ylab("BMI")+
    ggtitle("Age effect on BMI 0.9 Quantile ")
  
[…]

### 2021-09-17 exploratory-data-analysis_JRT.R

@@ -8,7 +8,7 @@ library(dplyr)
 library(tidyverse)
 library(quantreg)
 library(splines)
-
+library(MASS)
 
 bmi.data<- read.csv(here::here("data", "ldl2.csv"),header=TRUE, sep=",")
 
@@ -92,8 +92,8 @@ print(bmi.data %>%
 ########################################################
 
 dat=data.frame(bmi.data$Age,as.factor(bmi.data$Race),as.factor(bmi.data$Gender),as.factor(bmi.data$Cholesterol_Drug_Use),bmi.data$BMI,bmi.data$Type_glu)
-colnames(dat) <- c("Age","Race","Gender","Drug_Use","BMI","Type_glu")
-dat$Drug_Use=recode(dat$Drug_Use, "1" = "Yes", "0" = "No" )
+colnames(dat) <- c("Age","Race","Gender","Chol_Med","BMI","Type_glu")
+dat$Chol_Med=recode(dat$Chol_Med, "1" = "Yes", "0" = "No" )
 ggplot(dat, aes(y=BMI  ,x=Age)) +
     geom_point()
 ggplot(dat, aes(Age ,BMI )) +
@@ -118,7 +118,7 @@ dat=na.omit(dat)
 png(file = here::here("images", "base_box_plot.png"),
     res = 400, height = 14, width = 20, units = "in")
 
-p<-ggplot(dat, aes(x=Age_10, y=BMI, color=Drug_Use)) +
+p<-ggplot(dat, aes(x=Age_10, y=BMI, color=Chol_Med)) +
     geom_boxplot(notch = FALSE, fill = "lightgray" )+
     stat_summary(fun = mean, geom = "point",
                  shape = 18, size = 2.5, color = "#FC4E07")+
@@ -126,8 +126,8 @@ p<-ggplot(dat, aes(x=Age_10, y=BMI, color=Drug_Use)) +
     xlab("Age Group")+
     ylab("BMI")+
     theme_bw(base_size = 35)+
-    facet_grid(Gender~Race)+
-    labs(title ="  BMI for Colesterol drug users and who are not",subtitle =" ", caption = " NHANES data set")
+    facet_grid(Gender~Race)
+   #+labs(title ="  BMI for Colesterol drug users and who are not",subtitle =" ", caption = " NHANES data set")
 
 print(p)
 dev.off()
[…]

### 2021-09-19 manuscript/manuscript2.tex
Update

@@
 \hypersetup{
-  pdftitle={Quantile Regression Analysis for Statin Effects on Body mass Index},
+  pdftitle={Quantile Regression Analysis for Statin Effects on Body Mass Index},
   pdfkeywords={My keywords},
@@
 
-\title{Quantile Regression Analysis for Statin Effects on Body mass Index}
+\title{Quantile Regression Analysis for Statin Effects on Body Mass Index}
 \author{}
-\date{\vspace{-2.5em}June 09, 2021}
+\date{\vspace{-2.5em}September 17, 2021}
 
@@
 \begin{abstract}
-My abstract
+An individuals body mass index (BMI) is an important predictor of a cardiovascular diseases, stroke, diabetes and many other medical conditions.
+In this article, we use quantile regression to study the effects of age, total cholesterol, and use of medication on the conditional distribution of BMI and compare these results to those obtained by ordinary least squares.
+We study age and total cholesterol effect on the BMI in two different ways: quadratic terms and spline basis expansions.
+The national health and nutrition examination survey (NHANES) data is used in this study.
+The differences between using quadratic terms and spline basis expansion for the predictors is also presented.
 \end{abstract}
@@
 }
+\newpage
 \section{Introduction}
 
-High body mass index (BMI) has a negative impact on public health.
-Due to high cost of obesity, it is crucial to get better understanding of the underlying risk factors for obesity.
-This can help decision makers to create new recommendations that help to prevent and stop the dramatic increase in BMI.
+High body mass index (BMI) has a negative impact on an individuals health (Nuttall 2015) because there is a positive relationship between the risk of death from all causes including cardiovascular disease, cancer, or other diseases and BMI for both genders (Calle et al.
+1999).
+Due to high cost of obesity on an individuals health, it is crucial to get better understanding of the underlying risk factors for obesity.
+Understanding the causes of obesity can help decision makers create new recommendations that help to prevent and stop the dramatic increase in BMI.
 
-BMI plays an important role in predicting heart disease risk(Katzmarzyk et al.
+BMI plays an important role in predicting heart disease risk (Katzmarzyk et al.
 2012).
-Approximately 18 million deaths annually per year world wide are caused by cardiovascular diseases(CVD) , and this number is similar to this number of nonfatal cardiovascular events (Hay et al.
+Approximately 18 million deaths annually per year world wide are caused by cardiovascular diseases(CVD), and this number is similar to the number of nonfatal cardiovascular events (Hay et al.
 2017).
-In 2011, annual costs for CVD and stroke were estimated at \(\$320.1\) billion, which is more than spending on cancer.
+In 2011, annual costs for CVD and stroke were estimated at \(\$320.1\) billion, which is more than what is spent on cancer.
 The total CVD cost includes \$195.6 billion in direct costs (health-care costs) and \$124.5 billion of future productivity loss (Mozaffarian et al.
@@
 Important risk factors associated with CVD are high BMI and abnormal lipid ratio (Yusuf et al.
-2004), (Anderson et al.
+2004; Anderson et al.
 1991).
-There are some drugs the are used reducce CVD risks by lowering low-density lipoprotein (LDL) like statin.
-Statin use reduces the risk of cardiovascular diseases, even with a population with no CVD risks (Yusuf et al.
+There are some medications that are used reduce CVD risks by lowering low-density lipoprotein (LDL) including statins.
+Statin use reduces the risk of cardiovascular diseases, even with a population with no CVD risk factors (Yusuf et al.
 2016).
-On the other hand, statin uses have negative side effects on health conditions, such as elevating glucose levels (Castro et al.
-2016).
+On the other hand, statin uses is associate with negative side effects on health conditions including increased BMI.
 The effect of BMI on the choice of lipid-lowering treatment has been studied by (Ferrières et al.
 2018).
-They found that there is a positive correlation (\(\rho=0.13\)) between statin does levels and BMI levels.
-Additionaly, taking cholesterol drug medication associates with a high risk of elevating BMI level.
-It is been shown that statin users consume 192 additional calories per day which causes gaining a 6 lb to 11 lb.
-in a year.
-Statin users gain 1.3 units in the BMI measure while non-staining users gain 0.4 unit.
-Moreover, consumption of fat in statin users raised by 14.4\%(Sugiyama et al.
+Where they found that there is a positive correlation (\(\rho=0.13\)) between statin does levels and BMI levels.
+Additionally, it is been shown that statin users consume on average 192 additional calories per day which causes gaining on average a 6 to 11 lbs in a year.
+Statin users gain on average 1.3 units in the BMI measure while non-staining users gain on average 0.4 \(kg/m^2\).
+Moreover, consumption of fat in statin users raised on average by 14.4\%(Sugiyama et al.
 2014).
-This study gives as insight about the association between cholesterol druge uses and condition means.
-An important question to ask is, are there an associations between cholesterol drug uses and different BMI quantiles?
-This question helps us to understand cholesterol drug uses effect on the obese, overweight population, so that a decision maker take an optimal action about treatment policy.
+This study gives us insight about the association between cholesterol medication uses and conditional means of the BMI.
+
+An important question to ask is, are there an associations between cholesterol medication uses and different BMI quantiles?
+This question helps us to understand cholesterol medication uses effect on the obese, overweight population, so that a decision maker take an optimal action about treatment policy.
 
 Ordinary least squares (OLS) regression helps us to study the effects of predictors on the mean of the response.
-For example, estimating the association of different factors like a lipid-lowering drug with the conditional mean of BMI (Ferrières et al.
+For example, OLS is used to estimate the conditional mean of BMI given different factors like a lipid-lowering medications (Ferrières et al.
 2018).
-OLS approaches does not give us insight into the predictor's effects on different quantiles of the responses.\\
-Hosever, quantile regression (QR) is used to investigate the heterogeneity in the association of the \(\tau\)th.
-quantile \(0<\tau<1\) of BMI with a set of independent predictors to investigate the effects of a specific predictors on the various quantiles of the BMI.
-Estimation of underweight and overweight regressed on age could be hard because of the trend change and nonlinearity behavior of the BMI with respect to age, as it is shown in (Flegal 1999) BMI departs normality because of the skewness on the right and left tails.
-Therefore, QR is an appropriate method used to estimate the differences in the association of the BMI with predictors.
+However, OLS approaches does not give us insight into the predictor's effects on different quantiles of the responses.\\
+Instead, quantile regression (QR) is used to investigate the conditional relationship heterogeneity of the \(\tau\)th quantile \(0<\tau<1\) of BMI given with a set of independent predictors.
 
@@
 
+Estimating the average age effects on BMI could be hard because the age effects is varying with respect to BMI levels.
+In addition, it is been found that the BMI behaves nonlinear with respect to age (Flegal 1999).
+We compare two approaches to study the QR of BMI regressed on age and total cholesterol (TC) levels.
+One approach is to model the conditional distribution of the BMI as a polynomial function of the age, which is called quantile polynomial regression.A quantile polynomial regression is defined as a way to model the non-linear relationship between predictors and distribution of the response as an \(n\)th degree polynomial in the predictors.
+And the other approach is using a spline basis expansion of the predictors.\\
 Polynomial regression using the quadratic term of predictors forces the response to take convex or concave shape, see Figure 1.12 (Koenker 2005).
-This is because the limit of the response variable \(y\), when modeled as a quadratic function of the predictor variable \(x\), approach \(\pm\infty\) ( i.e.,as \(x \rightarrow\pm\infty,\) \(y\rightarrow\pm\infty.\) However, when we model the the reponse variable using a spline basis expansion of the predictor variable the response is not forced to take a specific shape.
-In the latter case, different polynomials are constructed for the different regions in the range of predictors the satisfies continuity and smoothness conditions at the knots.
-We found that spline regressions produce a different estimate than polynomial regressions.
+This is because the limit of the response variable \(y\), when modeled as a quadratic function of the predictor variable \(x\), approach \(\pm\infty\) ( i.e., as \(x \rightarrow\pm\infty,\) \(y\rightarrow\pm\infty).\) However, when we model the response variable using a spline basis expansion of the predictor variable the response is not forced to take a specific shape.
+In the latter case, different polynomials are constructed for the different regions in the range of predictors that satisfy continuity and smoothness conditions at the knots.
+Because of the above issue in the polynomial regression, we found that spline regressions produce a different estimate than polynomial regressions.
 
@@
 
-Quantile regression is a tool used to regress the dependent variable with high variance over the independent variables.
-QR is developed to study the relationships between variables that have week or no-relationships between their means.
-One of the advantages of using QR over OLS is QR is robust for outliers.
-
-For a random variable \(X\), the cumulative distribution function (CDF) is \[F(X)=P(X\leq x),\] and the \(\tau\)th quantile of \(X\) is defined by \[ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} \] where \(0<\tau<1\).
-Let the loss function is defined by \[\rho_{\tau}(u)= u(\tau-I_{(u<0)})\] where \(I\) is the indicator function (Koenker 2005).
+QR is a tool used to regress the dependent variable with high variance over the independent variables.
+QR is developed to study the relationships between predictors and the response when characteristics other than conditional mean of the response are of interest.
+Also, QR is a valuable tool to study association between predictors and response when we have a week or no-relationships between predictors and the conditional mean of the response.
+Moreover, one of the advantages of using QR over OLS is QR is robust to outliers.
+A brief description of quantile regression is introduced in the following paragraphs.
+For a continuous random variable \(X\), we denote by \(x\) for an instances of \(X\), the cumulative distribution function (CDF) is \[F(X)=P(X\leq x),\] and the \(\tau\)th quantile of \(X\) is defined by \[ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\}, \] where \(0<\tau<1\).
+Let the loss function of interest be defined by \[\rho_{\tau}(u)= u(\tau-I_{(u<0)}),\] where \(I_{\cdots}\) is the indicator function (Koenker 2005).
 The quantile estimator is the value that minimizes the expected loss function
@@
 =F(\hat{x})-\tau.\]
-Due to the monotonicity of the cumulative distribution function, any solution that satisfies \(\{x:F(x)=\tau \}\) is a minimizing for the expected loss function.
+Due to the monotonicity of the cumulative distribution function, any solution that satisfies \(\{x:F(x)=\tau \}\) is a minimizer for the expected loss function.
 
-Least square method expresses conditional mean of y given x as \(\mu(x)=x^T\beta\) and it solves \[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.\] Quantile regression expresses conditional quantile function \(Q_y(\tau|x)=x^T \beta ({\tau)}\) and solve \[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.\]This minimization problem can be reformulated to a linear programming problem
+OLS method expresses the conditional mean of \(y\) given \(x\) as \(\mu(x)=x^T\beta\) and it solves \[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.\]
+The above equation represent a function of the loss for the OLS regression. By solving this equation for \(\beta,\) we get the estimated regression equation \(\hat{y}=x_i^T\beta\).
+On the other hand, QR expresses the conditional quantile function \(Q_y(\tau|x)=x^T \beta ({\tau)}\) and solves \[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.\]
+The above minimization problem can be reformulated to a linear programming problem and it can be solved using standard statistical software.
 
-\subsection{Quantile Regression Technique }
+\section{Accounting for a Nonlinear Functional Response}
 
-\subsection{splines}
-
-A continuous predictor can be modeled as linear, say \(X\), or nonlinear term, say \(X^2\) depends on the relationship with the response variable.
-Most of the relations between the responses and predictors variables are complicated to the point that linear regressions are not suitable to model these relationships(Bruce, Bruce, and Gedeck 2020).
-For example, the response to different levels of drug doses is not a linear relationship.
-Linear regressions can be generalized to deal with nonlinear effects.
+Most of the relationships between the responses and predictors variables are nonlinear so that linear regressions are not suitable to model these relationships (Bruce, Bruce, and Gedeck 2020).
+For example, the response to different levels of medication doses is not a linear relationship.
+Linear regressions can be generalized to deal with nonlinear responses in a variety of ways.
 One approach is through including polynomial terms in the regression equation.
-This approach is called Polynomial regression.
+A continuous predictor can be modeled as a linear term (i.e.,\(x\)) or nonlinear term (i.e., \(x^2\)) depending on the relationship with the response variable.
 The mathematical model for \(n\) degree polynomial regression is shown in the Eq\eqref{non}
 \begin{equation}\label{non}
- y=\beta_0+\beta_1 X+\beta_2 X^2+\cdots+\beta_nX^n.
+ y=\beta_0+\beta_1 x+\beta_2 x^2+\cdots+\beta_n x^n+\epsilon.
  \end{equation}
@@
 One of the limitations of using polynomial regression is the curvature that can be captured is limited with low order terms.
-However, including higher-order terms has a negative impact on the model by introducing undesirable ``wiggliness'' in the regression equation.
-Another robust approach to model nonlinear relationships is splines.
-It is similar to a technique used by draftsmen in plotting curves.
-The spline is a process of constructing a set of piece-wise continuous
-polynomials that are smoothly connected at a set of points in the range of the predictor variable.
-The connection points are called knots i.e.~splines are used to smoothly interpolate between certain points.
-Let \(a,b\) ,and \(c\) are the endpoints of the \(x-\)axis intervals.
-A transformation for some or all of predictors is needed to capture the nonlinearity in the model.
+However, including higher-order terms has a negative impact on the model by introducing undesirable ``wiggliness'' in the regression equation, especially near the boundaries of the data.
+Another robust approach to model nonlinear relationships is splines, which is similar to a technique used by draftsmen in plotting curves.
+The spline is a process of constructing a set of piece-wise continuous polynomials that are smoothly connected at a set of points called knots in the range of the predictor variable and are used to smoothly interpolate between points.
 The family of transformation of the predictors that can be fit together to built the model's shape is known as a basis function.
@@
 This concept of a family of transformations that can fit together to capture general shapes is called a basis function.
-In this case, our objects are functions: \(b_1 (X ), b_2 (X ),\cdots , b_K (X ).\) In a more general way to represent a value of \(y=f(X)\) using a peacewise cubic polybomials with a singl knote \(c.\)
+In this case, our objects are functions: \(b_1 (X ), b_2 (X ),\cdots , b_K (X ).\) In a more general way to represent a value of \(y=f(X)\) using a peacewise cubic polynomials with a single knot \(c.\)
 
-\begin{equation}
-y_{i}=
- \left\{
-\begin{array}{ll}
- \beta_{01}+\beta_{11}x_i+\beta_{21}x_i^2+ \beta_{31}x_i^3+ \epsilon_i & \mbox{if } x_i< c \\
- \beta_{02}+\beta_{12}x_i+\beta_{22}x_i^2+ \beta_{23}x_i^3+ \epsilon_i& \mbox{if } x_i \geq c
-\end{array}
-\right.
-\end{equation}
 Imposing a continuity condition and first, and second derivative at \(c\) are equal in the two sides, we get a cubic splines.
@@
 
-A multivariate quantile regression model is used to assess the characteristics of the association variability in different quantiles of the conditional distribution of the body mass index.
+A multivariate quantile regression model is used to assess the characteristics of the association variability in different quantiles of the conditional distribution of the BMI.
 
-The independent variables in our model are gender, race, age, total cholesterol, cholesterol drug use (yes or no).
-All types of cholesterol drugs are used including statins.
-The included races are non-Hispanic white, non-Hispanic black, Hispanic, or other.
-The following formulas represents the different model that presented in the result.
+The independent variables in our model are gender, race, age, total cholesterol and cholesterol medication(yes or no).
+The ``yes'' response for the variable ``cholesterol medication'' refers to using any types of cholesterol medication including statin.
+The included races/ethnicity are non-Hispanic white, non-Hispanic black, Hispanic, and others.
+The relation between total cholesterol and fasting glucose was been studied in (Tsaousis 2014; Chang et al.
+2011).
+They found that there is a positive correlation between total cholesterol and fasting glucose on average.
+Therefore, fasting glucose level is not included in our analysis to avoid collinearity.
+The following formulas represents the different QR models that fit conditional distribution of BMI on :
 
-\begin{equation}
- \hat{BMI}= bs(Age, df = 5) + Race + Gender + Cholesterol Drug Use
- \end{equation}
-
-\begin{equation}
- \hat{BMI}= bs(Total chol, df=5)+ Race + Gender + Cholesterol Drug Use
- \end{equation}
-
-\begin{equation}
- \hat{BMI}= Age+Age^2+ Race + Gender + Cholesterol Drug Use 
- \end{equation}
-
-\begin{equation}
- \hat{BMI}= Total chol+ Total chol^2+ Race + Gender + Cholesterol Drug_Use
- \end{equation}
+\begin{itemize}
+ \item Model I: \textit{Age enters the model as a quadratic term, Race, Gender, and cholesterol medication use.}
+ \item Model II:\textit{TC enters the model as a quadratic term, Race, Gender, and cholesterol medication use.}
+ \item Model III:\textit{Age enters the model as spline basis expansion, Race, Gender, and cholesterol medication use (Yes or No).}
+ \item Model IV: \textit{TC enters the model as spline basis expansion, Race, Gender, and cholesterol medication use.}
+ \end{itemize}
 
@@
 
-The data used in this study is the National Health and Nutrition Examination Survey data (NHANES)(Disease Control and (CDC) 2018).
+The data used in this study is from the National Health and Nutrition Examination Survey (NHANES, Disease Control and (CDC) (2018)).
 The survey examines a nationally representative sample of the U.S.
-population.
-It focuses on a variety of health and nutrition measurements.
-The survey data are released every two years cycle.
+population focusing on a variety of health and nutrition measurements released in two year cycle.
 In this study, we accumulated 6 cycles of NHANES data (2007--2018).
-We used two data files: One contains demographic variables, such as age, sex, race, income, etc., and the other contains data that are related to body measurements, such as BMI, head circumference, etc.
-These files are merged by using the respondent sequence number (SEQN)
-There are around 12,000 records. We selected a population age between 20 and 80.
-BMI are classified into different categories according to underweight, 18.5 kg/m2; normal weight, 18.5 to 25 kg/m2; overweight, 25 to 30 kg/m2; obese, 30 to 35 kg/m2; and very obese more than 35 kg/m2.
+We used two data files: One contains demographic variables, such as age, sex, race, income, etc.
+and the other contains data that are related to body measurements, such as BMI, head circumference, etc.
+These files are merged by using the respondent sequence number (SEQN), resulting in around 12,000 records after missing values are deleted.
+We selected an adult population aged between 20 and 80.
+On average, adults female population have higher BMI.
+The race/ethnicity variables denotes for Mexican American, Other Hispanic, Non-Hispanic White, Non-Hispanic Black, and Other Race - Including Multi-Racial.
+BMI are classified into different categories according to underweight, 18.5 \(kg/m^2\); normal weight, 18.5 to 25 \(kg/m^2\); overweight, 25 to 30 \(kg/m^2\); obese, 30 to 35 \(kg/m^2\); and very obese more than 35 \(kg/m^2\).
 
@@
 \toprule
-Syntax & Male & Female\tabularnewline
+& Male & Female\tabularnewline
 \midrule
@@
 Mean of Age & 49.9 & 49.73\tabularnewline
-BMI & 28.549 & 29.379\tabularnewline
-TC & &\tabularnewline
+Mean of BMI & 28.549 & 29.379\tabularnewline
+Mean of TC & 189.641 & 195.977\tabularnewline
 Statin use (ratio) & 0.198 & 0.181\tabularnewline
@@
 
-\caption{Illustration of data distribution using a box plot. The plot compares cholesterol drug users vs non-cholesterol drug users}\label{fig:box}
+\caption{Illustration of data distribution using a box plot. The plot compares cholesterol medicated users vs non-cholesterol medicated users}\label{fig:box}
 \end{figure}
 
-Figure \ref{fig:box} shows the association between age and BMI with respect to cholesterol drug is inconsistent.
-At the early age, the correlation is positive while at the middle age the correlation is almost flat, and at the old age the correlation is negative.
-Moreover, at low age cholesterol medications are described only for a population with high BMI, but at a higher age, the difference in term of the BMI for a population that takes cholesterol medication and without cholesterol medication decreases until it diminishes as in the white population.
-The heterogeneity can also be seen in gender ?, for the Hispanic female population, the cholesterol medication is taken by the population with lower BMI if compared to the population that does not take cholesterol medication.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{/home/mabdulsa/BMI/images/exploratory}
-
-}
-
-\caption{A better figure caption}\label{fig:data}
-\end{figure}
+Figure \ref{fig:box} shows how the association between age and BMI given cholesterol medication use changes based on age.
+At younger ages, the average BMI for black population increases as a function of age up to around age 30 years.
+For ages more than 40 years, the association becomes negative.
+This observation suggests that at around 30 year old people start to take care of their weights.
+Mexican Females do not show significant reduction in the BMI as a function of age.
+For White Males, the association is flat at the middle ages and negative at older ages.
+Moreover, at lower ages, cholesterol medications are prescribed only for a population with high varying BMI, but at older ages, the difference in BMI given cholesterol medication status decreases until it diminishes as in the white population.
+The heterogeneity can also be seen in gender, for the Hispanic female population, the cholesterol medication is taken by the population with lower BMI if compared to the population that does not take cholesterol medication.
 
@@
 
-The resulting estimate of effects on conditional mean of BMI level may not reflect the size and nature of these effects on lower or upper quantile.
-For example, in Figure \ref{fig:resu1}, the conditional mean effect of gender on BMI level is about -1, that is on average male's BMI is less than a female's BMI by one unit.
-However, the disparity of the gender effects on lower tails is much larger which is about 1, but the disparity is lower for the upper tail of the distribution somewhat around -3 unit.
+Figures \ref{fig:resu1} and \ref{fig:resu12} illustrate marginal effects of predictors on different quantiles, where in the first plot age and total cholesterol entered the model as quadratic terms while in the second plot, spline basis expansion is used to model age and total cholesterol.
+First, we look at the differences in the plot that is due to using OLS vs QR, then we look at the differences due to the using quadratic term to model predictors vs spline basis expansion.
 
-From the OLS it is obvious cholesterol drug users have on average higher BMI levels if compared to non-cholesterol drug users which are around 1.75.
-The disparity in BMI level for cholesterol drug users vs non-cholesterol drug users is almost the same for different Quantiles.
-cholesterol drug use seems to be associated with rather large effects on BMI levels somewhat around 1.5 to 1.7.
+From Figures \ref{fig:resu1}, we can see the effects on conditional mean of BMI level may not reflect the size and nature of these effects on lower or upper quantiles.
+For example, the conditional mean effect of gender on BMI level is about -1 \(kg/m^2\), that is, on average a male BMI is less than female BMI by 1 \(kg/m^2\).
+However, at the lower quantiles males have higher BMI by 1 \(kg/m^2\).
+Then, the differences start to diminish up to 0 at 40th quantile.
+At higher quantiles, a male BMI is less than a female BMI.
+For example, at 60th quantile a male BMI is less than a female BMI by 1 \(kg/m^2\), and it continue to increase up to 3\(kg/m^2\) at 90th quantile.
+
+From the OLS it is obvious cholesterol medication users have on average higher BMI levels if compared to non-cholesterol medicated users which are around 1.75.
+The disparity is almost consistent throughout different BMI quantiles.
+For example, in the lower quantiles of the distribution the cholesterol medicated users have higher BMI value by about 1.5 \(kg/m^2\) on average, but around at 50 th percentile of the conditional distribution the difference is on average 1.8 \(kg/m^2\).
+Overall, cholesterol medication use seems to be associated with rather large effects on BMI levels somewhat between 1 to 2 \(kg/m^2\) on average.
 
@@
 
-\caption{Quantile regression of BMI ploted  for different marginal effects. The predictors modeled using quadratic terms }\label{fig:resu1}
+\caption{Quantile regression of BMI ploted  for different marginal effects. The predictors modeled using quadratic terms. }\label{fig:resu1}
 \end{figure}
@@
 
-\caption{Quantile regression of BMI ploted  for different marginal effects. The predictors modeled using splines }\label{fig:resu12}
+\caption{Quantile regression of BMI ploted  for different marginal effects. The predictors modeled using splines. }\label{fig:resu12}
 \end{figure}
 
-Age effect modeled as a quadratic factor.
-The age effect is concave in general, see Figure \ref{fig:resu3}.
-At the lower quantile, BMI increases from age 20 to around age 50, and it starts to decrease after that.
-In the 55th quantile, the concavity is stronger at age 50 if compared to the left or right tail.
-The quadratic effect of age is reflected in the hyperbolic shape.
-However, the age effect modeled as b spline behaves in a different way.
-Age effect on BMI increases from age 20 to around age 36 and then start to decrease up to around age 63 then move up again and then decreases up to age 80, see Fig.\ref{fig:resu33}.
-The BMI trend in this modeling is close to the trend shown in (Chen 2005) by using a complicated polynomial and log transformation for the response.
+\subsection{Age effects Analysis}
+
+Figure \ref{fig:resu1000} illustrate the differences in modeling age in two different ways (Model III; spline basis expansion) and (Model I; quadratic term ).\\
+Model III shows, at the lower quantile, the marginal age effects on BMI increases from age 20 to around age 42, and then it stays flat up to age 70 but it starts to decrease after that.
+While model I shows that there is positive relationship between Age and BMI in the age range between 20 and 50.
+Then age effects stay flat in the age range between 50 and 60 years old and decreases after that.
+
+At the 50th quantile, model III shows the highest age effect on BMI occurs earlier by 10 years when compares to the lower quantile, but model I shows maximum effect occurs at around age 50, which is similar to the age effect at lower quantiles.
+The age effects start to decrease using Model III at around 70 years old while model I shows the decay starts at around age 60.\\
+At higher quantiles (\(\tau=75\)) Model III shows the maximum age effects occurs at age around 32 years old, which is earlier than the age at which the peak coccurs in by three years than , but Model I shows the highest age effects occurs at around age 50.
+The decay, according to Model III, starts at around age 70 years old, but Model I shows the decay starts earlier at around 70 years old.
+Convex behavior of the quadratic term has a clear pattern in formulating age effects on the BMI.
+The box plot (Fig.
+\ref{fig:box}) supports Model III results because the highest mean and inter quantile range occurs at age 30.
+
+Using Model III, at the 90th quantile of the conditional BMI distribution, we have a similar behavior as in 0.75th quantile except the relationship is stronger, i.e, for example, the age effects at age 20 is 37 \(kg/m^2\) while at the later the effect is 30 \(kg/m^2\).
+The BMI trend in this modeling is close to the trend shown in (Chen 2005), which computed using a complicated polynomial and log transformation for the response.
+Our conclusion from Figure \ref{fig:resu1000} is that the marginal age effects on BMI is different on different quantiles.
+Moreover, modeling age as quadratic term or as spline basis expansion produce different effect with respect to different quantiles of the conditional BMI distribution.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{/home/mabdulsa/BMI/images/comp_age_mixed}
+
+}
+
+\caption{  An illustration for the differences in modeling the age effects on different BMI quantiles.
+The predictors (Age) modeled using quadratic terms and basis splines expension.}\label{fig:resu1000}
+\end{figure}
+\subsection{TC effects Analysis}
+
+Figure \ref{fig:resu1010} presents the marginal effect of TC for four different quantiles of the conditional distribution of the BMI.
+The quadratic effect of total cholesterol on the conditional distribution of BMI is required to be convex when age is modeled using quadratic term.
+However, TC effect on the BMI is different when TC is modeled using spline basis expansion.
+The disparity is due to the same reason mentioned earlier, which is as
+TC\(\rightarrow\pm\infty,\) BMI\(\rightarrow \pm\infty).\) At the lower tail (\(\tau=0.1\)), for TC less than 300 mg\(\setminus\)dl, we have positive association, that is, when TC increases, the BMI increases also, on average.
+Moreover, when TC passes 300 mg\(\setminus\)dl level, spline basis expansion modeling of TC presents negative correlation between TC and BMI while quadratic modeling of TC shows positive correlation.
+In addition, the confidence interval (CI) for quadratic modeling of age is larger than the CI for spline basis expansion modeling for the age.
+The CI for quadratic modeling of the age indicate poor fitting while spline basis expansion perform better.
+
+At the 50th quantile of BMI, the two methods of modeling TC shows almost the same trend through whole TC range.\\
+At higher quantiles \((\tau=75)\), for TC values less than 350 mg/dL, the association is negative that is as TC cholesterol level increases the BMI decreases, for both functional form for modeling TC.
+However, the two models differ after TC values passes 350 mg/dL because quadratic functional form forces the TC effect to take a convex shape.
+At a higher quantile \((\tau=90),\) both the models for TC show BMI taking a convex shape, but quadratic way of modeling BMI is more parabolic than the spline model.
+When TC passes 380 mg\(\setminus\)dL, the TC model using the spline basis expansion shows the BMI starts to decrease more slowly compared to the quadratic.
+
+\begin{figure}
+
+ {\centering \includegraphics[width=1\linewidth]{/home/mabdulsa/BMI/images/comp_tot_mixed}
+
+ }
+
+ \caption{ An illustration of  marginal effects of total cholesterol  on different BMI quantiles.
+The predictors modeled using quadratic terms and splines.
+The BMI quantiles $ au=$ 0.1, 0.5, 0.75 and 0.90 coressponds to  21.5,  27.9,  32.4 and 37.7 $kg/m^2$, respectively.
+}\label{fig:resu1010}
+ \end{figure}
+
+For a population with low BMI, it is expected when TC increases (more than 200 mg\(\setminus\)dL), individuals start to reduce their BMI, on average.
+However, this trend is captured by using spline basis expansion for the TC but it was missed by using quadratic model for TC ( upper left corner plot in Figure \ref{fig:resu1010}.) In addition, an individual with high BMI reduces their weight to reduce their TC.
+The quadratic modeling of the TC shows a sharp decrease in the BMI when compared to spline basis expansion at \(\tau=0.9\) ( lower right corner of Figure \ref{fig:resu1010}.) As it was shown in (Mc Auley 2020) the obese population has a higher TC and this trend is not captured by quadratic term modeling for TC.
+
+\subsection{Analysing Race/Ethinicity effect on BMI}
+
+Figure \ref{fig:resu3} illustrates age effects on 90th BMI quantile, where age modeled as a quadratic term.
+There is a clear association between age and BMI.
+In general, age effects on BMI, considering race ethnicity, behaves at a similar way as the whole population, which is a parabolic shape.
+For example, a young Mexican female not using cholesterol medication has an average BMI around 40 \(kg/m^2\), but the BMI values decreases later up to 35 \(kg/m^2\) at age 80 years.
+The effects of age is higher for cholesterol medicated users by an average of about about 2 \(kg/m^2\).
+Moreover, Mexican males have a higher average BMI than females by about 2 \(kg/m^2\) at \(\tau =0.9\).
+The lowest age effects on 90th BMI quantile is found in the white race.
+In general age effect on BMI for males are higher than for females. Figure \ref{fig:resu33} presents age effect on BMI through using spline basis expansion.
 
@@
 
-\caption{Illustration of the quadratic age effect on BMI leveles for four different quantiles of the conditional BMI distribution. }\label{fig:resu3}
+\caption{Illustration of the quadratic age effect on 90th BMI quantile for different race ethnacity groups.}\label{fig:resu3}
 \end{figure}
-
-Using splines
 
@@
 
-\caption{Age effect modeled using bsplines }\label{fig:resu33}
+\caption{Illusteration of the age effect on the 90th BMI quantile, where age modeled using spline basis expension. The effect shown for diiferent race/ethenicity groups and gender.}\label{fig:resu33}
 \end{figure}
+
+Figure \ref{fig:resu4} and Figure \ref{fig:resu330} present TC effect on BMI with respect to different race/ethnicity groups by modeling TC as a quadratic term and spline basis expansion, respectively.
+Male population have higher
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{/home/mabdulsa/BMI/images/comp_age_mixed}
-
-}
-
-\caption{  An illustration of  marginal effects of age on different BMI quantiles. The predictors modeled using quadratic terms and splines.}\label{fig:resu1000}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{/home/mabdulsa/BMI/images/comp_tot_mixed}
-
-}
-
-\caption{ An illustration of  marginal effects of total cholesterol  on different BMI quantiles. The predictors modeled using quadratic terms and splines.}\label{fig:resu1010}
-\end{figure}
-
-The quadratic effect of total cholesterol on the conditional distribution of BMI is convex.
-At the lower tail, the correlation is positive that is as cholesterol increases the BMI increases.
-decreasing glucose level by somewhat around 1.4 up to around 180 Cholesterol level.
-However, at higher quantile the association become negative that is as cholesterol level increases the BMI decreases, see Figure \ref{fig:resu4}.
-The relation between total cholesterol and fasting glucose has been studied in (Tsaousis 2014),(Chang et al.
-2011).
-They found that there is a positive correlation between the two groups on average.
-
-On the other hand, when we use splines to modeled the total cholesterol, there is a huge difference in the shape of the association expect at the higher quantile there is some similarity.
-At the lower quantile, there is negative correlation between total cholesterol and BMI for total cholesterol in the range less than 160, then the correlation becomes positive for total cholesterol in the range of (170, 250).
-at the 55th quantile, the correlation is positive for low cholesterol level and then becomes almost flat for the rest cholesterol values.
-At a higher quntile, the correlation becomes negative at cholesterol level in the range (160,300), see Figure \ref{resu330}.
-
 \section{Conclusion}
 
-Multivariate quantile regression is used to study the effects of different risk factors on the BMI levels.
-Cholesterol drug effects on BMI is negligible at low quantile but at higher quantile cholesterol medication effects on BMI is larger.
-This study showed that the association between BMI and total cholesterol is varying with respect to different quantile.
+Multivariate quantile regression is used to study the effects of different risk factors on different BMI levels.
+our study shows that different risk factors for higher BMI have different effects on different quantiles.
+Moreover, predictors effect on BMI is subject to the methods used to represent it, which are quadratic modeling spline basis expansion.
+Quadratic term for the response to take a convex shape.
+This is different from spline basis expansions in which different polynomials have been used to model the predictors.
+Our results shows the turning point in the association between age and BMI is 30 years old.
+This is the age when people start to consider reducing weight.
+This trend is shown through the descriptive statistics and QR.
+However, quadratic modeling for the age is not able to detect this trend.
 
-total people who have TC levels around 190 mg/dL have the lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile, the optimal cholesterol level is around 200 mg/dL.
-Moreover,
+The effects of TC on the BMI is studied with respect to two ways for modeling TC.
+The turning point for patients to start reducing their BMI is when TC hit around 200 mg\(\setminus\)dL.
+However, if TC hits 350, the association become positive.
+This is a sign where patients are losing their control on their TC and BMI levels.
 
@@
 Cade, Brian S, and Barry R Noon. 2003. ``A Gentle Introduction to Quantile Regression for Ecologists.'' \emph{Frontiers in Ecology and the Environment} 1 (8): 412--20.
+
+\leavevmode\hypertarget{ref-calle1999body}{}%
+Calle, Eugenia E, Michael J Thun, Jennifer M Petrelli, Carmen Rodriguez, and Clark W Heath Jr.
+1999.
+``Body-Mass Index and Mortality in a Prospective Cohort of Us Adults.'' \emph{New England Journal of Medicine} 341 (15): 1097--1105.
 
@@
 
+\leavevmode\hypertarget{ref-mc2020effects}{}%
+Mc Auley, Mark Tomás. 2020. ``Effects of Obesity on Cholesterol Metabolism and Its Implications for Healthy Ageing.'' \emph{Nutrition Research Reviews} 33 (1): 121--33.
+
 \leavevmode\hypertarget{ref-mozaffarian2015executive}{}%
@@
 ``Executive Summary: Heart Disease and Stroke Statistics---2015 Update: A Report from the American Heart Association.'' \emph{Circulation} 131 (4): 434--41.
+
+\leavevmode\hypertarget{ref-nuttall2015body}{}%
+Nuttall, Frank Q. 2015. ``Body Mass Index: Obesity, Bmi, and Health: A Critical Review.'' \emph{Nutrition Today} 50 (3): 117.
 
